# Data

The STAT presented proposed analyses and data sources for the 2021 `r spp` 
assessment during the PFMC Pre-Assessment Workshop for 2021 Vermilion and 
Lingcod Stock Assessments, hosted virtually on March 29, 2021. Topics addressed 
included progress on research priorities, data sources and types, stock structure, 
fleet structure, key model parameters (e.g. natural mortality), and potential 
challenges. Descriptions of each data source included in the model 
(Figure \@ref(fig:data-plot)) and sources that were explored, but not included
are included within this section.

## Fishery-Dependent Data

A complete summary of estimated `r spp` removals by each fleet in the 
commercial and recreational fleets modeled in this assessment is provided in Table 
\@ref(tab:landings).  The data sources for landings varied by each fleet and a summary 
of each data source and the time period for which it was used is in Table \@ref(tab:catch-source).
Of note is that the commercial landings are in metric tons (mt) and the recreational landings 
are in numbers of fish (thousands of fish). Data and 
methods used to derive these estimates are described in this section.

## Commercial

```{r render-21, results = "asis"}
sa4ss::read_child("21data-a-commercial.Rmd")
```

```{r render-21b, results = "asis"}
sa4ss::read_child("21data-b-recreational.Rmd")
```


## Fishery-Independent data


```{r render-21c, results = "asis"}
sa4ss::read_child("21data-c-fishery-independent.Rmd")
```


## Data sources considered, but not used


```{r render-21d, results = "asis"}
sa4ss::read_child("21data-sources-not-used.Rmd")
```

## Biology

```{r render-2, results = "asis"}
sa4ss::read_child("22biology.Rmd")
```

