# Data

The STAT presented proposed analyses and data sources for the 2021 `r spp` 
assessment during the PFMC Pre-Assessment Workshop for 2021 Vermilion and 
Lingcod Stock Assessments, hosted virtually on March 29, 2021. Topics addressed i
ncluded progress on research priorities, data sources and types, stock structure, 
fleet structure, key model parameters (e.g. natural mortality), and potential 
challenges.Descriptions of each data source included in the model 
(Figure \@ref(fig:data-plot)) and sources that were explored but not included
are included within this section.

## Fishery-Dependent Data

A complete summary of estimated `r spp` removals (commercial and recreational) 
in this assessment model, by year and data source, is provided in Tables 
(\@ref(tab:comm-catches)) and \@ref(tab:rec-catches), respectively. Data and 
methods used to derive these estimates are described in this section.


```{r render-21, results = "asis"}
sa4ss::read_child("21commercial.Rmd")
```

```{r render-22, results = "asis"}
sa4ss::read_child("22recreational.Rmd")
```


## Fishery-Independent data


```{r render-23, results = "asis"}
sa4ss::read_child("23surveys.Rmd")
```


```{r render-21g, results = "asis"}
sa4ss::read_child("21f-survey-wcgbts.Rmd")
```


```{r render-21h, results = "asis"}
sa4ss::read_child("21h-survey-ccfrp.Rmd")
```




### Data sources considered, but not used




```{r render-21, results = "asis"}
sa4ss::read_child("21commercial.Rmd")
```

```{r render-21, results = "asis"}
sa4ss::read_child("21commercial.Rmd")
```
