# Assessment Model

## History of Modeling Approaches

Vermilion was assessed coastwide as a data poor species using 
Depletion-Based Stock Reduction Analysis (DB-SRA) [@Dick2010]. Average catch 
2008-2009 was 136.3 mt, and the median OFL in 2010 was 314.3 mt with a 28% 
probability that recent catch exceeded the 2010 [@Dick2010].

A 2005 assessment was not accepted for management. 
From the September 2005 [Briefing Book](https://www.pcouncil.org/documents/2005/09/f-groundfish-management-september-2005.pdf/): 
"The SSC considers the assessment to be best available science, but at this  stage does not 
endorse the results as being suitable for setting OYs." A 2013 data moderate 
assessment was prepared, but not reviewed. From Pacific Coast Groundfish Stock 
Assessment Review (STAR) Panel Report For Data-Moderate Assessments (2013): 
"There was insufficient time during the review to evaluate all the assessments 
originally requested by the Council. Assessments for vermilion/sunset rockfishes 
(*Sebastes miniatus* and *Sebastes crocotulus*) and yellowtail rockfish 
(south of \CapeM) were not presented by the Stock Assessment Team (STAT)."


### Most Recent STAR Panel and SSC Recommendations 

The 2005 STAR panel report compiled recommendations specific to vermilion, and also 
generic rockfish recommendations The generic rockfish recommendation are not 
presented here.

**Vermilion rockfish recommendations**

Investigation into the species composition of nominal vermilion rockfish is needed.
It is not clear that separate assessments for the northern and southern areas are warranted
for vermilion rockfish. Although there were differences in the estimated magnitude and
timing of recruitment events, the estimated stock trends were similar in both areas.
Pooling of data from northern and southern areas may permit a more robust assessment
model to be obtained.

*2021 STAT response.* Since the 2005 assessment, vermilion rockfish were speciated 
to vermilion and sunset rockfishes [@Hyde2009].  Sunset rockfish are more common south of 
Pt. Conception (\PtC) and historical catches and length distributions between 
the two areas are different. The STAT discussed this at the Pre-Assessment workshop 
and all participants agreed that modeling the areas separately was an appropriate 
decision.


**General rockfish Recommendations**

- The historical catch is an important input into any stock assessment. 
Although efforts have been made to construct catch time series for California rockfish, 
a more sustained effort is needed to do this for all rockfish species. It should not be 
left to individual analysts to do this for a species as stock assessments arise. It 
should be done by a specialist team for all species simultaneously, so that consistent 
times series can beestablished.

- Management changes affect fisher behaviour and alter the correct interpretation of CPUE
time series. As for catch histories, it is important that a specialist team consider and
document all management changes and how they may have impacted on catch rates for
all species. Again, this should not be left to individual assessment authors as the issues
are generic and patterns might not be obvious without a multi-species perspective.

- Improved documentation of input data and output for GLM analyses of CPFV and
RecFIN CPUE data is recommended. In general, GLM analyses should provide analysis
of deviance tables, estimated coefficients, and their standard errors to document these
calculations. Information on amount of RecFIN records filtered by species association
also needs to be presented to show the effect of the species association analysis. 
Although this method is an objective approach to filtering records, it is unknown 
how well works in practice to reduce the potential biases of CPUE data. A paper describing a
comprehensive application of GLM methods to CPFV and RecFIN CPUE data on
California rockfish would be a important contribution to the assessment process and the
primary literature.

- Many rockfish assessments use CPUE data from the CPFV fishery as an index of
population abundance. The CPFV fishery is focused primarily on marketing a successful
“fishing experience” that is related to the desirability of the species caught, quantity,
body size, and fighting characteristics. The default assumption of proportionality
between CPUE and abundance has not been evaluated for a fishery with these
characteristics. Simulation modeling of fleet dynamics in a multi-species context is one
possible way to address these issues.

- A more complete understanding of the multi-species aspects of rockfish population
dynamics is needed. Although some rockfish stocks have declined in recent decades
under heavy fishing pressure and environmental change, other rockfish species have
apparently increased. Are these species adapted to different environmental conditions, or
are these increases due to the indirect effects of reduced competition and/or predation?


Conducting additional assessments of the many relatively uncommon rockfish in
California is a difficult but worthwhile objective. To facilitate this process, 
the Panel has a number suggestions:

1. Keep the models simple.  
2. Make reasonable assumptions based on life history and better studied species for
parameters that cannot be reliably estimated, such as natural mortality, stock-recruit
steepness, selectivity.  
3. Think meta-analytically. For example, similar species that are often caught together
are likely to have experienced similar fishing mortality rates and trends. There are also
more rigorous methods for sharing information between related stocks that could be
considered.  
4. Make the most of CPUE data:  
    + For several assessments, indices from GLM analyses of site-specific CPFV data
apparently tracked population trends better than indices from RecFIN data, even
when a subset of records had been selected using the Stevens and MacCall (2004)
procedure. Greater priority should be given to collecting site-specific CPUE data.
Given the ubiquity of GPS systems and hand-held data recorders, obstacles to
collecting site-specific information from fisheries are now logistic rather than
technological.  
    + Location information for the historical groundfish catch data of all species is
currently available, in hard copy form only, from the California Department of
Fish and Game. Putting this information into electronic format would greatly
improve the ability to assign catches of all species to specific stocks on a trip-bytrip basis.  
5. Do not put too much trust in model results. Models are no better that their input data
and assumptions, and for many rockfish species, the data are sparse and potentially
misleading.  



```{r render-31, results = "asis"}
sa4ss::read_child("31model-star-responses.Rmd")
```


```{r render-32, results = "asis"}
#if(model.area=='NCA'){
sa4ss::read_child("32model-description-north.Rmd") 
#} else {
#sa4ss::read_child("32model-description-south.Rmd")
#}
```



```{r render-34, results = "asis"}
sa4ss::read_child("34model-prestar-base-selection.Rmd")
```


```{r render-35, results = "asis"}
sa4ss::read_child("35model-prestar-base-results.Rmd")
```


```{r render-36, results = "asis"}
sa4ss::read_child("36model-uncertainty.Rmd")
```


