# Assessment Model Description

## History of Modeling Approaches

Current yield estimates for vermilion rockfish were estimated using
Depletion-Based Stock Reduction Analysis (DB-SRA) [@Dick2010]. Average catch 
in 2008-2009 was 136.3 mt, and the median OFL in 2010 was 314.3 mt with a 28% 
probability that recent catch exceeded the OFL in 2010 [@Dick2010].

A 2005 assessment was not accepted for management. 
From the September 2005 [Briefing Book](https://www.pcouncil.org/documents/2005/09/f-groundfish-management-september-2005.pdf/): 
"The SSC considers the assessment to be best available science, but at this  stage does not 
endorse the results as being suitable for setting OYs." A 2013 data moderate 
assessment was prepared, but not reviewed. From the Pacific Coast Groundfish Stock 
Assessment Review (STAR) Panel Report for Data-Moderate Assessments (2013): 
"There was insufficient time during the review to evaluate all the assessments 
originally requested by the Council. Assessments for vermilion/sunset rockfishes 
(*Sebastes miniatus* and *Sebastes crocotulus*) and yellowtail rockfish 
(south of \CapeM) were not presented by the Stock Assessment Team (STAT)."


### Most Recent STAR Panel and SSC Recommendations 

The 2005 STAR panel report compiled recommendations specific to vermilion, and also 
generic rockfish recommendations The generic rockfish recommendation are not 
presented here.  The 2005 assessment was not accepted for management by the PFMC.

**Vermilion rockfish recommendations**

Investigation into the species composition of nominal vermilion rockfish is needed.
It is not clear that separate assessments for the northern and southern areas are warranted
for vermilion rockfish. Although there were differences in the estimated magnitude and
timing of recruitment events, the estimated stock trends were similar in both areas.
Pooling of data from northern and southern areas may permit a more robust assessment
model to be obtained.

*2021 STAT response.* Since the 2005 assessment, vermilion rockfish were speciated 
to vermilion and sunset rockfishes [@Hyde2009].  Sunset rockfish are more common south of 
Pt. Conception (\PtC) and historical catches and length distributions between 
the two areas are different. The STAT discussed this at the Pre-Assessment workshop 
and all participants agreed that modeling the areas separately was an appropriate 
decision.




```{r render-31, results = "asis"}
sa4ss::read_child("31model-star-responses.Rmd")
```


```{r render-32, results = "asis"}
sa4ss::read_child("32model-description.Rmd") 
```



```{r render-34, results = "asis"}
sa4ss::read_child("34model-prestar-base-selection.Rmd")
```

