## Pre-STAR Base Model Results

The base model parameter estimates along with approximate asymptotic standard errors are shown in Table \ref{tab:params} and the likelihood components are shown in Table \ref{tab:likes}. Estimates of derived reference points and approximate 95 percent asymptotic confidence intervals are shown in Table \ref{tab:referenceES}. Estimates of stock size and status over time are shown in Table \ref{tab:timeseries}. 

### Parameter Estimates

```{r parameters, include = FALSE, eval = TRUE, cache = TRUE}
# get parameter names from base model
estimated_pars <- model$parameters %>%
  dplyr::filter(!is.na(Active_Cnt)) %>%
  rownames()
```

The base model has a total of `r length(estimated_pars)` estimated parameters
(Figure \@ref(tab:params)) that can be grouped into the following
categories and are described in more detail in the following sections:

Biological parameters  
- 2 natural mortality parameters (female and male $M$)
- 10 growth parameters, where females and males each had
- 3 Schnute growth parameters (length at age frog, length at age frog, and $k$)
- 2 parameters controlling variability in growth, the CV in length at age 0.5
  and the CV in length at age 14 with a linear ramp in length-at-age

Stock-recruit parameters  
- `r 2 + nrow(model$recruit)` recruitment parameters  
- $log(R_0)$ controlling equilibrium recruitment  
- `r nrow(model$recruit)` recruitment deviations parameters covering the range  
  `r min(model$recruit$Yr)`-`r max(model$recruit$Yr)`, with 
  `r min(model$recruit$Yr[model$recruit$era=="Main"])`-`r max(model$recruit$Yr[model$recruit$era=="Main"])`
  representing the "main" period modeled as a zero-centered deviation vector  
  
Index parameters  
- `r sum(sum(grepl("Q_extra", estimated_pars)))` extra standard deviation parameters
for indices  

Selectivity parameters  
- `r sum(grepl("Size_DblN", estimated_pars))` selectivity parameters, of which
`r sum(grepl("Size_DblN.*BLK", estimated_pars))` represented changes over time  

### Fixed parameters


- $h$ controlling the steepness of the stock-recruit relationship
- $M$ for male




### Growth (Length-at-Age)
```{r}
# calculate Linf and t0 from Schnute vB parameterization
unSchnute.fn <- function(Amin, Amax, Lmin, Lmax, k)
{
   Linf <- Lmin + (Lmax-Lmin)/(1-exp(-k*(Amax-Amin)))
   t0   <- Amin + Amax - (1/k)*log((exp(k*Amax)*Lmax - exp(k*Amin)*Lmin)/(Lmax-Lmin))
   out  <- c(Linf, t0)
   names(out) <- c("Linf","t0")
   return(out)
}
# vermilion example
# females
unSchnute.fn(0, 30, 8.3113, 53.6773, 0.1679070)
# for males,  apply exponential offsets to the female values
unSchnute.fn(0, 30, 8.3113*exp(-2.3422300), 53.6773*exp(-0.0667862), 0.1679070*exp(0.2930410))
```

\begin{centering}

Females $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Fem_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Fem_GP_1[1], 3)`; $t_0$ = `r round(model$Growth_Parameters[1,10], 2)`

Males $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Mal_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Mal_GP_1[1], 3)`; $t_0$ = `r round(model$Growth_Parameters[2,10], 2)`

\end{centering}

\vspace{0.5cm}



### Fits to the Data

Model fits to the indices of abundance, fishery length composition, survey length 
composition, and conditional age-at-length observations are all discussed below. 
The full r4ss plotting output is available in the supplementary material.

### Population Trajectory



### Reference Points


Figure \@ref(fig:bh-curve)
Figure \@ref(fig:bh-resids)


Reference points were calculated using the estimated selectivities and catch distribution among fleets in the most recent year of the model, `r endyr`. 
Sustainable total yield (landings plus discards) was 
`r round(model$derived_quants[model$derived_quants$Label == 'Dead_Catch_SPR', 'Value'], 2)` mt when using an $SPR_{50\%}$ 
reference harvest rate. The spawning output equivalent to 40% of the unfished level ($SB_{40\%}$) was `r round(model$derived_quants[model$derived_quants$Label == 'SSB_SPR', 'Value'], 2)` 
million eggs. 

The predicted spawning output from the base model shows frogs (Figure \@ref(fig:ssb)).  The spawning output then frogs.

The `r endyr`. spawning biomass relative to unfished equilibrium spawning biomass is above the target of 40% of unfished levels (Figure \@ref(fig:depl)). 
The relative fishing intensity, $(1-SPR)/(1-SPR_{50\%})$, was above the management target frogs (Figure \@ref(fig:1-spr)). The relative fishing intensity has been frogs (Figure \@ref(fig:phase)).

Table \ref{tab:ref-pts} shows the full suite of estimated reference points for the base model and Figures \@ref(fig:yield2) and \@ref(fig:yield3) show the equilibrium curve based on a steepness value fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"], 2)`.




