
\newpage

# Appendix A. Detailed Fit to Length Composition Data{-} 
\renewcommand{\thepage}{A\arabic{page}}
\renewcommand{\thefigure}{A\arabic{figure}}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}


```{r, results='asis'}
#plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(mod_loc, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   width = 90,
			   height = 90)
}
```

\FloatBarrier



# Appendix B. MRFSS Dockside Index of Abundance{-}
\renewcommand{\thepage}{B\arabic{page}}
\renewcommand{\thefigure}{B\arabic{figure}}
\renewcommand{\thetable}{B\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}


```{r mrfss-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_NCA.md") 
```

\newpage

# Appendix C. California Onboard CPFV Index of Abundance{-}
\renewcommand{\thepage}{C\arabic{page}}
\renewcommand{\thefigure}{C\arabic{figure}}
\renewcommand{\thetable}{C\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r ca-cpfv-onboard-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_NCA.md") 
``` 

\newpage


# Appendix D. Deb Wilson-Vandenberg Onboard CPFV Index of Abundance{-}
\renewcommand{\thepage}{D\arabic{page}}
\renewcommand{\thefigure}{D\arabic{figure}}
\renewcommand{\thetable}{D\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r devwv-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_DebWV_onboard_writeup_NCA.md") 
``` 

\newpage


# Appendix E. CRFS PR Dockside Index of Abundance{-}
\renewcommand{\thepage}{E\arabic{page}}
\renewcommand{\thefigure}{E\arabic{figure}}
\renewcommand{\thetable}{E\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_NCA.md")
``` 

\newpage

# Appendix F. CCFRP Index of Abundance{-}
\renewcommand{\thepage}{F\arabic{page}}
\renewcommand{\thefigure}{F\arabic{figure}}
\renewcommand{\thetable}{F\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r ccfrp-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CCFRP_writeup_NCA.md") 
``` 

\newpage

# Appendix G. WCGBTS Index of Abundance{-}
\renewcommand{\thepage}{G\arabic{page}}
\renewcommand{\thefigure}{G\arabic{figure}}
\renewcommand{\thetable}{G\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r wcgbts-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_NCA.md")
``` 

\newpage

# Appendix H. Recreational Regulations{-}
\renewcommand{\thepage}{H\arabic{page}}
\renewcommand{\thefigure}{H\arabic{figure}}
\renewcommand{\thetable}{H\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r rec-regs, results = 'asis'}
sa4ss::read_child("70appendices-regs.Rmd")
``` 

\newpage 

# Appendix I. Management Boundary Analysis{-}
\renewcommand{\thepage}{I\arabic{page}}
\renewcommand{\thefigure}{I\arabic{figure}}
\renewcommand{\thetable}{I\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r mngmnt-split, results = 'asis'}
sa4ss::read_child("./indices/Vermilion_PR_management_split_writeup_NCA.md")
``` 

\newpage 

# Appendix J. Decision Table Assuming Category 2{-}
\renewcommand{\thepage}{J\arabic{page}}
\renewcommand{\thefigure}{J\arabic{figure}}
\renewcommand{\thetable}{J\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

Uncertainty in the forecasts is based upon the three states of nature agreed upon 
at the STAR panel, reflecting three different natural mortality rates. The steepness 
parameter of the Beverton-Holt stock-recruit curve was fixed in the base model
and in all of the forecasts.  The northern California model is not data rich and 
while there is uncertainty in steepness, it was not well estimated in the base 
model when natural mortality was also estimated. The alternative states of nature 
maintain the 
female to male natural mortality rate ratio from  the base model. To capture the 
$75\%$ interval around the negative log-likelihood, alternate states were identified 
within 0.66 negative log-likelihood points from the base model where female 
$M$ = 0.0856 and male $M$ = 0.0805.
The high state of nature fixes female $M$ = 0.0956 and male $M$ = 0.08989. 
For the low state of nature, female $M$ = 0.0769 and male $M$ = 0.07231.

For reference, the base model predicted $\sigma$ = 0.246. The buffers between the 
OFL and ABC  were calculated assuming a category 2 stock, with  $\sigma$ = 1.0 
and a $p^*$ = 0.45. The alternative catch stream (rows in the table) include $\sigma$ = 1.0
with a $p^*$ = 0.4 for a category 2 stock.  

Current forecasts based on the alternative states of nature and requested catch 
streams project that the stock will remain above the target threshold of 40% in 
2032 (Table \@ref(tab:DecisionEScat2)).  In all of the scenarios of the low state 
of nature, the stock remains below the 
target threshold of $40\%$ until 2026 or 2027.
The base model with the base catches results in an increasing stock over the period 
from 
2023-2032. In all scenarios the catch significantly decreases from 2022 to 2023; 
projected catch in 2022 is 227 mt, and 2023 catches from the base 
model range from 118-139 mt.  The base model includes a portion of the stock within 
the northern management unit (north of \CapeM).  An analysis based on the private/rental 
mode index through 2019 suggests 
that $4.44\%$ of the catches from this model should be apportioned to the northern 
management unit for vermilion rockfish.


```{r,echo=FALSE, warning=FALSE, message=FALSE}
decisiontable.filein = list.files(path = table_loc, 
                  pattern = glob2rx(paste0("VRML_decision_table_", model.area, "_cat2.xlsx")), 
                  full.names = TRUE)
decisiontable_cat2 <- readxl::read_xlsx(decisiontable.filein) %>%
   mutate(across(grep("Spawning", .), round, 0)) %>%
   mutate(across(grep("Catch", .), round, 1)) %>%
   mutate(across(grep("Fraction", .), round, 3))
```



```{r, results = 'asis'}
kableExtra::kbl(decisiontable_cat2, 
                col.names = c(" ","Year",
                              "Buffer",
                              "Catch (mt)",
                              "Spawning Output", "Fraction Unfished",
                              "Spawning Output", "Fraction Unfished",
                              "Spawning Output", "Fraction Unfished"),
                caption = "Decision table summarizing 12-year projections 
                (2021 to 2032) for vermilion rockfish based on three alternative 
                states of nature spanning quantiles of spawning output in 
                2021.  Columns range over low, medium, and high state of 
                nature, and rows range over different assumptions of total 
                catch levels corresponding to the forecast catches from 
                each state of nature.  Catches in 2021 and 2022 are fixed 
                at catches provided by the CDFW.",
                booktabs=TRUE,
                label="DecisionEScat2",
                digits = c(0,0,3,0,0,3,0,3,0,3),
                align = "c",
                escape = FALSE,
                linesep = "") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  add_header_above(c(" " = 4,
                     "NLL = 1031.36" = 2,
                     "NLL = 1030.7" = 2,
                     "NLL = 1031.36" = 2)) %>%
  add_header_above(c(" " = 4,
                     "Male M = 0.0723" = 2, 
                     "Male M = 0.0805" = 2,
                     "Male M = 0.0899" = 2), line = F) %>%
  add_header_above(c(" " = 4,
                     "Female M = 0.0769" = 2, 
                     "Female M = 0.0856" = 2,
                     "Female M = 0.0956" = 2), line = F) %>%
  add_header_above(c(" " = 4, 
                     "Low Productivity" = 2, 
                     "Base Model" = 2, 
                     "High Productivity" = 2)) %>%
  column_spec(1, width = "1in") %>%
  column_spec(c(2:4), border_left = T) %>%
  column_spec(c(5,7,9), width = ".8in", border_left = T) %>%
  column_spec(c(6,8,10), width = ".8in") %>%
  collapse_rows(columns = 1, valign = "middle", latex_hline = "major") 
```




\clearpage
# References{-}
\thispagestyle{empty} 


