
\newpage

# Appendix A. Detailed Fit to Length Composition Data{-} 
\renewcommand{\thepage}{A\arabic{page}}
\renewcommand{\thefigure}{A\arabic{figure}}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}


```{r, results='asis'}
plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(mod_loc, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   width = 90,
			   height = 90)
}
```

\FloatBarrier



# Appendix B. MRFSS Dockside Index of Abundance{-}
\renewcommand{\thepage}{B\arabic{page}}
\renewcommand{\thefigure}{B\arabic{figure}}
\renewcommand{\thetable}{B\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}


```{r mrfss-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_NCA.md") 
```

\newpage

# Appendix C. California Onboard CPFV Index of Abundance{-}
\renewcommand{\thepage}{C\arabic{page}}
\renewcommand{\thefigure}{C\arabic{figure}}
\renewcommand{\thetable}{C\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r ca-cpfv-onboard-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_NCA.md") 
``` 

\newpage


# Appendix D. Deb Wilson-Vandenberg Onboard CPFV Index of Abundance{-}
\renewcommand{\thepage}{D\arabic{page}}
\renewcommand{\thefigure}{D\arabic{figure}}
\renewcommand{\thetable}{D\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r devwv-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_DebWV_onboard_writeup_NCA.md") 
``` 

\newpage


# Appendix E. CRFS PR Dockside Index of Abundance{-}
\renewcommand{\thepage}{E\arabic{page}}
\renewcommand{\thefigure}{E\arabic{figure}}
\renewcommand{\thetable}{E\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_NCA.md")
``` 

\newpage

# Appendix F. CCFRP Index of Abundance{-}
\renewcommand{\thepage}{F\arabic{page}}
\renewcommand{\thefigure}{F\arabic{figure}}
\renewcommand{\thetable}{F\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r ccfrp-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CCFRP_writeup_NCA.md") 
``` 

\newpage

# Appendix G. WCGBTS Index of Abundance{-}
\renewcommand{\thepage}{G\arabic{page}}
\renewcommand{\thefigure}{G\arabic{figure}}
\renewcommand{\thetable}{G\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r wcgbts-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_NCA.md")
``` 

\newpage

# Appendix H. Recreational Regulations{-}
\renewcommand{\thepage}{H\arabic{page}}
\renewcommand{\thefigure}{H\arabic{figure}}
\renewcommand{\thetable}{H\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r rec-regs, results = 'asis'}
sa4ss::read_child("70appendices-regs.Rmd")
``` 

\newpage 

# Appendix I. Management Boundary Analysis{-}
\renewcommand{\thepage}{I\arabic{page}}
\renewcommand{\thefigure}{I\arabic{figure}}
\renewcommand{\thetable}{I\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r mngmnt-split, results = 'asis'}
sa4ss::read_child("./indices/Vermilion_PR_management_split_writeup_NCA.md")
``` 

\clearpage
# References{-}
\thispagestyle{empty} 


