\clearpage

# Appendix



## MRFSS Dockside Index of Abundance

```{r mrfss-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_NCA.md") 
```
  
\clearpage

## California Onboard CPFV Index of Abundance
 
```{r ca-cpfv-onboard-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_NCA.md") 
``` 

\clearpage 

## Deb Wilson-Vandenberg Onboard CPFV Index of Abundance

```{r devwv-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_DebWV_onboard_writeup_NCA.md") 
``` 

\clearpage


## CRFS PR Dockside  Index of Abundance

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_NCA.md")
``` 

\clearpage

## CCFRP Index of Abundance

```{r ccfrp-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CCFRP_writeup_NCA.md") 
``` 

\clearpage

## WCGBTS Index of Abundance

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_NCA.md")
``` 

\clearpage

## Graphic representing California's recreational regulations over time

```{r rec-regs, results = 'asis'}
  sa4ss::read_child("70appendices-regs.Rmd")
``` 

