\clearpage

# Appendix

## MRFSS Dockside Index of Abundance {#mrfss-index}

```{r mrfss-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_SCA.md") 
```
  
\clearpage
 
## California CPFV Onboard Index of Abundance {#cpfv-index}

```{r ca-cpfv-onboard-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_SCA.md") 
``` 

\clearpage

## CRFS PR Dockside Index of Abundance {#pr-index}

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_SCA.md")
``` 

\clearpage

## NWFSC Hook-and-Line Survey Index of Abundance {#nwfschl-index}

```{r nwfschl-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_NWFSC_HL_writeup_SCA.md")
``` 


\clearpage

## WCGBTS Index of Abundance {#wcgbts-index}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_SCA.md")
``` 

\clearpage

## Recreational Regulations {#regs-graphic}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_SCA.md")
``` 


# References
       


