\clearpage

# Appendix


## Detailed Fit to Length Composition Data{#append-fit} 


```{r, results='asis'}
plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(mod_loc, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\clearpage

## MRFSS Dockside Index of Abundance {#mrfss-index}

```{r mrfss-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_NCA.md") 
```
  
\clearpage

## California Onboard CPFV Index of Abundance {#cpfv-index}
 
```{r ca-cpfv-onboard-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_NCA.md") 
``` 

\clearpage 

## Deb Wilson-Vandenberg Onboard CPFV Index of Abundance {#debwv-index}

```{r devwv-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_DebWV_onboard_writeup_NCA.md") 
``` 

\clearpage


## CRFS PR Dockside Index of Abundance {#pr-index}

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_NCA.md")
``` 

\clearpage

## CCFRP Index of Abundance {#ccfrp-index}

```{r ccfrp-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CCFRP_writeup_NCA.md") 
``` 

\clearpage

## WCGBTS Index of Abundance {#wcgbts-index}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_NCA.md")
``` 

\clearpage

## Recreational Regulations {#regs-graphic}

```{r rec-regs, results = 'asis'}
  sa4ss::read_child("70appendices-regs.Rmd")
``` 

\clearpage 

# References

