\clearpage

# Appendix


## Indices of Abundance{#append-indices}

```{r mrfss-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_NCA.md") 
```
  
\newpage 
 
```{r ca-cpfv-onboard-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_NCA.md") 
``` 

\newpage 

```{r devwv-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_DebWV_onboard_writeup_NCA.md") 
``` 

\newpage


```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_NCA.md")
``` 

\newpage

```{r ccfrp-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CCFRP_writeup_NCA.md") 
``` 


```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_NCA.md")
``` 





  
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_SCA.md") 
  sa4ss::read_child("./indices/vermilion_NWFSC_HL_writeup_SCA.md")       
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_SCA.md") 
   sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_SCA.md")
     sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_SCA.md")
