---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
params:
    model: "south"
preamble: |
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{placeins}
  - \usepackage{enumerate}
lang: en
papersize: a4
---



<!--chapter:end:00a.Rmd-->




<!--chapter:end:00authorsnorth.Rmd-->




<!--chapter:end:00authorssouth.Rmd-->

---
bibliography:
  - sa4ss.bib
---

<!--chapter:end:00bibliography.Rmd-->

---
title: The status of Vermilion Rockfish (_Sebastes miniatus_) and Sunset Rockfish (_Sebastes crocotulus_) in U.S. waters off the coast of California north of Pt. Conception in 2021
---

<!--chapter:end:00titlenorth.Rmd-->

---
title: The status of Vermilion Rockfish (_Sebastes miniatus_) and Sunset Rockfish (_Sebastes crocotulus_) in U.S. waters off the coast of California south of Pt. Conception in 2021
---

<!--chapter:end:00titlesouth.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}


\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:01a.Rmd-->


# Executive Summary{-}

Placeholder


## Stock{-}
## Landings{-}
## Data and Assessment{-}
## Stock Biomass{-}
## Recruitment{-}
## Exploitation Status{-}
## Reference Points{-}
## Management Performance{-}
## Unresolved Problems and Major Uncertainties{-}
## Decision Table{-}
## Research and Data Needs{-}

<!--chapter:end:01executive.Rmd-->

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
\setcounter{figure}{0}

<!--chapter:end:10a.Rmd-->

# Introduction

```{r render-12, results = "asis"}
sa4ss::read_child("12basicinfo.Rmd")
```


```{r render-13, results = "asis"}
sa4ss::read_child("13fisheries.Rmd")
```


<!--chapter:end:11introduction.Rmd-->



## Basic Information and Life History
## Early Life History

<!--chapter:end:12basicinfo.Rmd-->



## Historical and Current Fishery Information
## Summary of Management History
## Management Performance
## Foreign Fisheries

<!--chapter:end:13fisheries.Rmd-->


# Data

Placeholder


## Fishery-Dependent Data
## Fishery-Independent data
### Data sources considered, but not used

<!--chapter:end:20data.Rmd-->

### Commercial Landings and Discards

*Commercial Landings Prior to 1916*

For landings estimates prior to 1916, we based our reconstruction on the total rockfish catches reported in a summary of early California fisheries landings by Sette and Fielder [-@Sette1928] for the years 1888, 1892, 1895, 1899, 1904, 1908 and 1915.  No rockfish were reported for 1888, thus we assumed no catches for that year and interpolated the catches between 0 and the 1892 catches (total of 834 tons) reported.  Similarly, catches between the reported years were interpolated assuming a straight linear trend between the years reported.  We used a ratio-estimator derived from the catch reconstruction fraction of vermillion rockfish in total rockfish landings for the 1916 to 1919 period (the ratio for a comparable five year period was nearly identical).  We apportioned the catches north and south of Point Conception based on ratio estimators that used the same assumptions used to apportion catches in the reconstruction time period (1916-1968).  The catch reconstruction estimates indicated that vermillion made up slightly under 1% of the total rockfish catches during the early (1916-1919) time period, although the estimates indicate a slightly larger fraction (1.5%) of total catches south of Conception relative to the fraction of total catches to the north (0.9%).  However, it is likely that the reconstruction is overestimating the fraction of smaller and/or more deeply distributed species relative to larger, shallower species as the reconstruction is based on the species composition data collected from market category samples in the late 1970s and early 1980s.  The fishery has been shown to have progressed over time from a shallower, more nearshore distribution of effort to one in which deeper and more offshore waters were targeted [@Miller2014].  The notion that vermillion catches may have been greater is also consistent with the recognition by Roedel [-@Roedel1948] that during the 1930s and 1940s vermillion were “One of the more important commercial species, it is one of three leading species in Southern California." However, by the time of that report, vermillion represented 5 to 8% of the southern California catch (based on Ralston et al. [-@Ralston2010]), much more than at the beginning of the time series.  Future efforts to improve historical catch reconstructions by accounting for the shift in effort over time to deeper waters should continue to be flagged as a research need. 


*Commercial Landings, 1916-1968*





*Commercial Landings, 1969-1983*


*Commercial Landings, 1984-2000*


*Commercial Discard, 1900-2000*

*Commercial Landings and Discard, 2001-2020*


*Commercial length composition data*



*Commercial age composition data*

<!--chapter:end:21data-a-commercial.Rmd-->



### Recreational Landings and Discard

<!--chapter:end:21data-b-recreational.Rmd-->



## Fishery-Independent Data
### \acrlong{s-ccfrp}
### \acrlong{s-wcgbt}

<!--chapter:end:21data-c-fishery-independent.Rmd-->

### \acrlong{s-tri}

The \gls{s-tri} was first conducted by the \gls{afsc} in 1977, and the survey continued until 2004 [@weinberg_2001_2002].
Its basic design was a series of equally-spaced east-to-west transects across the continential shelf from which searches for tows in a specific depth range were initiated.
The survey design changed slightly over time.
In general, all of the surveys were conducted in the mid summer through early fall.
The 1977 survey was conducted from early July through late September.
The surveys from 1980 through 1989 were conducted from mid-July to late September.
The 1992 survey was conducted from mid July through early October.
The 1995 survey was conducted from early June through late August.
The 1998 survey was conducted from early June through early August.
Finally, the 2001 and 2004 surveys were conducted from May to July.

Haul depths ranged from 91-457 m during the 1977 survey with no hauls shallower than 91 m.
Due to haul performance issues and truncated sampling with respect to depth, the data from 1977 were omitted from this analysis.
The surveys in 1980, 1983, and 1986 covered the US West Coast south to 36.8\textdegree N latitude and a depth range of 55-366 m.
The surveys in 1989 and 1992 covered the same depth range but extended the southern range to 34.5\textdegree N (near Point Conception).
From 1995 through 2004, the surveys covered the depth range 55-500 m and surveyed south to 34.5\textdegree N.
In 2004, the final year of the \gls{s-tri} series, the \gls{nwfsc} \gls{fram} conducted the survey following similar protocols to earlier years.


### \acrlong{s-aslope}

The \gls{s-aslope} operated during the months of October to November aboard the R/V _Miller Freeman_.
Partial survey coverage of the US west coast occurred during the years 1988-1996 and complete coverage (north of 34\textdegree 30\textquotesingle S) during the years 1997 and 1999-2001.
Typically, only these four years that are seen as complete surveys are included in assessments.

<!--chapter:end:21data-sources-not-used.RMd-->



## Biological Data
### Length and Age Compositions
### Age Structures
### Ageing Precision and Bias
### Maturation and Fecundity
### Natural Mortality
### Sex Ratio
### Length-Weight Relationship
### Steepness

<!--chapter:end:22biology.Rmd-->


# Assessment Model

Placeholder


## Summary of Previous Assessments and Reviews
### History of Modeling Approaches
### Most Recent STAR Panel and SSC Recommendations 

<!--chapter:end:30model.Rmd-->

## Summary of Previous Assessments and Reviews

### History of Modeling Approaches

This is the first full assessment for vermilion rockfish. 
Vermilon was assessed coastwide as a data poor species using 
Depletion-Based Stock Reduction Analysis (DB-SRA) [@Dick2010]. The DB-SRA 
model assigned a frog% probability that the then recent (2008-2009) catch 
exceeded the 2010 OFL.

A 2005 assessment was not accepted for management and a 2013 data moderate 
assessment was prepared, but not reviewed.


### Most Recent STAR Panel and SSC Recommendations 

None.


### Response to STAR Panel Requests (not required in draft)




<!--chapter:end:31model-star-responses.Rmd-->

## Model Structure and Assumptions


### Transition to the Current Stock Assessment


### Model Specifications

### Modeling Platform and Structure
General model specifications (e.g., executable version, model structure, definition of fleets and areas)



### Summary of Data for Fleets and Areas

### Other Specifications



### Model Parameters
Describe estimated vs. fixed parameters, priors

<!--chapter:end:32model-description-north.Rmd-->

## Model Structure and Assumptions


### Model Changes from the Last Assessment


### Modeling Platform and Structure
General model specifications (e.g., executable version, model structure, definition of fleets and areas)


### Model Parameters
Describe estimated vs. fixed parameters, priors

### Key Assumptions and Structural Choices

<!--chapter:end:32model-description-south.Rmd-->

## Model Structure and Assumptions


### Model Changes from the Last Assessment (not required for an update assessment)


### Modeling Platform and Structure
General model specifications (e.g., executable version, model structure, definition of fleets and areas)


### Model Parameters
Describe estimated vs. fixed parameters, priors

### Key Assumptions and Structural Choices

<!--chapter:end:34model-prestar-base-selection.Rmd-->



## Pre-STAR Base Model Results
### Parameter Estimates
### Growth (Length-at-Age)
### Fits to the Data
### Population Trajectory
### Reference Points

<!--chapter:end:35model-prestar-base-results.Rmd-->

## Model Diagnostics
Describe all diagnostics

### Convergence

### Sensitivity Analyses

### Retrospective Analysis

### Likelihood Profiles

### Unresolved Problems and Major Uncertainties

<!--chapter:end:36model-uncertainty.Rmd-->

# Reference Points

# Harvest Projections and Decision Tables

# Regional Management COnsiderations

# Unresolved Problems and Major Uncertainties

# Research and Data Needs

<!--chapter:end:40management.Rmd-->

# Acknowledgments
Here are all the mad props!

<!--chapter:end:41acknowledgements.Rmd-->

\floatplacement{table}{H}

# Tables

```{r render-51, results = "asis"}
sa4ss::read_child("51tables-catch.Rmd")
```

```{r render-52, results = "asis"}
sa4ss::read_child("52tables-compsamplesize.Rmd")
```


```{r render-59, results = "asis"}
sa4ss::read_child("59tables-execsummary.Rmd")
```

<!--chapter:end:50tables.Rmd-->


```{r, warning = FALSE, inclue = FALSE}
landings <- readxl::read_xlsx("./tables/landings.xlsx", sheet = model.area) %>%
  rename(fleet_ID = Fleet) %>%
  mutate(fleet_ID = as.character(fleet_ID))
landings <- inner_join(landings,fleet_info)
landings <- landings %>% 
  mutate(Fleet = paste0(FleetNames, "(",fleet_ID,")")) %>%
  dplyr::select(Year, Fleet, Catch) %>%
  tidyr::pivot_wider(names_from = Fleet, values_from=Catch)  %>%
   mutate(`Total commerical` = rowSums(dplyr::across(`COM_HKL(1)`:`COM_NET(3)`), na.rm=TRUE)) %>%
   mutate(`Total recreational` = rowSums(dplyr::across(`REC_PC(4)`:`REC_PR_DIS(7)`), na.rm=TRUE))  %>%
   mutate(`Total catch` = `Total commerical` + `Total recreational`)

```


```{r, catches, results = 'asis'}
library(kableExtra)
kableExtra::kbl(landings, longtable = TRUE, booktabs = TRUE, 
  caption = "Landings of vermilion fleet and year.",
) %>%
  kableExtra::kable_styling(latex_options = "repeat_header")#, full_width = FALSE)
```

<!--chapter:end:51tables-catch.Rmd-->




<!--chapter:end:52tables-compsamplesize.Rmd-->


```{r, warning = FALSE, inclue = FALSE}
management <- readxl::read_xlsx("./tables/VRML_management_history.xlsx", sheet = "Management")  %>%
  mutate_at(2:12, funs(round(.,2)))
management$Area_landings = c("OFL", "ABC", "Total landings", 
                             "CA rec landings", "OR rec landings", 
                             "WA rec landings","Commercial landings", 
                             "OFL", "ABC", "Total Landings", 
                             "CA rec landings", "Commercial landings")
colnames(management)[1] = ""

```


```{r,management, results = 'asis'}
kableExtra::kbl(management, booktabs = TRUE, 
  caption = "Annual estimates of total mortality, overfishing limit (OFL), acceptable biological catch (ABC), annual catch limit (ACL) for vermilion. The ABC is equal to the ACL.  Data were obtained from the GEMM reports.",
  escape = FALSE) %>%
kableExtra::pack_rows("North of $\\CapeM$", start_row = 1, end_row = 7) %>%
kableExtra::pack_rows("South of $\\CapeM$", start_row = 8, end_row = 12) %>%
  kable_styling(latex_options = "scale_down")
```

<!--chapter:end:59tables-execsummary.Rmd-->


# Figures

Placeholder



<!--chapter:end:60figures.Rmd-->




<!--chapter:end:61figures-data-catches.Rmd-->




<!--chapter:end:62figures-lengths.Rmd-->




<!--chapter:end:63figures-biology.Rmd-->




<!--chapter:end:64figures-selectivity-diagnostics.Rmd-->




<!--chapter:end:65figures-lenfits.Rmd-->

<!-- ======================================================================= -->
<!-- **************************** Time Series ****************************** --> 
<!-- ======================================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc, "plots", "ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning output",
label = 'ssb')
```



```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of relative spawning output",
label = 'depl')
```


<!--chapter:end:66figures-timeseries.Rmd-->




<!--chapter:end:67figures-indices-age.Rmd-->




<!--chapter:end:68figures-recruit-refpoints.Rmd-->

<!-- ======================================================================= -->
<!-- **************************   Sensitivity  ***************************** --> 
<!-- ======================================================================= -->





<!-- ======================================================================= -->
<!-- ************************** Likelihood Profile ************************* --> 
<!-- ======================================================================= -->






<!-- ======================================================================= -->
<!-- *******************     Retrospectives    ***************************** --> 
<!-- ======================================================================= -->


<!--chapter:end:69figures-sens-likeli-retro.Rmd-->


# Appendix

Placeholder


## Annual Length Composition Data
## Detailed Fit to Length Composition Data{#append-fit} 

<!--chapter:end:70appendices.Rmd-->

# Appendix


```{r, results = "asis"}
files_intro <- dir("./indices", pattern = paste0("*", model.area,".md$"), full.names = TRUE)
ignore <- mapply(read_child, files_intro)
```

<!--chapter:end:71indices.Rmd-->

