---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
params:
    model: "north"
preamble: |
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{placeins}
  - \usepackage[inline]{showlabels}
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
lang: en
papersize: a4
---

<!-- Common lat/long 
Cape Mendocino, Pt. Conception and OR border -->
\newcommand\CapeM{$40^\circ 10^\prime N$}
\newcommand\PtC{$34^\circ 27^\prime N$}
\newcommand\CAOR{$42^\circ 00^\prime N$}


```{r, setup, include=FALSE}
rmarkdown::find_pandoc(version = "2.14.0.3")
```


```{r opts, include = FALSE}

library(kableExtra)
library(dplyr)
library(ggplot2)
library(tidyr)
library(rmarkdown)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })
options(knitr.duplicate.label = "allow") #allow duplicate labels - needed for longtable
options(knitr.kable.NA = '') #print blank cells in tables with NA
#knitr::knit_hooks$set(crop = knitr::hook_pdfcrop) #crop figures
#knitr::knit_hooks$set(optipng = knitr::hook_optipng) #optimize figure size


source("C:/Stock_Assessments/VRML_Assessment_2021/GitHub/Vermilion_2021/code/dir_recent.R")
dir.path <- ifelse(params$model=="north",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/NCA/",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/SCA/")
model.dir <- dir_recent(dir = dir.path, pattern = "Verm")
base_loc <- paste0(model.dir,"/")


if (is.null(params$model) & file.exists("00mod.Rdata")) {
  stopifnot(file.exists("00mod.Rdata"))
  load("00mod.Rdata")
} else {
  load(dir(base_loc, pattern = "00mod.Rdata", full.names = TRUE))
}

model.area <- ifelse(params$model=="north", "NCA", "SCA")
spp = 'vermilion rockfish'
Spp = 'Vermilion rockfish'
fig_loc = paste0(getwd(), "/figures")
base_loc_plots = paste0(base_loc,"plots")
table_loc = paste0(getwd(), "/tables/")
tex_tables_loc = paste0(getwd(),"/tex_tables/", params$model)
tex_parent_loc = paste0(getwd(),"/tex_tables/")
#move the tex tables to the parent folder depending on which model you're working on 
#best solution I have so far
files <- list.files(path = tex_tables_loc, full.names = TRUE)
files_new <- gsub(dirname(files[1]), tex_parent_loc, files)
for (i in 1:length(files)){
  file.copy(files[i], files_new[i])
}


# model_loc = "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/"



if(params$model=="north"){
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "Deb Wilson-Vandenberg onboard survey",
                           "West coast groundfish bottomfish trawl survey",
                           "recreational PC onboard survey",
                           "Abrams thesis research survey",
                           "SWFSC groundfish ecology survey",
                           "California Collaborative Fisheries Research Project survey")
} else {
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "NWFSC hook-and-line survey",
                           "West Coast Groundfish Bottomfish Trawl Survey",
                           "recreational PC onboard survey",
                           "CDFW reserach (aka green binder)",
                           "Early years hook-and-line")
}

model$FleetNames_label <- stringr::str_replace_all(model$FleetNames, "_", "-")

fleet_info = data.frame(cbind(model$fleet_ID, model$FleetNames, model$FleetNames_label, model$FleetNames_parsed))
colnames(fleet_info) = c("fleet_ID", "FleetNames", "FleetNames_label", "FleetNames_parsed")

plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))

```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: Melissa H. Monk
    code: 1
    first: M
    middle: H
    family: Monk
  - name: E. J. Dick
    code: 1
    first: E
    middle: J
    family: Dick
  - name: John C. Field
    code: 1
    first: J
    middle: C
    family: Field
  - name: Emma M. Saas
    code: 1
    first: E
    middle: M
    family: Saas
author_list: Monk, M.H., E.J. Dick, J.C. Field, E.M. Saas
affiliation:
  - code: 1
    address: Southwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110
      McAllister Way, Santa Cruz, California 95060
address: ^1^Southwest Fisheries Science Center, U.S. Department of Commerce, National
  Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110 McAllister
  Way, Santa Cruz, California 95060
---

<!--chapter:end:00authorsnorth.Rmd-->

---
bibliography: 
  - sa4ss.bib
---

<!--chapter:end:00bibliography.Rmd-->

---
title: DRAFT The status of Vermilion Rockfish (_Sebastes miniatus_) and Sunset Rockfish (_Sebastes crocotulus_) in U.S. waters off the coast of California north of Pt. Conception in 2021
---

<!--chapter:end:00titlenorth.Rmd-->

\newpage

\includegraphics{cover_photo.png}
Two fish of the vermilion/sunset cryptic species pair.  Confirmation of 
species can only be determined via genetic analysis and species identification 
of these two fish caught in the Santa Barbara channel at approximately 250 ft depth 
is unknown. Photo courtesy of Sabrina Beyer.

<!--
\printnoidxglossary[sort=word]
-->


<!--chapter:end:01a-photo.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}


\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:01a.Rmd-->

# Executive Summary{-}
To be completed after the STAR panel.

## Stock{-}
This assessment reports the status of the vermlion rockfish (_Sebastes miniatus_) 
and sunset rockfish (_Sebastes crocotulus_) complex (referred to as vermilion 
throughout), resource in U.S. waters off the coast of California `r params$model` 
of Point Conception (\PtC) using data 
through 2020.


## Landings{-}
Replace text.

## Data and Assessment{-}
Replace text.

## Stock Biomass{-}
Replace text.

## Recruitment{-}
Replace text.

## Exploitation Status{-}
Replace text.

## Reference Points{-}
Replace text.

## Management Performance{-}
Replace text.

## Unresolved Problems and Major Uncertainties{-}
Replace text.

## Decision Table{-}
Replace text.

## Research and Data Needs{-}
Replace text.

<!--chapter:end:01executive.Rmd-->

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
\setcounter{figure}{0}

<!--chapter:end:10a.Rmd-->

# Introduction
Note to readers: Text in section is the same in both California `r spp` assessment 
documents.

```{r render-12, results = "asis"}
sa4ss::read_child("12basicinfo.Rmd")
```


```{r render-13, results = "asis"}
sa4ss::read_child("13fisheries.Rmd")
```


<!--chapter:end:11introduction.Rmd-->

# Data

The STAT presented proposed analyses and data sources for the 2021 `r spp` 
assessment during the PFMC Pre-Assessment Workshop for 2021 Vermilion and 
Lingcod Stock Assessments, hosted virtually on March 29, 2021. Topics addressed 
included progress on research priorities, data sources and types, stock structure, 
fleet structure, key model parameters (e.g. natural mortality), and potential 
challenges. Descriptions of each data source included in the model 
(Figure \@ref(fig:data-plot)) and sources that were explored, but not included
are included within this section.

## Fishery-Dependent Data

A complete summary of estimated `r spp` removals by each fleet in the 
commercial and recreational fleets modeled in this assessment is provided in Table 
\@ref(tab:landings).  The data sources for landings varied by each fleet and a summary 
of each data source and the time period for which it was used is in Table \@ref(tab:catch-source).
Of note is that the commercial landings are in metric tons (mt) and the recreational landings 
are in numbers of fish (thousands of fish). Data and 
methods used to derive these estimates are described in this section.



```{r render-21, results = "asis"}
sa4ss::read_child("21data-a-commercial.Rmd")
```


```{r render-21b, results = "asis"}
sa4ss::read_child("21data-b-recreational.Rmd")
```



```{r render-21c, results = "asis"}
sa4ss::read_child("21data-c-fishery-independent.Rmd")
```


```{r render-21d, results = "asis"}
sa4ss::read_child("21data-sources-not-used.Rmd")
```



```{r render-2, results = "asis"}
sa4ss::read_child("22biology.Rmd")
```


<!--chapter:end:20data.Rmd-->

# Assessment Model Description

## History of Modeling Approaches

Vermilion was assessed coastwide as a data poor species using 
Depletion-Based Stock Reduction Analysis (DB-SRA) [@Dick2010]. Average catch 
2008-2009 was 136.3 mt, and the median OFL in 2010 was 314.3 mt with a 28% 
probability that recent catch exceeded the 2010 [@Dick2010].

A 2005 assessment was not accepted for management. 
From the September 2005 [Briefing Book](https://www.pcouncil.org/documents/2005/09/f-groundfish-management-september-2005.pdf/): 
"The SSC considers the assessment to be best available science, but at this  stage does not 
endorse the results as being suitable for setting OYs." A 2013 data moderate 
assessment was prepared, but not reviewed. From Pacific Coast Groundfish Stock 
Assessment Review (STAR) Panel Report For Data-Moderate Assessments (2013): 
"There was insufficient time during the review to evaluate all the assessments 
originally requested by the Council. Assessments for vermilion/sunset rockfishes 
(*Sebastes miniatus* and *Sebastes crocotulus*) and yellowtail rockfish 
(south of \CapeM) were not presented by the Stock Assessment Team (STAT)."


### Most Recent STAR Panel and SSC Recommendations 

The 2005 STAR panel report compiled recommendations specific to vermilion, and also 
generic rockfish recommendations The generic rockfish recommendation are not 
presented here.  The 2005 assessment was not accepted for management by the PFMC.

**Vermilion rockfish recommendations**

Investigation into the species composition of nominal vermilion rockfish is needed.
It is not clear that separate assessments for the northern and southern areas are warranted
for vermilion rockfish. Although there were differences in the estimated magnitude and
timing of recruitment events, the estimated stock trends were similar in both areas.
Pooling of data from northern and southern areas may permit a more robust assessment
model to be obtained.

*2021 STAT response.* Since the 2005 assessment, vermilion rockfish were speciated 
to vermilion and sunset rockfishes [@Hyde2009].  Sunset rockfish are more common south of 
Pt. Conception (\PtC) and historical catches and length distributions between 
the two areas are different. The STAT discussed this at the Pre-Assessment workshop 
and all participants agreed that modeling the areas separately was an appropriate 
decision.




```{r render-31, results = "asis"}
sa4ss::read_child("31model-star-responses.Rmd")
```


```{r render-32, results = "asis"}
sa4ss::read_child("32model-description.Rmd") 
```



```{r render-34, results = "asis"}
sa4ss::read_child("34model-prestar-base-selection.Rmd")
```


<!--chapter:end:30model.Rmd-->

# Assessment Results

The base model parameter estimates along with approximate asymptotic standard errors are shown in Table \ref{tab:params} and the likelihood components are shown in Table \@ref(tab:params). Estimates of derived reference points and approximate 95 percent asymptotic confidence intervals are shown in Table \@ref(tab:referenceES). Estimates of stock size and status over time are shown in Table \@ref(tab:timeseries). 

The full r4ss plotting output is available in the supplementary material.

## Parameter Estimates

```{r parameters, include = FALSE, eval = TRUE, cache = TRUE}
# get parameter names from base model
estimated_pars <- model$parameters %>%
  dplyr::filter(!is.na(Active_Cnt)) %>%
  rownames()
```

The base model has a total of `r length(estimated_pars)` estimated parameters
(Figure \@ref(tab:params)) that can be grouped into the following
categories and are described in more detail in the following sections:



Biological parameters  
- 1 natural mortality parameter (female and male assumed the same)  
- 9 growth parameters
    + 6 Schnute growth parameters (length at age 0, length at age 30, and $k$)   
    + 3 parameters controlling variability in growth, the CV in length at age 0  
  and the CV in length at age 30 with a linear ramp in length-at-age  (CV for old males was not estimated


Stock-recruit parameters  
- $log(R_0)$ controlling equilibrium recruitment  
- `r nrow(model$recruit)` recruitment deviations parameters covering the range  
  `r min(model$recruit$Yr)`-`r max(model$recruit$Yr)`, with 
  `r min(model$recruit$Yr[model$recruit$era=="Main"])`-`r max(model$recruit$Yr[model$recruit$era=="Main"])`
  representing the "main" period modeled as a zero-centered deviation vector  
  
Index parameters  
- `r sum(sum(grepl("Q_extra", estimated_pars)))` extra standard deviation parameters
for indices  

Selectivity parameters  
- `r sum(grepl("Size_DblN", estimated_pars))` selectivity parameters, of which
`r sum(grepl("Size_DblN.*BLK", estimated_pars))` represented changes over time  

## Fixed parameters
- $h$ controlling the steepness of the stock-recruit relationship
- $M$ for males
- Selectivity parameters estimated at the bounds during model exploration were fixed in the pre-STAR model

## Growth Estimation
```{r, include=FALSE, echo = FALSE}
# calculate Linf and t0 from Schnute vB parameterization
unSchnute.fn <- function(Amin, Amax, Lmin, Lmax, k)
{
   Linf <- Lmin + (Lmax-Lmin)/(1-exp(-k*(Amax-Amin)))
   t0   <- Amin + Amax - (1/k)*log((exp(k*Amax)*Lmax - exp(k*Amin)*Lmin)/(Lmax-Lmin))
   out  <- c(Linf, t0)
   names(out) <- c("Linf","t0")
   return(out)
}
# vermilion example
# females 
female_growth <- unSchnute.fn(0, 30, model$MGparmAdj$L_at_Amin_Fem_GP_1[1], model$MGparmAdj$L_at_Amax_Fem_GP_1[1], model$MGparmAdj$VonBert_K_Fem_GP_1[1])

if(model.area=="SCA"){
# for males,  apply exponential offsets to the female values
male_growth <- unSchnute.fn(0, 30,  
   model$MGparmAdj$L_at_Amin_Fem_GP_1[1]*exp(model$MGparmAdj$L_at_Amin_Mal_GP_1[1]),     model$MGparmAdj$L_at_Amax_Fem_GP_1[1]*exp(model$MGparmAdj$L_at_Amax_Mal_GP_1[1]),
   model$MGparmAdj$VonBert_K_Fem_GP_1[1]*exp(model$MGparmAdj$VonBert_K_Mal_GP_1[1]))
male_growth[3] <- model$MGparmAdj$VonBert_K_Fem_GP_1[1]*exp(model$MGparmAdj$VonBert_K_Mal_GP_1[1])
} else {

male_growth <- unSchnute.fn(0, 30, 
                            model$MGparmAdj$L_at_Amin_Mal_GP_1[1],
                            model$MGparmAdj$L_at_Amax_Mal_GP_1[1],
                            model$MGparmAdj$VonBert_K_Mal_GP_1[1])
male_growth[3] <- model$MGparmAdj$VonBert_K_Mal_GP_1[1]
}
```



The northern California base model estimated reasonable growth parameters for k and lengths at age 0 and age 30. Internal estimates of growth were estimated directly for both females and males, and not as an offset. An offset for male growth was explored, but the CV of length at $L_{age=30}$ was estimated around 2-3%.  When the male CV was fixed to female CV, the assessment model shrunk the CV of females at $L_{age=30}$, which the STAT did not find reasonable.  Therefore, the male CV at $L_{age=30}$ was fixed at the CV estimated for females of 0.07 (Figure \@ref(fig:fittedgrowth)).

The direct estimation of male  $L_{age=0}=6.02$ cm was reasonable compared to female  $L_{age=0}=7.8$.  While $k$ was estimated  larger for males (0.19) than females (0.15), female $L_{age=30}$  of 55 cm was larger than males at 49 cm.  These results are consistent with other studies that have looked at sex-specific growth in vermilion rockfish.

Estimates of the vonBertalanffy parameters transformed from the Schnute parameterization used by SS are below.  In both parameterizations of the growth equation, the $k$ has the same definition.
\begin{centering}

Females $L_{\infty}$ = `r round(female_growth[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Fem_GP_1[1], 3)`; $t_0$ = `r round(female_growth[2], 2)`

Males $L_{\infty}$ = `r round(male_growth[1])` cm; $k$ = `r round(male_growth[2], 3)`; $t_0$ = `r round(male_growth[2], 2)`

\end{centering}

\vspace{0.5cm}


## Natural Mortality Estimation

The northern California model directly estimates male growth and natural mortality parameters due to the above-mentioned issue with estimation of CVs for length at age 30. Female natural mortality was estimated at 0.089 (SE = 0.009) and male natural mortality was estimated at 0.084 (SE = 0.01), which the STAT considered reasonable given that observed maximum ages for both sexes are similar. Latitudinal gradients in natural mortality have been estimated for many species of rockfish, which is consistent with the higher estimates of M in the southern model.

 

## Fits to Age Composition
The following plots show fits to the conditional age-at-length composition for each 
fleet/survey:   
- WCGBT survey: Figures \ref{fig:comp_condAALfit_residsflt9mkt0_page1} - \ref{fig:comp_condAALfit_residsflt9mkt0_page3}, \ref{fig:comp_condAALfit_data_weighting_TA1.8_condAgeNWFSC_TWL}, and \ref{fig:comp_condAALfit_Andre_plotsflt9mkt0_page1} - \ref{fig:comp_condAALfit_Andre_plotsflt9mkt0_page4}   
- Abrams research survey: Figures \ref{fig:comp_condAALfit_residsflt11mkt0}, \ref{fig:comp_condAALfit_data_weighting_TA1.8_condAgeABRAMS_RESEARCH} and \ref{fig:comp_condAALfit_Andre_plotsflt11mkt0}  
- SWFSC groundfish ecology survey: Figures \ref{fig:comp_condAALfit_residsflt12mkt0} , \ref{fig:comp_condAALfit_data_weighting_TA1.8_condAgeSWFSC_GF_ECOL} and \ref{fig:comp_condAALfit_Andre_plotsflt12mkt0}  
  
Fits to the conditional age at length data sets seemed reasonable, with no evidence of strong residual patterns. The largest residuals were mainly associated with the infrequently encountered, oldest individuals. The model was able to reproduce interannual changes in mean age for the NWFSC trawl and Abrams research data, but tended to slightly overestimate average age (by about 1 year) in three of the four years for the SWFSC GF Ecology data set.


## Estimated Selectivity and Fits to Length Composition
The following plots show estimated selectivity (when not mirrored) and fits to the length composition for each 
fleet/survey:

- Commercial hook-and-line: Figures \ref{fig:endyr-selex-COM-HKL}, \ref{fig:len-pearson-COM-HKL}, and \ref{fig:mean-len-fit-COM-HKL} 
- Commercial trawl: Figures \ref{fig:endyr-selex-COM-TWL}, \ref{fig:len-pearson-COM-TWL}, and \@ref(fig:mean-len-fit-COM-TWL}
- Commercial net: Figures \ref{fig:endyr-selex-COM-NET}, \ref{fig:len-pearson-COM-NET}, and \ref{fig:mean-len-fit-COM-NET}
- Recreational retained PC: Figures \ref{fig:endyr-selex-REC-PC}, \ref{fig:sel03_len_timevary_surf_flt4sex1},  \ref{fig:len-pearson-REC-PC}  and Figure \ref{fig:mean-len-fit-REC-PC} 
- Recreational discard PC Figures \ref{fig:endyr-selex-REC-PC-DIS}, \ref{fig:len-pearson-REC-PC-DIS}  and \ref{fig:mean-len-fit-REC-PC-DIS}
- Recreational retained PR: Figures \ref{fig:endyr-selex-REC-PR}, \ref{fig:sel03_len_timevary_surf_flt6sex1}, \ref{fig:len-pearson-REC-PR} and \ref{fig:mean-len-fit-REC-PR}  
- Deb Wilson-Vandenberg onboard CPFV survey: Figure \ref{fig:len-pearson-DWV-ONBOARD}  and \ref{fig:mean-len-fit-DWV-ONBOARD} 
- WCGBT survey: Figures \ref{fig:endyr-selex-NWFSC-TWL}, \ref{fig:endyr-selex-NWFSC-TWL}, \ref{fig:len-pearson-NWFSC-TWL}  and \ref{fig:mean-len-fit-NWFSC-TWL} 
- Abrams research survey: Figures \ref{fig:len-pearson-ABRAMS-RESEARCH}  and \ref{fig:mean-len-fit-ABRAMS-RESEARCH}  
- SWFSC groundfish ecology survey: Figures \ref{fig:len-pearson-SWFSC-GF-ECOL}  and \ref{fig:mean-len-fit-SWFSC-GF-ECOL}    
- CCFRP: Figures \ref{fig:endyr-selex-CCFRP}, \ref{fig:len-pearson-CCFRP} and Figure \ref{fig:mean-len-fit-CCFRP}  

Fits to the time-aggregated length comps were best for the commercial, recreational, and CCFRP fleets Figure \@ref(fig:lenfits-all). The WCGBT survey does not sample primary adult habitat types, resulting in a length frequency distribution that appears bimodal and is difficult for the model to reproduce Figure \@ref(fig:lenfits-all), and also reflected in the descending limb of the selectivity around 0.42 for any fish larger than 20 cm (Figure \@ref(fig:endyr-selex-NWFSC-TWL)). Fits to the two short-term research fleets (SWFSC GF Ecology and Abrams) are adequate, but ultimately based on mirrored selectivity curves (details in selectivity section, below). Fits to length composition data from the recreational fleets show evidence of modal progressions due to strong year classes (e.g., the 1984-5 year classes entering the fishery a few years later), do not show evidence of strong patterns in the pearson residual plots, and the model is able to track associated changes in mean length over time.

The Abrams research fleet and SWFSC groundfish ecology lengths were mirrored to the commercial hook-and-line fleet, which was fixed to asymptotic selectivity (Figure \@ref(fig:endyr-selex-COM-HKL)).  Initial estimation of the commercial trawl selectivity resulted in large estimates with large standard errors.  Therefore, it was fixed to be asymptotic and the peak size and the ascending width were estimated (Figure \@ref(fig:endyr-selex-COM-TWL)).  The historic net fishery selectivity was well estimated with four parameters and a descending limb; fish were fully selected by around 43 cm and by around 47 cm selectivity decreased to 0.6 (Figure \@ref(fig:endyr-selex-COM-NET)).

All three estimated selectivities for recreational fleets were estimated as domed selectivities (Figures \@ref(fig:endyr-selex-REC-PC), \@ref(fig:endyr-selex-REC-PC-DIS), \@ref(fig:endyr-selex-REC-PR)). A number of regulatory changes in the recreational fleets prompted selectivity time blocks, and both recreational retained fleets estimated a large length at full selectivity in the later time block, from 2017-2020, which was expected due to the relaxation of depth restrictions in areas of higher vermilion density.   The width of the end year selectivity for the recreational PR fleet is wider than that of the PC fleet, which has larger size at peak selectivity.  Peak selectivity of the discard fleet is around 20 cm, and once fish reach 40 cm, they are no longer selected by the discard fleet.  There is no size limit on vermilion rockfish and this is assumed to represent angler preference.

The CCFRP fishes within 150 ft of water to reduce barotrauma-induced mortality and does not observe the larger fish that are seen in the recreational fleets fishing in deeper waters and further offshore (\@ref(endyr-selex-CCFRP). The estimated length composition fits vary by year, with the early years expecting larger fish than were observed and the more recent years (2015-2020) expecting smaller fish, likely from the larger 2013-2014 year classes.



## Fits to Indices
The following plots show log-scale fits to the indices and residuals by fleet/survey:
- MRFSS dockside PC survey: Figures \@ref(fig:log-cpue-REC-PC) and \@ref(fig:cpue-resid-REC-PC)  
- Deb Wilson-Vandenberg onboard CPFV survey: Figures \@ref(fig:log-cpue-DWV-ONBOARD) and \@ref(fig:cpue-resid-DWV-ONBOARD)  
- CDFW/Cal Poly onboard CPFV survey: Figures \@ref(fig:log-cpue-REC-PC-ONBOARD) and \@ref(fig:cpue-resid-REC-PC-ONBOARD)  
- CDFW dockside PR survey: Figures \@ref(fig:log-cpue-REC-PR) and \@ref(fig:cpue-resid-REC-PR)  
- CCFRP survey: Figures \@ref(fig:log-cpue-CCFRP) and \@ref(fig:cpue-resid-CCFRP)  

Fits to the indices vary in quality. Three of the four recreational indices represented the PC fleet, covering the years 1980-2019.
The MRFSS era dockside interview index was fit reasonably well except for the first few years of the index (Figures \@ref(fig:log-cpue-REC-PC) and \@ref(fig:cpue-resid-REC-PC)). The Deb Wilson-Vandenberg onboard survey from 1988-1998 was fairly flat and uninformative, and the model was not able to reproduce a spike in 1990 when an increased CPUE was estimated in the standardized index (Figures \@ref(fig:log-cpue-DWV-ONBOARD) and \@ref(fig:cpue-resid-DWV-ONBOARD)). However, it is unclear whether the increase in CPUE for one year is an artifact of the data or represents an actual short-term increase in abundance. The CDFW and Cal Poly onboard index, which now contains 21 years of data provided an uninformative fit to the data. Both the beginning (1999-2001) and ending (2017-2019) years represent time periods when the fishery had access to deeper water.  Even with selectivity time blocks for these periods, the index was not fit to the decrease in observed CPUE from 1999-2001 or the slight increase from 2017-2019. There is some pattern in the residuals with groups of alternating positive and negative years (Figures \@ref(fig:log-cpue-REC-PC-ONBOARD) and \@ref(fig:cpue-resid-REC-PC-ONBOARD)).
The recreational PR index was not well fit, even with additional error added within the model and residual patterns 
also indicate a poor fit (Figures \@ref(fig:log-cpue-REC-PR) and \@ref(fig:cpue-resid-REC-PR)). Residuals for the 
first part of the survey are positive and negative for the second half of the survey. The only fishery-independent 
index, CCFRP, fit reasonably well to the increasing trend from 2016-2020 (Figures \@ref(fig:log-cpue-CCFRP) and \@ref(fig:cpue-resid-CCFRP)). All of the indices (recreational and CCFRP) indicated an increasing trend from 
2008 to 2010 and then a decrease with lows in all indices  in 2013 that was not fit in any of the indices.  CCFRP 
is the only index sampling within the MPAs, and starting in 2017 the index represents the entire coast.  




## Derived Quantities
Vermilion spawning output in northern California was estimated to be 436 million eggs in 2021 (~95% asymptotic intervals: 222-650; Table \@ref(tab:referenceES), which equates to a depletion level of 39% (~95% asymptotic intervals: 21%-57%; Table \@ref(tab:referenceES); Figure \@ref(fig:depl)) in 2021. Depletion is a ratio of the estimated spawning output in a particular year relative to estimated unfished, equilibrium spawning output. Spawning output north of Point Conception declined rapidly throughout the 1970s, 1980s, and 1990s to a level below the Minimum Stock Size Threshold (MSST), but catches decreased enough in the late 1990s and 2000s for the stock to reach a stable level of spawning output (Table \@ref(tab:timeseries), Figure \@ref(fig:ssb)). Stock size is estimated to have been at the lowest level during the 1990s, but has since increased, in part due to strong recruitments in 1999 and 2016. The stock is estimated to have been below the management target of B40% since the early 1980s (Figure \@ref(fig:depl)), recently returning to levels near the target biomass. Relative exploitation rates [(1-SPR) / (1-SPR50%)] increased through time, exceeding target levels from the 1970s through the 1990s. Exploitation over the past decade has fluctuated around target levels (Figure \@ref(fig:1-spr)), with most catches landed by the recreational sector. In 2021, vermilion biomass north of Point Conception is estimated to be near the target biomass level, while experiencing fishing intensity around the SPR fishing intensity target (Figure \@ref(fig:phase)). The equilibrium yield curve is shifted left, as expected from the Beverton-Holt steepness parameter (h=0.72) (Figures \@ref(fig:yield2) and \@ref(fig:yield3)).


## Recruitment Deviations

Model estimates of recruitment for the 1970-2018 period indicated an extended period of below average recruitment throughout the 1970s and early 1980s, which is generally inconsistent with strong recruitment trends for many years in the 1970s and in 1980 for other species of rockfish.  As this time period is only weakly informed by length data, this may indicate some potential for model misspecification. Major recruitments (strong year classes) estimated in the northern California model include strong 1984, 1985, 1999, and 2016 year classes. (Figures \@ref(fig:recdevs), \@ref(fig:bh-resids) and  \@ref(fig:phase)). These are consistent with estimates of strong year classes in other rockfish stock assessments, nearly all of which suggest very high recruitment in 1999. More recently, strong year classes have been estimated in 2016 for widow rockfish, sablefish and Pacific hake, observations that are consistent with observations of high juvenile rockfish abundance in the California Current during the 2015-2016 large marine heatwave [@Schroeder2019].  Due to ageing error, years adjacent to strong (or weak) cohorts are sometimes estimated as having similar deviations. 



### Reference Points
Reference points were calculated using the estimated selectivities and catch distribution among fleets in the most recent year of the model, `r endyr`. 
Sustainable total yield (landings plus discards) was 
`r round(model$derived_quants[model$derived_quants$Label == 'Dead_Catch_SPR', 'Value'], 2)` mt when using an $SPR_{50\%}$ 
reference harvest rate. The spawning output equivalent to 40% of the unfished level ($SB_{40\%}$) was `r round(model$derived_quants[model$derived_quants$Label == 'SSB_SPR', 'Value'], 2)` 
million eggs. 

The `r endyr`. spawning biomass relative to unfished equilibrium spawning biomass is above the target of 40% of unfished levels (Figure \@ref(fig:depl)). 
The relative fishing intensity, $(1-SPR)/(1-SPR_{50\%})$, was above the management target frogs (Figure \@ref(fig:1-spr)). 

Table \@ref(tab:referenceES) shows the full suite of estimated reference points for the base model and Figures \@ref(fig:yield2) and \@ref(fig:yield3) show the equilibrium curve based on a steepness value fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"], 2)`.


<!--chapter:end:35model-prestar-base-results-north.Rmd-->

# Assessment Model Diagnostics

## Sensitivity to Assumptions, Data and, Weighting

To better understand how data from individual fishery sectors or scientific surveys affected assessment results, we excluded data sets from the likelihood, one fleet at a time (referred to here as a “drop-one” analysis). “Fleet” in this sense refers to either a fishing fleet or a survey “fleet.” To do this, we set “lambdas” (multipliers for each likelihood component) equal to zero. This is equivalent to removing the data from the model. When composition data were excluded, the selectivity parameters for that fleet were fixed at the base model estimates to standardize the size and age composition of harvested fish. When abundance indices were excluded, relevant catchability and ‘extraSE’ parameters associated with the index were not estimated. Composition data weights for the remaining fleets were kept consistent with the base model values. Results from all the ‘drop-one’ runs were compared to the base model using time series plots and tables containing likelihood components, parameter estimates and derived quantities.

```{asis, echo = model.area=='SCA'}
For the southern California model, the NWFSC hook-and-line (HKL) survey is divided across two fleets (8 and 12; see survey description in section \@ref(sec:nwfsc-hook-and-line-survey)). For consistency with other ‘drop-one’ runs, fleets 8 and 12 were excluded at the same time to remove all data associated with the hook-and-line survey. Removal of the HKL survey fleet (index, length comps, and age comps) resulted in larger estimates of unfished spawning output (Figure \@ref(fig:drop-spawnbio)), and affected the trend in spawning biomass in recent years. Only removal of the REC_PC fleet had a noticeable effect on spawning output in the terminal year, but the difference was well within the estimated range of uncertainty from the base model. Relative spawning output (‘depletion’) estimates showed little change relative to the range of plausible outcomes predicted by the base model (Figure \@ref(fig:drop-bratio)). Removal of the REC_PC fleet reduced the magnitude of negative recruitment deviations estimated in the 1970s, as well as the strength of the 1999 year class (Figure \@ref(fig:drop-recdev)), but most general patterns in recruitment were consistent across the set of drop-one sensitivity tests. Changes in likelihoods, parameter estimates and derived quantities are recorded in Tables \@ref(tab:drop-one) and \@ref(tab:drop-one2). Comparison of likelihoods among drop-one scenarios should be treated with caution due to changes in the data sets that were fit in each model run.
```

```{asis, echo = model.area=='NCA'}
Drop-one analysis of the northern California assessment revealed slightly larger variability in spawning output trends relative to the south, but all runs were still within the range of uncertainty estimated by the base model (Figure \@ref(fig:drop-spawnbio)). Removal of most fleets had little effect on terminal stock status, with best estimates in the vicinity of target biomass levels (Figure \@ref(fig:drop-bratio)). An exception was removal of the REC_PC fleet, which caused the best estimate of terminal depletion to drop just above the minimum stock size threshold. This suggests that the REC_PC data sets, together, favor a less-depleted stock relative to data from the other fleets. The strength of the 2016 year class is sensitive to the removal of fleet-specific data sets (Figure \@ref(fig:drop-recdev)). Removal of the REC_PR fleet produces the largest estimates of 2016 cohort size, and removal of the NWFSC_TWL fleet estimates a 2016 deviation that is less than half as large (but still positive). Uncertainty in the strength of this recent year class should be taken into consideration for short term forecasts of stock abundance and yield. Changes in likelihoods, parameter estimates and derived quantities are recorded in Table \@ref(tab:drop-one). Comparison of likelihoods among drop-one scenarios should be treated with caution due to changes in the data sets that were fit in each model run.
```



## Likelihood Profiles

Likelihood profiles were conducted for natural mortality (M), steepness (h) and the log of R0 (unfished recruitment) by fixing these parameters across a range of values and continuing to estimate the remaining parameters assuming the base model framework.  

```{asis, echo = model.area=='SCA'}
The profiles for natural mortality in the southern base model (Figures \@ref(fig:m-profile), \@ref(fig:m-depl), and \@ref(fig:m-spawn)) suggest that this parameter is reasonably well informed between a range of approximately 0.11 and 0.14.  The profiles suggest a somewhat commonly observed phenomena of tension between the age data, which would suggest a lower natural mortality rate, and the length and index data, which tend to fit the data better with a higher value for M.  The notable exceptions to these generalizations include the NWFSC hook and line survey index, which fits the data better with a considerably lower M, and the commercial fisheries data (hook and line, and setnet), which also fit the data better with a lower M.  Intuitively, spawning output increased with lower natural mortality rate estimates, while the estimate of relative stock status was more pessimistic, while the converse was true (lower spawning output, more optimistic stock status estimates) with higher M values. 

A profile of steepness was conducted on values ranging from 0.30 to 0.90 in 0.10 increments.  The resulting likelihood profiles (by component, and by component and fleet) are shown as Figure \@ref(fig:h-profile), while model trajectories (spawning output and relative depletion) are shown as Figures \@ref(fig:h-depl), and \@ref(fig:h-spawn).  The likelihood profiles show that the overall best fit to the data is associated with high steepness values, although the data were generally uninformative above steepness values of 0.5.  Overall the length data were not very informative, and there were some odd changes in the likelihood in some fleets at very low (0.3) steepness values.  Similarly the age data were only marginally informative, and suggested higher steepness values in general.  Most of the indices also suggested higher steepness values, particularly the NWFSC hook and line survey index, although the Rec PC index had a significantly better fit at lower steepness values.  Predictably, spawning output scaled down with higher steepness values and up with lower values, however the estimate of stock status in 2021 varied relatively little across the range of values.  Interestingly the most optimistic runs with respect to relative stock status were both the highest and the lowest values in the profile, although the overall difference was negligible for the ending year. The higher steepness runs were more pessimistic with respect to historical (late 1980s through the early 2000s) stock status.  
 
A profile on the log of unfished recruitment (Ln R0) was conducted on values ranging from 6.2 to 6.9 (the base model estimate in base model was 6.66).  In general, age data was better fit by the model with lower values of R0, survey data (as well as recruitment via likelihood penalties) were better fit by higher R0 values, and the cumulative fit to length data was best close to the base model estimate (Figure \@ref(fig:r0-profile)).  The components by fleet were variable in the cases of length composition data, in which the commercial hook and line fishery and the Rec PC data fit better with lower R0 values, while the remaining fleets fit better with higher R0 values or were non-informative (Figures \@ref(fig:r0-depl) and \@ref(fig:r0-spawn)).  Counterintuitively, spawning output is estimated to be greater with the higher R0 values and lower with the lower R0 values, as a result of corresponding model changes in the estimate of the natural mortality rate (which is estimated to be much lower in the low R0 model).  This results in the lower R0 runs also being more pessimistic, as the lower R0 runs were associated with considerably lower natural mortality rates.  Additional profiles in which M is fixed may be helpful in evaluating model performance across many of the key model parameters.
```

```{asis, echo = model.area=='NCA'}
The profiles for natural mortality in the northern model (Figures \@ref(fig:m-profile), \@ref(fig:m-depl), and \@ref(fig:m-spawn)) suggest that this parameter is reasonably well informed between a range of approximately 0.07 and 0.11, a somewhat lower range of values than was estimated for the southern model.  Interestingly, profiles for natural mortality in the north indicated that the length data were better fit by the model with a lower natural mortality rate, and the age data were better fit by a higher rate, a result that is in contrast to that observed in the southern model.  Most of the indices were also better fit by a higher natural mortality rate, although the Deb Wilson-Vandenberg Index and the onboard observer index were better fit with lower natural mortality rates.  As is typical, spawning output increased with decreasing natural mortality, such that the model estimate with M = 0.05 was 1.5 times that of the model estimate when M was assumed to be 0.12. Similarly, the model estimated depletion in 2020 was well above the target level, close to 70%, for the M=0.12 model, while the ending depletion was just barely over the minimum stock size threshold of 25% of the unfished level in the M=0.05 model (Figure \@ref(fig:m-depl)).  

A profile of steepness was conducted on values ranging from 0.30 to 0.90 in 0.10 increments.  The likelihood profiles (by component, and by component and fleet) are shown as  Figure \@ref(fig:h-profile), and the resulting model trajectories (spawning output and relative depletion) are shown as Figures \@ref(fig:h-spawn) and \@ref(fig:h-depl).  The likelihood profiles show that the overall best fit to the data is associated with high steepness values, although the data were generally uninformative above steepness values of 0.5.  Overall the length data were not very informative, and there was some odd jumps in the likelihood in some fleets at very low (0.3) steepness values.  Similarly the age data were only marginally informative, and suggested higher steepness values in general.  Most of the indices also suggested higher steepness values, particularly the NWFSC hook and line survey index, although the Rec PC index had a significantly better fit at lower steepness values.  Predictably, spawning output scaled down with higher steepness values and up with lower values, however the estimate of stock status in 2021 was actually more optimistic with lower steepness values and more pessimistic with higher steepness values.  The higher steepness runs were also more pessimistic with respect to historical (late 1980s through the early 2000s) stock status.       

A profile on the log of unfished recruitment was conducted on values ranging from 5.7 to 6.4 (the base model estimate was 6.07), and is shown as Figure \@ref(fig:r0-profile).  In general, age data was better fit by the model with higher values of R0, as was most of the survey data (as well as recruitment via likelihood penalties).  The DWV_onboard survey index and the Rec_PR were both somewhat better fit by the lower R0 values. All length data were either better fit to lower R0 values or were uninformative.  As with the southern model, spawning output is estimated to be greater with the higher R0 values, although the overall difference in scaling was minimal for early years.  Also consistent with the southern model result, the northern model result was more pessimistic with the lower R0 values, with the low R0 values being below the MSST and higher R0 values suggesting that relative spawning output is well above target levels (Figures \@ref(fig:r0-depl) and \@ref(fig:r0-spawn)). As with the southern model, this is a result of corresponding model changes in the estimate of the natural mortality rate (which is estimated to be much lower in the low R0 model), such that the R0 profile is in many ways simply providing the same information as the profile on the natural mortality rate.  Additional profiles in which M is fixed may be helpful in evaluating model performance.
```



## Retrospective Analysis
```{asis, echo = model.area=='SCA'}
A five year retrospective analysis was conducted on the southern base model by sequentially removing data, beginning with data from the year 2020.  Figures \@ref(fig:retro-spawnb), \@ref(fig:retro-bratio), and \@ref(fig:retro-recdev) show the estimated spawning output, the estimated depletion, the recruitment deviation estimates and the estimated fit to the NWFSC hook and line survey index (which appeared to be the index fit most affected by the analysis).  The greatest impact was the declining estimate of the strength of the 2016 year class, similar to the northern model, with the interesting result that with the loss of only 1-3 years of data the model attributes greater recruitment to 2015 relative to the base model, with variable responses among other recruitment estimates.  This change is associated with an increasingly pessimistic perception of stock status, although the overall scaling of spawning output is relatively modest.  This shift is understandably associated with the change in population trajectory as data supporting strong recent recruitment are removed.  Beyond this shift, this analysis does not suggest that there are substantive retrospective patterns (Table \@ref(tab:retro)).  Note that data weighting was not conducted on these models.
```


```{asis, echo = model.area=='NCA'}
A five year retrospective analysis was conducted on the northern base model by sequentially removing data, beginning with data from the year 2020.  Figures \@ref(fig:retro-spawnb), \@ref(fig:retro-bratio), and \@ref(fig:retro-recdev) show the estimated spawning output, the estimated depletion, the recruitment deviation estimates and the estimated fit to the CCFRP index (which was the index most affected by the analysis).  The greatest impact of sequentially removing recent data was the declining estimate of the strength of the 2016 year class, a result similar to the southern model, as the length composition and index data that informed those year classes were removed.  There was also a slightly lesser reduction in the strength of the 2013 and 2014 year classes.  However, aside from a modest rescaling upwards of recruitment deviations, the spawning output and depletion estimates did not change by any significant measure, suggesting no concerning retrospective patterns (Table \@ref(tab:retro)).  Note that data weighting was not conducted on these models. 
```


## Other Model Sensitivities
Results from the pre-STAR base model were compared to several alternative model specifications, as described below.

- Estimate the Beverton-Holt steepness parameter (*h*) rather than fixing it at the prior mean (*h*=0.72); estimate uncertainty intervals for comparison to base
- Start recruitment deviations 5 years earlier than the base model configuration
- Start recruitment deviations 5 years later than the base model configuration
- Compare results based on the McAllister-Ianelli data weighting method (for composition data) to the Francis method used for the base model.
- Mirror the recreational discard fleets’ selectivity curves to the corresponding retained fleets (PC or PR) rather than fitting to discard length comps as in the base model.


```{asis, echo = model.area=='NCA'}
Trends in spawning output for the northern California assessment model were generally robust to this set of sensitivities (Figure \@ref(fig:sens1-spawnb)). Best estimates from all runs were within the estimated range of uncertainty for the base model. Steepness was estimated at a higher value than the prior mean (estimated at 0.94 vs. fixed at 0.72). Similarly, stock status did not vary greatly among this set of sensitivity runs, with only a minor increase in 2021 relative spawning output when using McAllister-Ianelli weights and a slight decrease when estimating steepness (Figure \@ref(fig:sens1-bratio)). The use of McAllister-Ianelli weights had the greatest impact on estimated recruitment deviations (Figure \@ref(fig:sens1-recdev)). This weighting method significantly reduced the magnitude of the 2016 year class, and generally increased the variance of the estimated deviations. The McAllister-Ianelli method gives greater weight to the composition data for this model (Table \@ref(tab:sens1)), and resulted in lower estimates of the male and female natural mortality rates (Table \@ref(tab:data-weights)).
```


```{asis, echo = model.area=='SCA'}
Trends in spawning output for the southern California assessment model were generally robust to this set of sensitivities, with the exception of recent estimates of spawning output which were much lower when using McAllister-Ianelli data weights, relative to the Francis method used in the base model (Figure \@ref(fig:sens1-spawnb)). The model tuned to McAllister-Ianelli weights was below target biomass, while the other models that used Francis weights showed similar trends in depletion and were above target biomass (Figure \@ref(fig:sens1-bratio)). The McAllister-Ianelli approach estimated a natural mortality rate that was about 20% lower than the Francis method (Tables \@ref(tab:drop-one) and \@ref(tab:drop-one2)). Best estimates from all runs were within the estimated range of uncertainty for the base model. Steepness in the southern region was estimated at a similar value than the prior mean (estimated at 0.77 vs. fixed at 0.72), and estimation of this parameter did not have a large effect on uncertainty in spawning output or recruitment deviations. The use of McAllister-Ianelli weights had the greatest impact on estimated recruitment deviations (Figure \@ref(fig:sens1-recdev)). This weighting method increased the variance of the estimated deviations as well as the estimated strength of the 1999 year class, relative to the models using the Francis approach. Changing the start date of the recruitment deviations had almost no effect. The McAllister-Ianelli method gives greater weight to the composition data for this model (Table \@ref(tab:sens1)).
```

## Unresolved Problems and Major Uncertainties


<!--chapter:end:36model-uncertainty.Rmd-->

# Harvest Projections and Decision Tables

**This section will be completed after the STAR panel**
<!--
Projections of OFL (mt), ABC (mt), age 10+ biomass (mt), spawning output (billions of eggs), and depletion (% of unfished spawning output) are shown for the default harvest control rule in Table 62. Catch estimates for 2021 and 2022 are based on GMT recommendations (M. Mandrup, CDFW; pers. comm.), with frog mt for commercial and frog mt for recreational fleets. Projections assume a constant allocation among fleets equal to the recommended catch for 2021 and 2022 (frog% commercial, frog% commercial).
-->

## Regional Management and Spatial Management Considerations

Over the last several decades, spatially explicit management measures at both the state and federal/management council level have been implemented to achieve a wide range of marine resource and fishery management objectives. Depth restrictions to commercial and recreational fisheries in the Rockfish Conservation Areas (RCAs) and the Cowcod Conservation Areas (CCAs) are key among those, as are the suite of total and partial exclusion of commercial and recreational fishing activities in the California statewide network of Marine Protected Areas (MPAs). While the former are associated with explicit fisheries management objectives, the latter have a suite of ecological and economic objectives, most of which are not specific to, nor integrated across, the fisheries management arena. Despite this, both types of spatial management measures are expected to result in various biological, ecological, and socioeconomic effects within and adjacent to their boundaries.  All of these effects have the potential to influence the nature and quality of the data used to inform stock assessments of species that reside in these areas, including vermilion rockfish.

Regardless of the management objective, spatial closures are expected to increase the spatial heterogeneity in abundance and size or age structure of fished stocks. This greater spatial variability can complicate the assumptions made in stock assessment models, particularly the assumption that the densities and demographic structure of assessed populations are relatively homogeneous, at least across predictable habitat types such as bathymetric gradients or substrate types [@Punt2004; @Field2007; @Berger2017].  Although a wide range of factors above and beyond spatial management measures can also lead to violations of those assumptions, and the challenge is intuitively less problematic for populations with high movement rates and/or high population turnover, the challenge can be particularly important for longer lived populations with lower movement rates.  The challenge can best be summarized by the result that the more effective MPAs or other closed areas are at protecting populations within them, the more likely it is that traditional assessment approaches will be biased or more uncertain.  

If the spatial closures also prevent fisheries independent surveys from evaluating the relative abundance and demographic structure of managed populations, the challenges in developing robust population models, and thus robust management advice, become even more severe.  While spatially explicit assessment models provide a means of more explicitly addressing these challenges, such models are computationally intensive, require robust data from the specific areas being modeled, and may also require detailed information regarding movement and dispersal rates [@McGilliard2015; @Berger2017; @Punt2020; @Cadrin2020].  Moreover, the complexity of these spatial models increases substantially if the size and location of closed areas changes over time, as many of the more “fisheries management based” closures (e.g., RCAs) have in California groundfish fisheries.  Thus, such approaches may be less feasible for more data limited stocks, such as northern and southern vermilion rockfish, at least in the near term.  However, the fact that both the northern and southern assessment models are informed by fishery-independent surveys that include habitats both inside and outside area closures provides some hope for greater recognition of spatial factors in future assessments.  



# Unresolved Problems and Major Uncertainties
We recommend the following research be conducted before the next assessment:

- Investigate the structure of complex and contribution of each species to the 
vermilion/sunset complex. Investigate possible spatial differences in biological parameters within 
a single species and also between the two species.  Little biological data for south of 
Point Conception or north of Point Arena were available for this assessment and is needed 
to better under biological parameters. 
  + Conduct life history studies
  + Conduct research to identify the proportion of each species in population and in catches

- Take a closer look at the Ralston historical catch reconstruction (\ref{Ralston2010}) and 
all other historical data sources.

- Refine CCFRP survey index to look at alternative possible model structures, including 
a hierarchical structure and random effects. The CCFRP survey is the only 
fishery-independent survey available for nearshore rockfish sampling the nearshore rocky 
reef habitats. As of this assessment, only two years of coastwide data are available, 
and the index was limited to the site in central California that have been monitored 
since 2007.

- Continue to investigate the most appropriate model structure for the NWFSC HL survey index.
The NWFSC HL survey is the only long-term fishery-independent survey in rocky (untrawlable) habitat 
in the Southern California Bight. We also recommend evaluating how to structure the NWFSC Hook-and-Line survey index given its expansion into the CCA, also independent analysis of information content in NWFSC Hook-and-Line survey.Increased spatiotemporal sampling around Pt. Conception would aid in identifying stock boundaries.

- Utilize existing ROV survey data sources
  + SWFSC Submersible Survey of the Cowcod Conservation Areas [@Yoklavich2007]. 
  +  This was a line-transect survey designed to estimate cowcod abundance in 2002 
  conducted from a submersible inside the CCAs.  Originally, only cowcod were enumerated from the video footage.  Over the last few years, the SWFSC has re-analyzed the video footage to enumerate other rockfish species. 
    + The SWFSC Fishery Resource Division (FRD) conducted a survey of potential cowcod habitat between Point Conception and the U.S. – Mexico border from October through December of 2012 [@Stierhoff2013].
    +  SWFSC staff are submitting proposals to conduct an additional submersible survey in the southern California Bight
    + CDFW ROV survey data


- Collection of length and age data are recommended for both the commercial and 
recreational fisheries.  Very little age data are available from either fishery for 
vermilion and sunset rockfishes.

- Investigate possible environmental drivers/co-variates for biological parameters, 
particularly for recruitment.

- Resolve differences between CalCOM and PacFIN expanded length composition data sets. 




<!--chapter:end:40management.Rmd-->

\clearpage

# Acknowledgments (not required for draft assessments)

<!--chapter:end:41acknowledgements.Rmd-->

\clearpage
\floatplacement{table}{H}

# Tables

```{r render-51, results = "asis"}
sa4ss::read_child("51tables-execsummary.Rmd")
```

```{r render-52, results = "asis"}
sa4ss::read_child("52tables-catch.Rmd")
```


```{r render-54, results = "asis"}
sa4ss::read_child("54tables-compsamplesize.Rmd")
```

```{r render-56, results = "asis"}
sa4ss::read_child("56tables-results.Rmd")
```


```{r render-57, results = "asis"}
sa4ss::read_child("57tables-uncertainty.Rmd")
```

<!--chapter:end:50tables.Rmd-->

\clearpage
# Figures


```{r render-61, results = "asis"}
sa4ss::read_child("61figures-data-catches.Rmd")
```


```{r render-62, results = "asis"}
sa4ss::read_child("62figures-lengths.Rmd")
```


```{r render-63, results = "asis"}
sa4ss::read_child("63figures-biology.Rmd")
```

\FloatBarrier

```{r render-64, results = "asis"}
sa4ss::read_child("64figures-selectivity-diagnostics.Rmd")
```

\clearpage
\FloatBarrier


```{r render-65, results = "asis"}
sa4ss::read_child("65figures-lenfits.Rmd")
```



\FloatBarrier

```{r render-67, results = "asis"}
sa4ss::read_child("67figures-indices-age.Rmd")
```


\FloatBarrier

```{r render-68, results = "asis"}
sa4ss::read_child("68figures-timeseries.Rmd")
```

\FloatBarrier

```{r render-68a, results = "asis"}
sa4ss::read_child("68a-figures-recruit-refpoints.Rmd")
```

\FloatBarrier

```{r render-69, results = "asis"}
#if(model.area=="NCA"){
sa4ss::read_child("69figures-sens-likeli-retro.Rmd")
# } else {
#   sa4ss::read_child("69figures-sens-likeli-retro-south.Rmd")
# }
```

<!--chapter:end:60figures.Rmd-->

\clearpage

# Appendix



## MRFSS Dockside Index of Abundance {#mrfss-index}

```{r mrfss-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_NCA.md") 
```
  
\clearpage

## California Onboard CPFV Index of Abundance {#cpfv-index}
 
```{r ca-cpfv-onboard-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_NCA.md") 
``` 

\clearpage 

## Deb Wilson-Vandenberg Onboard CPFV Index of Abundance {#debwv-index}

```{r devwv-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_DebWV_onboard_writeup_NCA.md") 
``` 

\clearpage


## CRFS PR Dockside Index of Abundance {#pr-index}

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_NCA.md")
``` 

\clearpage

## CCFRP Index of Abundance {#ccfrp-index}

```{r ccfrp-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CCFRP_writeup_NCA.md") 
``` 

\clearpage

## WCGBTS Index of Abundance {#wcgbts-index}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_NCA.md")
``` 

\clearpage

## Recreational Regulations {#regs-graphic}

```{r rec-regs, results = 'asis'}
  sa4ss::read_child("70appendices-regs.Rmd")
``` 

\clearpage 

# References


<!--chapter:end:70appendices-north.Rmd-->

