---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
params:
    model: "north"
preamble: |
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{placeins}
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
lang: en
papersize: a4
csl: CJFAS.csl
---

<!-- Common lat/long 
Cape Mendocino, Pt. Conception and OR border -->
\newcommand\CapeM{$40^\circ 10^\prime N$}
\newcommand\PtC{$34^\circ 27^\prime N$}
\newcommand\CAOR{$42^\circ 00^\prime N$}



```{r opts, include = FALSE}
library(kableExtra)
library(dplyr)
library(ggplot2)
library(tidyr)
library(rmarkdown)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })
options(knitr.duplicate.label = "allow") #allow duplicate labels - needed for longtable
options(knitr.kable.NA = '') #print blank cells in tables with NA
#knitr::knit_hooks$set(crop = knitr::hook_pdfcrop) #crop figures
#knitr::knit_hooks$set(optipng = knitr::hook_optipng) #optimize figure size


source("C:/Stock_Assessments/VRML_Assessment_2021/GitHub/Vermilion_2021/code/dir_recent.R")
dir.path <- ifelse(params$model=="north",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/NCA/",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/SCA/")
model.dir <- dir_recent(dir = dir.path, pattern = "Verm")
base_loc <- paste0(model.dir,"/")


if (is.null(params$model) & file.exists("00mod.Rdata")) {
  stopifnot(file.exists("00mod.Rdata"))
  load("00mod.Rdata")
} else {
  load(dir(base_loc, pattern = "00mod.Rdata", full.names = TRUE))
}

model.area <- ifelse(params$model=="north", "NCA", "SCA")
spp = 'vermilion rockfish'
Spp = 'Vermilion rockfish'
fig_loc = paste0(getwd(), "/figures")
base_loc_plots = paste0(base_loc,"plots")
table_loc = paste0(getwd(), "/tables/")
#exec table folder that is now really the csv files, but not changing th name
exec_tables_loc = paste0(getwd(),"/exec_tables/", params$model,"/")
#tex_parent_loc = paste0(getwd(),"/tex_tables/")
#move the tex tables to the parent folder depending on which model you're working on 
#best solution I have so far
# files <- list.files(path = tex_tables_loc, full.names = TRUE)
# files_new <- gsub(dirname(files[1]), tex_parent_loc, files)
# for (i in 1:length(files)){
#   file.copy(files[i], files_new[i])
# }


# model_loc = "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/"


#give fleets each a full name
if(params$model=="north"){
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "Deb Wilson-Vandenberg onboard survey",
                           "West coast groundfish bottomfish trawl survey",
                           "recreational PC onboard survey",
                           "Abrams thesis research survey",
                           "SWFSC groundfish ecology survey",
                           "California Collaborative Fisheries Research Project survey")
} else {
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "NWFSC hook-and-line survey",
                           "West Coast Groundfish Bottomfish Trawl Survey",
                           "recreational PC onboard survey",
                           "CDFW reserach (aka green binder) survey",
                           "Early years hook-and-line")
}


#Give fleets a designation
#give fleets each a full name
if(params$model=="north"){
model$FleetType <- c("com","com","com",
                     "rec","rec", "rec","rec",
                     "rec",
                     "fi", #fishery-independent
                     "rec",
                     "fi",
                     "fi",
                     "fi")
} else {
model$FleetType <- c("com","com","com",
                     "rec","rec", "rec","rec",
                     "fi",
                     "fi",
                     "rec",
                     "fi",
                     "fi")
}
#create a fleet info table
model$FleetNames_label <- stringr::str_replace_all(model$FleetNames, "_", "-")

fleet_info = data.frame(cbind(model$fleet_ID, model$FleetNames, model$FleetNames_label, model$FleetNames_parsed, model$FleetType))
colnames(fleet_info) = c("fleet_ID", "FleetNames", "FleetNames_label", "FleetNames_parsed", "FleetType")
fleet_info$fleet_ID = as.numeric(fleet_info$fleet_ID)

plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: Melissa H. Monk
    code: 1
    first: M
    middle: H
    family: Monk
  - name: E. J. Dick
    code: 1
    first: E
    middle: J
    family: Dick
  - name: John C. Field
    code: 1
    first: J
    middle: C
    family: Field
  - name: Emma M. Saas
    code: 2
    first: E
    middle: M
    family: Saas
  - name: Tanya L. Rogers
    code: 1
    first: T
    middle: L
    family: Rogers
author_list: Monk, M.H., E.J. Dick, J.C. Field, E.M. Saas, T.L. Rogers
affiliation:
  - code: 1
    address: Southwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110
      McAllister Way, Santa Cruz, California 95060
  - code: 2
    address: Fisheries Collaborative Program, Insitute of Marine Sciences, University of California,         Santa Cruz, 110 McAllister Way, Santa Cruz, California 95060
address: 
  - ^1^Southwest Fisheries Science Center, U.S. Department of Commerce, National
    Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110 McAllister
    Way, Santa Cruz, California 95060
  - ^2^Fisheries Collaborative Program, Insitute of Marine Sciences, University of California, Santa     Cruz, 110 McAllister Way, Santa Cruz, California 95060
  
---

<!--chapter:end:00authorsnorth.Rmd-->

---
bibliography: 
  - sa4ss.bib
---

<!--chapter:end:00bibliography.Rmd-->

---
title: DRAFT The status of Vermilion Rockfish (_Sebastes miniatus_) and Sunset Rockfish (_Sebastes crocotulus_) in U.S. waters off the coast of California north of Pt. Conception in 2021
---

<!--chapter:end:00titlenorth.Rmd-->

\newpage

\includegraphics{cover_photo.png}
Two fish of the vermilion/sunset cryptic species pair.  Confirmation of 
species can only be determined via genetic analysis and species identification 
of these two fish caught in the Santa Barbara channel at approximately 250 ft depth 
is unknown. Photo courtesy of Sabrina Beyer.

<!--
\printnoidxglossary[sort=word]
-->


<!--chapter:end:01a-photo.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}


\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:01a.Rmd-->

# Executive Summary{-}


## Stock

This assessment reports the status of the vermlion rockfish (_Sebastes miniatus_) 
and sunset rockfish (_Sebastes crocotulus_) complex (referred to as vermilion rockfish 
throughout), resource in U.S. waters off the coast of California `r params$model` 
of Point Conception (\PtC) using data through 2020. Genetic evidence suggests 
a mixture of the two species with the majority of thee sunset rockfish population 
south of Point Conception. Alternative spatial structures for the vermilion rockfish 
assessment should be assessed if additional data on stock structure and the distribution 
of the two species become available.


## Catches{-}

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Pull some summary values to use in the text

#Sum the total catch 
Tot.catch <- model$catch %>%
  group_by(Yr) %>%
  summarise(Catch = sum(ret_bio)) 

# 5 years with highest catch  
max.catch.5 <- Tot.catch %>% top_n(5, Catch)

#Recent catches 
Tot.catch.recent <- Tot.catch %>% filter(Yr>2010)
```

Over the past decade, vermilion rockfish off the coast of California have been 
primarily caught by the recreational fishery (Table \@ref(tab:removalsES)). 
Annual total landings of catch and discards of `r spp` have ranged between 
`r paste0( min(round(Tot.catch.recent$Catch,0)), '-', max(round(Tot.catch.recent$Catch, 0)))` 
mt, with landings (catch + discards) in `r model$endyr` totaling `r round(Tot.catch.recent$Catch[Tot.catch.recent$Yr==model$endyr] ,0)` mt. 
Vermilion and sunset rockfishes landings from all sectors have historically been recorded as 
“vermilion rockfish” and recreational sampling in California currently does not 
differentiate between the two species.

Recreational removals in California prior to 2004 were only estimated at large 
spatial scales (north and south of Point Conception) following the design of 
the Marine Recreational Fisheries Statistics Survey (MRFSS). Recent sampling 
(2004 – present) by the California Recreational Fisheries Survey (CRFS) produces 
estimates of vermilion landings and discard at a finer spatial resolution. Total 
removals `r params$model` of Point Conception increased steadily following World 
War II, peaking in the late 1970s and early 1980s with annual removals exceeding 
`r round(max(Tot.catch$Catch), 0)` mt per year (Figure \@ref(fig:catch)). Recent 
years have seen a steady increase in landings, but total removals remain low 
relative to historical levels.

\FloatBarrier

```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc_plots, "catch2 landings stacked.png"), 
caption = "Catch histories by fleet used in the base model",
label = 'catch')
```


```{r,echo=FALSE, warning=FALSE, message=FALSE}
removals <- read.csv(paste0(exec_tables_loc,'a_Catches_ES.csv')) %>%
  mutate_at(c(-1), round,3) %>%
  rename(`Total Landings` = Total.Landings)
colnames(removals) = gsub("_","-",colnames(removals))
```

```{r, results = 'asis'}
kableExtra::kbl(removals,
                booktabs=TRUE,
                caption="Recent landings by fleet, total landings summed across 
                fleets, and the total mortality including discards.",
                label="removalsES",
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))
```


\FloatBarrier

## Data and Assessment{-}

This is the first full stock assessment for vermilion and sunset rockfishes. 
A full assessment was attempted in 2005, but not accepted for management and a 
data moderate assessment in 2013 was not reviewed.  The 2021 assessment uses 
Stock Synthesis 3 (version V3.30.17.0). The assessment is a two sex model, with 
the population spanning from Point Conception to the California/Oregon border. 
The assessment model operates on an annual time step covering the period 1875 to 
2020 (not including forecast years) and assumed an unfished 
population prior to 1875. Population dynamics are modeled for ages 0 through 70, 
with age-70 being the accumulator age.  

The model is conditioned on catch from two sectors (commercial and recreational) 
divided among seven fleets, and is informed by five abundance indices 
(one fishery-independent survey, two CPUE indices from shore-based sampling programs, 
and two CPUE indices from onboard observer programs).  Discards for the commercial 
fleet are not included in the model. Commercial discards of vermilion are a small 
fraction of the total mortality and data on commercial discard length composition is
limited. The recreational fishery is split into four fleets, one discard and one 
retained fish fleet each for the private/rental and the party/charter boat modes.

The assessment estimates parameters for natural mortality of females and males, 
steepness of the Beverton-Holt stock-recruitment relationship, and sex-specific 
growth parameters. Year class strength is estimated as deviations from the expected 
stock-recruitment relationship beginning in 1965.

The assessment estimates parameters for natural mortality of females and males 
and sex-specific growth parameters. Year class strength is estimated as deviations 
from the expected stock-recruitment relationship beginning in 1965. Steepness of 
the Beverton-Holt stock-recruitment relationship is fixed at the mean of the prior, 
0.72. A number of sources of uncertainty are addressed in this assessment. This 
assessment includes length data, estimated growth, an updated length-weight curve, 
an updated maturity curve, a number of new indices, and new conditional age-at-length data.  

\FloatBarrier

## Stock Biomass{-}

```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Read in table to use values in the text and print the table below
ssb <- read.csv(paste0(exec_tables_loc,'b_SSB_ES.csv')) %>%
  mutate_at(c(-1), round,3) 
```


Spawning output of vermilion rockfish was estimated to be `r round(ssb$Spawning.Output[ssb$Year==model$endyr],0)` million eggs in 2021 or `r scales::percent(ssb$Fraction.Unfished[ssb$Year==model$endyr], accuracy = 1)` of 
unfished spawning output (“depletion,” Table \@ref(tab:ssbES)). Depletion is a 
ratio of the estimated spawning output in a particular year relative to estimated 
unfished, equilibrium spawning output. 

```{asis, echo = model.area=='NCA'}
In northern California, spawning output declined rapidly in the 1970s and early 1980s, falling below the minimum stock size threshold for a number of years in the 1990sa dn early 2000s, followed by a steady recovery since the late 2000s (Figures \@ref(fig:ssbES) and \@ref(fig:deplES)). The trend in spawning output in 2020 is just above the management target (40% of unfished spawning output).
```

```{asis, echo = model.area=='SCA'}
In southern California, spawning output declined rapidly in the 1970s and early 1980s, falling below the minimum stock size threshold in the early 1980s, followed by a steady recovery since the late 2000s (Figures \@ref(fig:ssbES) and \@ref(fig:deplES)). The trend in spawning output in 2017 is approaching the management target (40% of unfished spawning output), but the precision of that estimate is low relative to other management reference points (e.g. the SPR50% proxies for target spawning output and maximum yield).
```


<!--BEGIN  EXECUTIVE SUMMARY SPAWNING BIOMASS AND DEPLETE TABLES AND FIGURES-->
```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of relative spawning output depletion (spawning output relative to unfished spawning output) with approximate 95% asymptotic confidence intervals (dashed lines)",
label = 'deplES')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc, "plots", "ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning output with approximate 95% asymptotic confidence intervals (dashed lines)",
label = 'ssbES')
```



```{r, results = 'asis'}
kableExtra::kbl(ssb,
                booktabs=TRUE,
                caption="Estimated recent trend in spawning output and the fraction unfished and the 95 percent intervals.",
                label="ssbES",
                col.names = c("Year" , "Spawning Output" , "Lower Interval" , "Upper Interval" , "Fraction Unfished" , "Lower Interval" , "Upper Interval"),
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"))
```

<!-- *************END EXECUTIVE SUMMARY SPAWNING BIOMASS AND**************** -->
<!-- *************DEPLETION TABLES AND FIGURES******************************* -->

\FloatBarrier

## Recruitment{-}

```{asis, echo = model.area=='NCA'}
Recruitment deviations were estimated from 1970-2020 with a recent, strong recruitment in 2016 that has contributed to the recent increase in vermilion biomass in northern California (Table \@ref(tab:recrES); Figure \@ref(fig:recruitsES)). Overall, variability in recruitment is average (to low) in the years following 2016.  
```

```{asis, echo = model.area=='SCA'}
ajor recruitments (strong year classes) in southern California were consistently estimated by the primary sources of age data (NWFSC hook-and-line and trawl surveys), with a strong 1999 year class estimated even when either data set is removed (see sensitivity section). Other years with relatively high estimates of recruitment were 1983-84, 1999, and 2016 these are consistent with estimates of strong year classes in other rockfish stock assessments. 
```


```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc, "plots", "ts11_Age-0_recruits_(1000s)_with_95_asymptotic_intervals.png"),
caption = "Age-0 recruits (1,000s) with ~95% asymptotic intervals",
label = 'recruitsES')
```

```{r,echo=FALSE, warning=FALSE, message=FALSE}
recr <- read.csv(paste0(exec_tables_loc,'c_Recr_ES.csv')) %>%
  mutate_at(c(-1), round,3) 
```

```{r, results = 'asis'}
kableExtra::kbl(recr,
                booktabs=TRUE,
                caption="Estimated recent trend in recruitment and recruitment deviations and the 95 percent intervals.",
                label="recrES",
                col.names = c("Year" , "Recruitment" , "Lower Interval" , "Upper Interval" , "Recruitment Deviations" , "Lower Interval" , "Upper Interval"),
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))
```

\FloatBarrier

## Exploitation Status{-}

```{asis, echo = model.area=='NCA'}
The annual (equilibrium) SPR harvest rate for vermilion was above target  from 2017-2019 (Table \@ref(tab:exploitES), Figure \@ref(fig:1-sprES)). Prior to 2011, the harvest rate exceeded the target for a number of years, regularly reaching levels 50% above target in the 1980s and 1990s (Figure \@ref(fig:1-sprES)). As with current estimates of spawning output, recent estimates of exploitation status are highly uncertain, ranging from 68% to 129% of target in 2020 (Table ES7). As a percentage of total biomass (ages 4+), California harvest rates peaked in the 1980s and 1990s, but have since declined to levels below 10% for the past decade (Figure \@ref(fig:FmortalityES)). Harvest rates in California are currently above target, and the stock is just above the target biomass (Figure \@ref(fig:phaseES)). The equilibrium yield curve is shifted left, as expected from the Beverton-Holt steepness parameter fixed at 0.72 (Figure \@ref(fig:yield2ES)).
```


```{r,echo=FALSE, warning=FALSE, message=FALSE}
exploit <- read.csv(paste0(exec_tables_loc,'d_SPR_ES.csv')) %>%
  mutate_at(c(2:7), round,3)
```

```{r, results = 'asis'}
kableExtra::kbl(exploit,
                booktabs=TRUE,
                caption="Estimated recent trend in the (1-SPR)/(1-SPR 50\\%) where SPR is the spawning potential ratio the exploitation rate, and the  95 percent intervals.",
                label="exploitES",
                col.names = c("Year" , "(1-SPR)/(1-SPR 50\\%)" , "Lower Interval" , "Upper Interval" , "Exploitation Rate" , "Lower Interval" , "Upper Interval"),
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))
```

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(base_loc, "plots", "SPR3_ratiointerval.png"), 
caption = "Timeseries of SPR ratio: (1-SPR)/(1-SPR_50%)",
label = '1-sprES')
```


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(base_loc, "plots", "ts_summaryF.png"), 
caption = "Time-series of estimated summary harvest rate (total catch divided by age-0 and older biomass) for the base case models with approximate 95% asymptotic confidence intervals (grey lines).",
label = 'FmortalityES')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc, "plots", "SPR4_phase.png"), 
caption = "Phase plot of the relative biomass (also referred to as fraction unfished) versus the SPR ratio where each point represents the biomass ratio at the start of the year and the relative fishing intensity in that same year. Lines through the final point show the 95 percent intervals based on the asymptotic uncertainty for each dimension. The shaded ellipse is a 95 percent region which accounts for the estimated correlations between the biomass ratio and SPR ratio",
label = 'phaseES')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(base_loc, "plots", "yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model. Values are based on the 2020
fishery selectivity",
label = 'yield2ES')
```


\FloatBarrier

## Ecosystem Considerations{-}

In this assessment, ecosystem considerations were not explicitly included in the analysis.  
This is primarily due to a lack of relevant data and results of analyses (conducted elsewhere) 
that could contribute ecosystem-related quantitative information for the assessment.

Vermilion/sunset rockfish are described as feeding on a wide range of both
pelagic and benthic prey items, including forage fish species such as anchovies 
and mesopelagic fishes, squid, krill and octopus, as well as sporadically abundant
pelagic organisms such as pyrosomes, salps and pelagic red crabs 
[@Phillips1964; @Love2002]. 

As with most other rockfish and groundfish in the California Current, recruitment, 
or cohort (year-class) strength appears to be highly variable for the vermilion/sunset 
rockfish complex, with only a modest apparent relationship to estimated levels of spawning output.  
Oceanographic and ecosystem factors are widely recognized to be key drivers of
recruitment variability for most species of groundfish, as well as most elements
of California Current food webs.  Although it is feasible that 
ecosystem factors, the results of pre-recruit surveys for co-occurring species, 
or the results of other groundfish assessments might ultimately be used to 
forecast recruitment for more data-limited stocks such as vermilion/sunset,
as suggested by [@Thorson2014], such approaches would require more 
development and evaluation.  Consequently, environmental factors are not 
explicitly considered in this assessment.


\FloatBarrier

## Reference Points{-}
```{r,echo=FALSE, warning=FALSE, message=FALSE}
refpts <- read.csv(paste0(exec_tables_loc,'e_ReferencePoints_ES.csv')) %>%
  mutate_at(c(2:4), round,3)
```

Reference point and management quantities for the vermilion rockfish base case model can be found in Table \@ref(tab:referenceES). In 2020, spawning output relative to unfished spawning 
output ("depletion") is estimated at `r scales::percent(ssb$Fraction.Unfished[ssb$Year==model$endyr], accuracy = 1)`. This stock assessment estimates that `r spp` in the `r params$model` is above the biomass 
target ($SB_{40\%}$), and well above the minimum stock size threshold ($SB_{25\%}$). 
Unfished age four-plus biomass is estimated to be `r refpts[2,2]` mt in the 
base case model. The target spawning output ($SB_{40\%}$) 
is `r refpts[7,2]` million eggs, which corresponds with an 
equilibrium yield of `r refpts[10,2]` mt. Equilibrium yield at the proxy $F_{MSY}$ 
harvest rate corresponding to $SPR_{50\%}$ is `r refpts[15,2]` mt (Table \@ref(tab:referenceES) and Figure \@ref(fig:yield2ES)).






```{r, results = 'asis'}
kableExtra::kbl(refpts,
                booktabs=TRUE,
                caption="Summary of reference points and management quantities including estimates of the 95 percent intervals.",
                label="referenceES",
                escape = FALSE,
                col.names = c("", "Estimate","Lower Interval","Upper Interval")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"))


```


\FloatBarrier

## Management Performance{-}
Vermilion rockfish are managed as part of the minor shelf rockfish
complex in the Pacific Coast Groundfish Fishery Management Plan. The total mortality 
of the minor shelf rockfish has been above the ACL in all years (2011-2019). 
Total mortality estimates from the NWFSC are not yet available 
for 2019-2020. A summary of these values 
as well as other base case summary results can be found in Tables \@ref(tab:managementES) and 
\@ref(tab:summaryES).


Results from post-STAR base models in all areas are presented in Table \@ref(tab:CombinedRefPtsES).
fraction of No. CA allocated to northern management area (north of \CapeM) is based on Appendix in Northern CA assessment.
The fraction of of the northern California stock that is estimated to be north of \CapeM 
is 4.44%. The projected OFLs (2023-2032) assume full attainment of GMT-projected catches for 2021-22, and catches based on the PFMC harvest control rule given P* =  0.45 and sigma = 1.



```{r, warning = FALSE, inclue = FALSE}
management <- readxl::read_xlsx("./tables/VRML_management_history.xlsx", sheet = "Management")  %>%
  mutate(across(c(2:13), ~ round(.,3)))
management$Area_landings = c("OFL", "ABC", "Total landings", 
                             "CA rec landings", "OR rec landings", 
                             "WA rec landings","Commercial landings", "Research",
                             "OFL", "ABC", "Total Landings", 
                             "CA rec landings", "Commercial landings", "Research")
colnames(management)[1] = ""

```


```{r, management, results = 'asis'}
kableExtra::kbl(management, booktabs = TRUE, 
  caption = "Annual estimates of total mortality, overfishing limit (OFL), acceptable biological catch (ABC), annual catch limit (ACL) for vermilion. The ABC is equal to the ACL.  Data were obtained from the GEMM reports.",
  label = 'managementES',
escape = FALSE) %>%
kableExtra::pack_rows(group_label = paste0("North of 40",intToUtf8(176),"10\' N"), start_row = 1, end_row = 8) %>%
kableExtra::pack_rows(group_label = paste0("South of 40",intToUtf8(176),"10\' N"), start_row = 9, end_row = 14) %>%
  kable_styling(latex_options = "scale_down")
```



```{r,echo=FALSE, warning=FALSE, message=FALSE}
combinedrefpts = readxl::read_xlsx(paste0(table_loc,"Combined_Reference_Points.xlsx")) %>%
 mutate(across(where(is.numeric), round, 1)) 
  
```

```{r, results = 'asis'}
kableExtra::kbl(combinedrefpts, format = "latex",
                booktabs=TRUE,
                label="CombinedRefPtsES",
                align = "l",
                caption = "Combined reference points for the four stock assessments conducted 
               for vermilion and sunset rockfishes in 2021.") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  column_spec(1, width = "2in") %>%
  column_spec(c(2:9), width = ".5in")
```


```{r,echo=FALSE, warning=FALSE, message=FALSE}
summaryES <- read.csv(paste0(exec_tables_loc,'i_Summary_ES.csv')) 
summaryES[1:2,] =management[1:2,1:12]
summaryES <- summaryES %>%
  mutate_at(-1, as.numeric) %>%
  mutate_at(-1, round, 3) 
summaryES$Quantity[4] = "(1-SPR)/(1-SPR 50\\%)"

```


```{r, results = 'asis'}

kableExtra::kbl(summaryES,
                booktabs=TRUE,
                caption="Summary of recent estimates and managment quantities.",
                label="summaryES",
              #  escape = FALSE, 
                col.names = c("Quantity", seq(2011,2021,1))) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"))
```



\FloatBarrier

## Unresolved Problems and Major Uncertainties{-}
The stratification of assessment areas along the coast was based on consideration of population structure identified in genetic analyses, differences in historical exploitation, disparate availability of data sources and state specific regulations to mitigate the catch of overfished species affecting catch of co-occurring stocks like vermilion rockfish.  The Panel discussed the potential for alternative stratification such as north and south of Cape Mendocino depending on the results of future analysis of population structure under the Saltonstall/Kennedy grant discussed in the assessment south of Point Conception to better understand the distribution of sunset rockfish, potential for hybridization and resolve considerations surrounding population structure apparent in vermilion rockfish. A more regional approach might allow for greater efficiency gained by fewer assessment areas, while accounting for key differences.  

Natural mortality remains the primary axis of uncertainty across assessment areas.  Additional collection of otoliths from across the range of the stock and ageing existing structures from the hook and line survey may help reduce uncertainty in the future. 


\FloatBarrier

## Decision Table and Forecasts{-}
The forecasts of stock abundance and yield were developed using the post-STAR 
base model, with the forecasted projections presented in 
Table \@ref(tab:projectionES). The total catches in 2021 and 2022 are set to 
the projected catch from the California Department of Fish and Wildlife (CDFW) by 
sector.

```{asis, echo = model.area=='NCA'}
Uncertainty in the forecasts is based upon the three states of nature agreed upon 
at the STAR panel, reflecting three different natural mortality rates. The steepness 
parameter of the Beverton-Hold stock-recruit curve  was fixed in the base model and the 
alternative states of nature and the alternate states of nature maintain the 
female to male natural mortality rata ratio from  the base model. To capture the 75% interval, alternate states were identified that were within 0.66 negative log-likelihood points from the base model.
The high state of nature fixes female $M$ = 0.0956 and male $M$ = 0.08989. For the low state of nature, female $M$ = 0.0769 and male $M$ = 0.07231.

For reference, the base model predicted sigma is 0.246. The buffers were calculated assuming a category 2 stock, with  sigma = 1.0 
and a $p^*$ = 0.45. Alternative catch streams assume (rows in the table) sigma = 1.0 
and a $p^*$ = 0.4, and removals of long-term equilibrium catch with and without a buffer assuming sigma = 1.0 and a $p^*$ = 0.45. The buffer multiplier with $p^*$ = 0.45 ranges from 0.874 in 2023 ramping to 0.803 in 2032. 
Current medium-term forecasts based on the alternative states of nature project that 
the stock will remain above the target threshold of 40% in 2032 (Table \@ref(tab:DecisionES)).  In al of the scenarios of the low state of natre,  
the stock remains below the target threshold of 40% until 2026 or 2027.
The base 
model with the base catches results in an increasing stock over the period from 
2023-2032. In all scenarios the catch significantly decreases from 2022 to 2023 in a 
all catch scenarios; assumed catch in 2022 is 227 mt, and 2023 cathes from the base 
model range from 118-139 mt.  The base model includes a portion of the stock within 
the northern management unit (north of \CapeM).  Analaysis from an appendix suggests 
that 4.44% of the catches from this model should be apportioned to the northern 
management unit for vermilion rockfish.
```


```{asis, echo = model.area=='SCA'}
Uncertainty in the forecasts is based upon the three states of nature agreed upon 
at the STAR panel, reflecting a bivariate sensitivity analysis between natural mortality and steepness. Both natural moratlity (assumed females equal to males) and steepness were estimated in the base model.

For reference, the base model predicted sigma is 0.258. The buffers were calculated assuming a category 2 stock, with  sigma = 1.0 
and a $p^*$ = 0.45. Alternative catch streams (rows in the table) assume sigma = 1.0 
and a $p^*$ = 0.4, and removals of long-term equilibrium catch with and without a buffer assuming sigma = 1.0 and a $p^*$ = 0.45. The buffer multiplier with $p^*$ = 0.45 ranges from 0.874 in 2023 ramping to 0.803 in 2032. The low state of nature assumes $M$ = .1125 and $h$ = 0.675, and the high state of nature asumes $M$ = 0.1475 and $h$ = 0.875.

Current medium-term forecasts based on the alternative states of nature project that 
the stock will remain above the target threshold of 40% in 2032 in the base model and also 
the state of nature assuming higher productivity (Table \@ref(tab:DecisionES)).  In all scenarios of the low state of nature,  
the stock remains below the target threshold of 40% until throughout the forecast.
The base 
model with the base catches results in an increasing stock over the period from 
2023-2032. In all scenarios the catch significantly decreases from 2022 to 2023 in a 
all catch scenarios; assumed catch in 2022 is 210 mt, and 2023 cathes from the base 
model range from 121-148 mt.
```


```{r,echo=FALSE, warning=FALSE, message=FALSE}
projection <- read.csv(paste0(exec_tables_loc,'g_Projections_ES.csv')) %>%
  mutate_at(c(2:4), round,3)
```


```{r, results = 'asis'}
kableExtra::kbl(projection,
                booktabs=TRUE,
                caption="Projections of potential OFLs (mt), ABCs (mt), estimated spawning output and fraction unfished.",
                label="projectionES",
               # escape = FALSE,
                col.names = c("Year" , "Predicted OFL (mt)" , "ABC Catch (mt)" , "Age 4+ Biomass (mt)" , "Spawning Output" , "Fraction Unfished")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))


```


\FloatBarrier

```{r,echo=FALSE, warning=FALSE, message=FALSE}
decisiontable.filein = list.files(path = table_loc, 
                  pattern = glob2rx(paste0("VRML_decision_table_", model.area, ".xlsx")), 
                  full.names = TRUE)
decisiontable <- readxl::read_xlsx(decisiontable.filein) %>%
   mutate(across(grep("Spawning", .), round, 0)) %>%
   mutate(across(grep("Catch", .), round, 1)) %>%
   mutate(across(grep("Fraction", .), round, 3))
```


```{r, results = 'asis'}

if(model.area=='NCA'){
kableExtra::kbl(decisiontable, format = "latex",
                booktabs=TRUE,
                label="DecisionES",
                digits = c(0,0,3,0,0,3,0,3,0,3),
                align = "c",
               # escape = FALSE, 
                col.names = c(" ","Year",
                              "Buffer",
                              "Catch (mt)",
                              "Spawning Output", "Fraction Unfished",
                              "Spawning Output", "Fraction Unfished",
                              "Spawning Output", "Fraction Unfished"),
                caption = "Decision table summarizing 12 year projections (2021 to 2032) for vermilion based on three alternative states of nature spanning quantiles of spawning output in 2021.  Columns range over low, medium, and high state of nature, and rows range over different assumptions of total catch levels corresponding to the forecast catches from each state of nature.  Catches in 2021 and 2022 are fixed at catches provided by the CDFW.") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  add_header_above(c(" " = 4,
                     "NLL = 1031.34" = 2,
                     "NLL = 1032" = 2,
                     "NLL = 1031.34" = 2)) %>%
  add_header_above(c(" " = 4,
                     "Male M = 0.0723" = 2, 
                     "Male M = 0.0805" = 2,
                     "Male M = 0.0899" = 2), line = F) %>%
  add_header_above(c(" " = 4,
                     "Female M = 0.0769" = 2, 
                     "Female M = 0.0856" = 2,
                     "Female M = 0.0956" = 2), line = F) %>%
  add_header_above(c(" " = 4, 
                     "Low Productivity" = 2, 
                     "Base Model" = 2, 
                     "High Productivity" = 2)) %>%
  column_spec(1, width = "1in") %>%
  column_spec(c(2:4), border_left = T) %>%
  column_spec(c(5,7,9), width = ".8in", border_left = T) %>%
  column_spec(c(6,8,10), width = ".8in") %>%
  collapse_rows(columns = 1, valign = "middle", latex_hline = "major") 
} else {

kableExtra::kbl(decisiontable, format = "latex",
                booktabs=TRUE,
                label="DecisionES",
                digits = c(0,0,3,0,0,3,0,3,0,3),
                align = "c",
               # escape = FALSE, 
                col.names = c(" ","Year",
                              "Buffer",
                              "Catch (mt)",
                              "Spawning Output", "Fraction Unfished",
                              "Spawning Output", "Fraction Unfished",
                              "Spawning Output", "Fraction Unfished"),
                caption = "Decision table summarizing 12year projections (2021 to 2032) for vermilion based on three alternative states of nature spanning quantiles of spawning output in 2021.  Columns range over low, medium, and high state of nature, and rows range over different assumptions of total catch levels corresponding to the forecast catches from each state of nature.  Catches in 2021 and 2022 are fixed at catches provided by the CDFW.") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  add_header_above(c(" " = 4,
                     "NLL = 1015.23" = 2,
                     "NLL = 1013.02" = 2,
                     "NLL = 1014.72" = 2)) %>%
  add_header_above(c(" " = 4,
                     "h = 0.675" = 2, 
                     "h = 0.730" = 2,
                     "h = 0.875" = 2), line = F) %>%
  add_header_above(c(" " = 4,
                     "M = 0.1125" = 2, 
                     "M = 0.1302" = 2,
                     "M = 0.1475" = 2), line = F) %>%
  add_header_above(c(" " = 4, 
                     "Low Productivity" = 2, 
                     "Base Model" = 2, 
                     "High Productivity" = 2)) %>%
  column_spec(1, width = "1in") %>%
  column_spec(c(2:4), border_left = T) %>%
  column_spec(c(5,7,9), width = ".8in", border_left = T) %>%
  column_spec(c(6,8,10), width = ".8in") %>%
  collapse_rows(columns = 1, valign = "middle", latex_hline = "major") 
}
```


\newpage



## Research and Data Needs{-}

There are several areas for further research that were identified while conducting 
this assessment that could result in information useful to future vermilion and sunset 
rockfish assessments.  The list below is believed to represent strategic pieces of 
information that would likely help to resolve key uncertainties associated with 
assessing either or both species. Many would provide the necessary information to 
evaluate basic life history parameters and spatiotemporal population and fleet dynamics.

- Investigate the structure of complex and contribution of each species to the 
vermilion/sunset complex. Investigate possible spatial differences in biological parameters within 
a single species and also between the two species. Little biological data for south of 
Point Conception or north of Point Arena were available for this assessment and is needed 
to better under biological parameters. 
  + Conduct life history studies
  + Conduct research to identify the proportion of each species in population and in catches

- Take a closer look at historical catch reconstructions and 
all other historical data sources.

- Refine CCFRP survey index to look at alternative possible model structures, including 
a hierarchical structure and random effects. The CCFRP survey is the only 
fishery-independent survey available for nearshore rockfish sampling the nearshore rocky 
reef habitats. As of this assessment, only two years of coastwide data are available, 
and the index was limited to the site in central California that have been monitored 
since 2007.

- Continue to investigate the most appropriate model structure for the NWFSC HL survey index.
The NWFSC HL survey is the only long-term fishery-independent survey in rocky (untrawlable) habitat 
in the Southern California Bight. We also recommend evaluating how to structure the NWFSC Hook-and-Line survey index given its expansion into the CCA, also independent analysis of information content in NWFSC Hook-and-Line survey.Increased spatiotemporal sampling around Pt. Conception would aid in identifying stock boundaries.

- Utilize existing ROV survey data sources
  + SWFSC Submersible Survey of the Cowcod Conservation Areas [@Yoklavich2007]. 
  +  This was a line-transect survey designed to estimate cowcod abundance in 2002 
  conducted from a submersible inside the CCAs.  Originally, only cowcod were enumerated from the video footage.  Over the last few years, the SWFSC has re-analyzed the video footage to enumerate other rockfish species. 
    + The SWFSC Fishery Resource Division (FRD) conducted a survey of potential cowcod habitat between Point Conception and the U.S. – Mexico border from October through December of 2012 [@Stierhoff2013].
    +  SWFSC staff are submitting proposals to conduct an additional submersible survey in the southern California Bight
    + CDFW ROV survey data


- Collection of length and age data are recommended for both the commercial and 
recreational fisheries.  Very little age data are available from either fishery for 
vermilion and sunset rockfishes.

- Investigate possible environmental drivers/co-variates for biological parameters, 
particularly for recruitment.

- Resolve differences between CalCOM and PacFIN expanded length composition data sets. 



<!--chapter:end:01executive.Rmd-->

