---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
params:
    model: "north"
preamble: |
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{placeins}
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
lang: en
papersize: a4
csl: CJFAS.csl
---

<!-- Common lat/long 
Cape Mendocino, Pt. Conception and OR border -->
\newcommand\CapeM{$40^\circ 10^\prime N$}
\newcommand\PtC{$34^\circ 27^\prime N$}
\newcommand\CAOR{$42^\circ 00^\prime N$}


```{r, setup, include=FALSE}
rmarkdown::find_pandoc(version = "2.14.0.3")
```


```{r opts, include = FALSE}
library(kableExtra)
library(dplyr)
library(ggplot2)
library(tidyr)
library(rmarkdown)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })
options(knitr.duplicate.label = "allow") #allow duplicate labels - needed for longtable
options(knitr.kable.NA = '') #print blank cells in tables with NA
#knitr::knit_hooks$set(crop = knitr::hook_pdfcrop) #crop figures
#knitr::knit_hooks$set(optipng = knitr::hook_optipng) #optimize figure size


source("C:/Stock_Assessments/VRML_Assessment_2021/GitHub/Vermilion_2021/code/dir_recent.R")
dir.path <- ifelse(params$model=="north",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/NCA/",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/SCA/")
model.dir <- dir_recent(dir = dir.path, pattern = "Verm")
base_loc <- paste0(model.dir,"/")


if (is.null(params$model) & file.exists("00mod.Rdata")) {
  stopifnot(file.exists("00mod.Rdata"))
  load("00mod.Rdata")
} else {
  load(dir(base_loc, pattern = "00mod.Rdata", full.names = TRUE))
}

model.area <- ifelse(params$model=="north", "NCA", "SCA")
spp = 'vermilion rockfish'
Spp = 'Vermilion rockfish'
fig_loc = paste0(getwd(), "/figures")
base_loc_plots = paste0(base_loc,"plots")
table_loc = paste0(getwd(), "/tables/")
tex_tables_loc = paste0(getwd(),"/tex_tables/", params$model)
tex_parent_loc = paste0(getwd(),"/tex_tables/")
#move the tex tables to the parent folder depending on which model you're working on 
#best solution I have so far
files <- list.files(path = tex_tables_loc, full.names = TRUE)
files_new <- gsub(dirname(files[1]), tex_parent_loc, files)
for (i in 1:length(files)){
  file.copy(files[i], files_new[i])
}


# model_loc = "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/"



if(params$model=="north"){
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "Deb Wilson-Vandenberg onboard survey",
                           "West coast groundfish bottomfish trawl survey",
                           "recreational PC onboard survey",
                           "Abrams thesis research survey",
                           "SWFSC groundfish ecology survey",
                           "California Collaborative Fisheries Research Project survey")
} else {
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "NWFSC hook-and-line survey",
                           "West Coast Groundfish Bottomfish Trawl Survey",
                           "recreational PC onboard survey",
                           "CDFW reserach (aka green binder) survey",
                           "Early years hook-and-line")
}

model$FleetNames_label <- stringr::str_replace_all(model$FleetNames, "_", "-")

fleet_info = data.frame(cbind(model$fleet_ID, model$FleetNames, model$FleetNames_label, model$FleetNames_parsed))
colnames(fleet_info) = c("fleet_ID", "FleetNames", "FleetNames_label", "FleetNames_parsed")

plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))

```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: E. J. Dick
    code: 1
    first: E
    middle: J
    family: Dick
  - name: Melissa H. Monk
    code: 1
    first: M
    middle: H
    family: Monk
  - name: Tanya L. Rogers
    code: 1
    first: T
    middle: L
    family: Rogers
  - name: John C. Field
    code: 1
    first: J
    middle: C
    family: Field
  - name: Emma M. Saas
    code: 1
    first: E
    middle: M
    family: Saas
author_list: Dick, E.J., M.H. Monk, T.L. Rogers, J.C. Field, E.M. Saas
affiliation:
  - code: 1
    address: Southwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110
      McAllister Way, Santa Cruz, California 95060
address: ^1^Southwest Fisheries Science Center, U.S. Department of Commerce, National
  Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110 McAllister
  Way, Santa Cruz, California 95060
---

<!--chapter:end:00authorssouth.Rmd-->

---
bibliography: 
  - sa4ss.bib
---

<!--chapter:end:00bibliography.Rmd-->

\newpage

\includegraphics{cover_photo.png}
Two fish of the vermilion/sunset cryptic species pair.  Confirmation of 
species can only be determined via genetic analysis and species identification 
of these two fish caught in the Santa Barbara channel at approximately 250 ft depth 
is unknown. Photo courtesy of Sabrina Beyer.

<!--
\printnoidxglossary[sort=word]
-->


<!--chapter:end:01a-photo.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}


\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:01a.Rmd-->

# Executive Summary{-}
To be completed after the STAR panel. Tables from the pre-STAR base model 
are included for reference during the STAR panel.

## Stock{-}
This assessment reports the status of the vermlion rockfish (_Sebastes miniatus_) 
and sunset rockfish (_Sebastes crocotulus_) complex (referred to as vermilion 
throughout), resource in U.S. waters off the coast of California `r params$model` 
of Point Conception (\PtC) using data through 2020.


## Landings{-}
Text will be provided after the STAR panel.

```{r,echo=FALSE, warning=FALSE, message=FALSE}
removals <- read.csv('./tex_tables/a_Catches_ES.csv') %>%
  mutate_at(c(-1), round,3) %>%
  rename(`Total Landings` = Total.Landings)
colnames(removals) = gsub("_","-",colnames(removals))
```

```{r, results = 'asis'}
kableExtra::kbl(removals,
                booktabs=TRUE,
                caption="Recent landings by fleet, total landings summed across fleets, and the total mortality including discards.",
                label="removalsES",
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))
```

## Data and Assessment{-}
Text will be provided after the STAR panel.

## Stock Biomass{-}
Text will be provided after the STAR panel.

```{r,echo=FALSE, warning=FALSE, message=FALSE}
ssb <- read.csv('./tex_tables/b_SSB_ES.csv') %>%
  mutate_at(c(-1), round,3) 
```

```{r, results = 'asis'}
kableExtra::kbl(ssb,
                booktabs=TRUE,
                caption="Estimated recent trend in spawning output and the fraction unfished and the 95 percent intervals.",
                label="ssbES",
                col.names = c("Year" , "Spawning Output" , "Lower Interval" , "Upper Interval" , "Fraction Unfished" , "Lower Interval" , "Upper Interval"),
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"))
```

## Recruitment{-}
Text will be provided after the STAR panel.

```{r,echo=FALSE, warning=FALSE, message=FALSE}
recr <- read.csv('./tex_tables/c_Recr_ES.csv') %>%
  mutate_at(c(-1), round,3) 
```

```{r, results = 'asis'}
kableExtra::kbl(recr,
                booktabs=TRUE,
                caption="Estimated recent trend in recruitment and recruitment deviations and the 95 percent intervals.",
                label="recrES",
                col.names = c("Year" , "Recruitment" , "Lower Interval" , "Upper Interval" , "Recruitment Deviations" , "Lower Interval" , "Upper Interval"),
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))
```

## Exploitation Status{-}
Text will be provided after the STAR panel.

```{r,echo=FALSE, warning=FALSE, message=FALSE}
exploit <- read.csv('./tex_tables/d_SPR_ES.csv') %>%
  mutate_at(c(2:7), round,3)
```

```{r, results = 'asis'}
kableExtra::kbl(exploit,
                booktabs=TRUE,
                caption="Estimated recent trend in the (1-SPR)/(1-SPR 50\\%) where SPR is the spawning potential ratio the exploitation rate, and the  95 percent intervals.",
                label="exploitES",
                col.names = c("Year" , "(1-SPR)/(1-SPR 50\\%)" , "Lower Interval" , "Upper Interval" , "Exploitation Rate" , "Lower Interval" , "Upper Interval"),
                escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))
```

## Reference Points{-}
Text will be provided after the STAR panel.



```{r,echo=FALSE, warning=FALSE, message=FALSE}
refpts <- read.csv('./tex_tables/e_ReferencePoints_ES.csv') %>%
  mutate_at(c(2:4), round,3)
```

```{r, results = 'asis'}
kableExtra::kbl(refpts,
                booktabs=TRUE,
                caption="Summary of reference points and management quantities including estimates of the 95 percent intervals.",
                label="referenceES",
                escape = FALSE,
                col.names = c("", "Estimate","Lower Interval","Upper Interval")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"))


```

## Management Performance{-}
Text will be provided after the STAR panel.

```{r, warning = FALSE, inclue = FALSE}
management <- readxl::read_xlsx("./tables/VRML_management_history.xlsx", sheet = "Management")  %>%
  mutate(across(c(2:13), ~ round(.,3)))
management$Area_landings = c("OFL", "ABC", "Total landings", 
                             "CA rec landings", "OR rec landings", 
                             "WA rec landings","Commercial landings", "Research",
                             "OFL", "ABC", "Total Landings", 
                             "CA rec landings", "Commercial landings", "Research")
colnames(management)[1] = ""

```


```{r, management, results = 'asis'}
kableExtra::kbl(management, booktabs = TRUE, 
  caption = "Annual estimates of total mortality, overfishing limit (OFL), acceptable biological catch (ABC), annual catch limit (ACL) for vermilion. The ABC is equal to the ACL.  Data were obtained from the GEMM reports.",
escape = FALSE) %>%
kableExtra::pack_rows(group_label = paste0("North of 40",intToUtf8(176),"10\' N"), start_row = 1, end_row = 8) %>%
kableExtra::pack_rows(group_label = paste0("South of 40",intToUtf8(176),"10\' N"), start_row = 9, end_row = 14) %>%
  kable_styling(latex_options = "scale_down")
```


## Unresolved Problems and Major Uncertainties{-}
Text will be provided after the STAR panel.

## Decision Table{-}
Text will be provided after the STAR panel.

*Projections* 



```{r,echo=FALSE, warning=FALSE, message=FALSE}
projection <- read.csv('./tex_tables/g_Projections_ES.csv') %>%
  mutate_at(c(2:4), round,3)
```

```{r, results = 'asis'}
kableExtra::kbl(projection,
                booktabs=TRUE,
                caption="Projections of potential OFLs (mt), ABCs (mt), estimated spawning output and fraction unfished.",
                label="projectionES",
                escape = FALSE,
                col.names = c("Year" , "Predicted OFL (mt)" , "ABC Catch (mt)" , "Age 4+ Biomass (mt)" , "Spawning Output" , "Fraction Unfished")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position","scale_down"))


```


*Summary Table*

```{r,echo=FALSE, warning=FALSE, message=FALSE}
summaryES <- read.csv('./tex_tables/i_Summary_ES.csv') 
summaryES[1:2,] =management[1:2,1:12]
summaryES <- summaryES %>%
  mutate_at(-1, as.numeric) %>%
  mutate_at(-1, round, 3) 
summaryES$Quantity[4] = "(1-SPR)/(1-SPR 50\\%)"


```

```{r, results = 'asis'}

kableExtra::kbl(summaryES,
                booktabs=TRUE,
                caption="Summary of recent estimates and managment quantities.",
                label="summaryES",
                escape = FALSE, 
                col.names = c("Quantity", seq(2011,2021,1))) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"))


```


## Research and Data Needs{-}
Text will be provided after the STAR panel.

<!--chapter:end:01executive.Rmd-->

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
\setcounter{figure}{0}

<!--chapter:end:10a.Rmd-->

# Introduction
Note to readers: Text in this section is the same in both California `r spp` assessment 
documents.

```{r render-12, results = "asis"}
sa4ss::read_child("12basicinfo.Rmd")
```


```{r render-13, results = "asis"}
sa4ss::read_child("13fisheries.Rmd")
```


<!--chapter:end:11introduction.Rmd-->

# Data

The STAT presented proposed analyses and data sources for the 2021 `r spp` 
assessment to the Council advisory bodies in Novemeber 2020, and again during the PFMC Pre-Assessment Workshop for 2021 Vermilion and 
Lingcod Stock Assessments, hosted virtually on March 29, 2021. Topics addressed 
included progress on research priorities, data sources and types, stock structure, 
fleet structure, key model parameters (e.g. natural mortality), and potential 
challenges. Descriptions of each data source included in the model 
(Figure \@ref(fig:data-plot)) and sources that were explored, but not included
are included within this section.

## Fishery-Dependent Data

A complete summary of estimated `r spp` removals by each fleet in the 
commercial and recreational sectors modeled in this assessment is provided in Table 
\@ref(tab:landings).  The data sources for landings varied by each fleet and a summary 
of each data source and the time period for which it was used is in Table \@ref(tab:catch-source).
The commercial landings are in metric tons (mt) and the recreational landings 
are in numbers of fish (thousands of fish). Data and 
methods used to derive these estimates are described in this section.



```{r render-21, results = "asis"}
sa4ss::read_child("21data-a-commercial.Rmd")
```


```{r render-21b, results = "asis"}
sa4ss::read_child("21data-b-recreational.Rmd")
```



```{r render-21c, results = "asis"}
sa4ss::read_child("21data-c-fishery-independent.Rmd")
```


```{r render-21d, results = "asis"}
sa4ss::read_child("21data-sources-not-used.Rmd")
```



```{r render-2, results = "asis"}
sa4ss::read_child("22biology.Rmd")
```


<!--chapter:end:20data.Rmd-->

# Assessment Model Description

## History of Modeling Approaches

Vermilion was assessed coastwide as a data poor species using 
Depletion-Based Stock Reduction Analysis (DB-SRA) [@Dick2010]. Average catch 
2008-2009 was 136.3 mt, and the median OFL in 2010 was 314.3 mt with a 28% 
probability that recent catch exceeded the 2010 [@Dick2010].

A 2005 assessment was not accepted for management. 
From the September 2005 [Briefing Book](https://www.pcouncil.org/documents/2005/09/f-groundfish-management-september-2005.pdf/): 
"The SSC considers the assessment to be best available science, but at this  stage does not 
endorse the results as being suitable for setting OYs." A 2013 data moderate 
assessment was prepared, but not reviewed. From Pacific Coast Groundfish Stock 
Assessment Review (STAR) Panel Report For Data-Moderate Assessments (2013): 
"There was insufficient time during the review to evaluate all the assessments 
originally requested by the Council. Assessments for vermilion/sunset rockfishes 
(*Sebastes miniatus* and *Sebastes crocotulus*) and yellowtail rockfish 
(south of \CapeM) were not presented by the Stock Assessment Team (STAT)."


### Most Recent STAR Panel and SSC Recommendations 

The 2005 STAR panel report compiled recommendations specific to vermilion, and also 
generic rockfish recommendations The generic rockfish recommendation are not 
presented here.  The 2005 assessment was not accepted for management by the PFMC.

**Vermilion rockfish recommendations**

Investigation into the species composition of nominal vermilion rockfish is needed.
It is not clear that separate assessments for the northern and southern areas are warranted
for vermilion rockfish. Although there were differences in the estimated magnitude and
timing of recruitment events, the estimated stock trends were similar in both areas.
Pooling of data from northern and southern areas may permit a more robust assessment
model to be obtained.

*2021 STAT response.* Since the 2005 assessment, vermilion rockfish were speciated 
to vermilion and sunset rockfishes [@Hyde2009].  Sunset rockfish are more common south of 
Pt. Conception (\PtC) and historical catches and length distributions between 
the two areas are different. The STAT discussed this at the Pre-Assessment workshop 
and all participants agreed that modeling the areas separately was an appropriate 
decision.




```{r render-31, results = "asis"}
sa4ss::read_child("31model-star-responses.Rmd")
```


```{r render-32, results = "asis"}
sa4ss::read_child("32model-description.Rmd") 
```



```{r render-34, results = "asis"}
sa4ss::read_child("34model-prestar-base-selection.Rmd")
```


<!--chapter:end:30model.Rmd-->

# Assessment Results
The base model parameter estimates along with approximate asymptotic standard errors are shown in Table \ref{tab:params} and the likelihood components are shown in Table \@ref(tab:params). Estimates of derived reference points and approximate 95 percent asymptotic confidence intervals are shown in Table \@ref(tab:referenceES). Estimates of stock size and status over time are shown in Table \@ref(tab:timeseries). 

The full r4ss plotting output is available in the supplementary material.

## Parameter Estimates

```{r parameters, include = FALSE, eval = TRUE, cache = TRUE}
# get parameter names from base model
estimated_pars <- model$parameters %>%
  dplyr::filter(!is.na(Active_Cnt)) %>%
  rownames()
```

The base model has a total of `r length(estimated_pars)` estimated parameters
(Figure \@ref(tab:params)) that can be grouped into the following
categories and are described in more detail in the following sections:

Biological parameters  
- 1 natural mortality parameter (female and male assumed the same)  
- 9 growth parameters   
    + 5 Schnute growth parameters (length at age 0 (females only), length at age 30 for both sexes, and $k$)    
    + 4 parameters controlling variability in growth, the CV in length at age 0    
  and the CV in length at age 30 with a linear ramp in length-at-age  (CV for young males was not estimated)  
            
Stock-recruit parameters  
- `r 2 + nrow(model$recruit)` recruitment parameters  
- $log(R_0)$ controlling equilibrium recruitment  
- Recruitment deviations parameters covering the range  
  `r min(model$recruit$Yr)`-`r max(model$recruit$Yr)`, with 
  `r min(model$recruit$Yr[model$recruit$era=="Main"])`-`r max(model$recruit$Yr[model$recruit$era=="Main"])`
  representing the "main" period modeled as a zero-centered deviation vector  
  
Index parameters  
- `r sum(sum(grepl("Q_extra", estimated_pars)))` extra standard deviation parameters
for indices  

Selectivity parameters  
- `r sum(grepl("Size_DblN", estimated_pars))` selectivity parameters, of which
`r sum(grepl("Size_DblN.*BLK", estimated_pars))` represented changes over time  

## Fixed parameters
* $h$ controlling the steepness of the stock-recruit relationship
* $M$ for males
* Selectivity parameters estimated at the bounds during model exploration were fixed in the pre-STAR model

## Growth Estimation
```{r, include=FALSE, echo = FALSE}
# calculate Linf and t0 from Schnute vB parameterization
unSchnute.fn <- function(Amin, Amax, Lmin, Lmax, k)
{
   Linf <- Lmin + (Lmax-Lmin)/(1-exp(-k*(Amax-Amin)))
   t0   <- Amin + Amax - (1/k)*log((exp(k*Amax)*Lmax - exp(k*Amin)*Lmin)/(Lmax-Lmin))
   out  <- c(Linf, t0)
   names(out) <- c("Linf","t0")
   return(out)
}
# vermilion example
# females 
female_growth <- unSchnute.fn(0, 30, model$MGparmAdj$L_at_Amin_Fem_GP_1[1], model$MGparmAdj$L_at_Amax_Fem_GP_1[1], model$MGparmAdj$VonBert_K_Fem_GP_1[1])


# for males,  apply exponential offsets to the female values
male_growth <- unSchnute.fn(0, 30,  
   model$MGparmAdj$L_at_Amin_Fem_GP_1[1]*exp(model$MGparmAdj$L_at_Amin_Mal_GP_1[1]),     model$MGparmAdj$L_at_Amax_Fem_GP_1[1]*exp(model$MGparmAdj$L_at_Amax_Mal_GP_1[1]),
   model$MGparmAdj$VonBert_K_Fem_GP_1[1]*exp(model$MGparmAdj$VonBert_K_Mal_GP_1[1]))
male_growth[3] <- model$MGparmAdj$VonBert_K_Fem_GP_1[1]*exp(model$MGparmAdj$VonBert_K_Mal_GP_1[1])

```


The southern California base model estimated reasonable growth parameters for female and male k, lengths at age 30, and CVs of length at age (both young and old). The male growth parameters were modeled as exponential offsets to female growth, with the male  $L_{age=0}$ and associated CV fixed to the estimates for females (7.7 cm and a CV of 0.09) because male estimates hit lower bounds. Female $k$ was estimated at 0.16, slightly lower than the estimates for males of $k$ of 0.18 (exponential offset of 0.13).  Females reached a larger size at $L_{age=30}$ of 55 cm than males, which reached 52 cm at estimated $L_{age=30}$ (Figure \@ref(fig:fittedgrowth)).  The CV’s of the $L_{age=30}$ for females and males were 0.077 and 0.058, respectively.

Estimates of the vonBertalanffy parameters transformed from the Schnute parameterization used by SS are below.  In both parameterizations of the growth equation, the $k$ has the same definition.
\begin{centering}

Females $L_{\infty}$ = `r round(female_growth[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Fem_GP_1[1], 3)`; $t_0$ = `r round(female_growth[2], 2)`

Males $L_{\infty}$ = `r round(male_growth[1])` cm; $k$ = `r round(male_growth[3], 3)`; $t_0$ = `r round(male_growth[2], 2)`

\end{centering}

\vspace{0.5cm}


## Natural Mortality Estimation

The southern California model estimates female natural mortality (*M*) and fixes male *M* at the same value. The estimated value of 0.125 (SE = 0.009) for both sexes is higher than the value estimated for northern California, but not inconsistent with the observed range of ages. Latitudinal gradients in natural mortality have been estimated for many species of rockfish, which is consistent with the lower estimates of M in the northern model.

## Fits to Conditional Age Composition
The following plots show the pearson residuals, mean age with Francis data weighting, and 
mean age and standard deviation in conditional age-at-length by fleet/survey:

- NWFSC hook-and-line survey: Figures \ref{fig:comp_condAALfit_residsflt8mkt0},
\ref{fig:comp_condAALfit_data_weighting_TA1.8_condAgeNWFSC_HKL}, and  \ref{fig:comp_condAALfit_Andre_plotsflt8mkt0_page1} - \ref{fig:comp_condAALfit_Andre_plotsflt8mkt0_page2}     

- WCGBT survey: Figures \ref{fig:comp_condAALfit_residsflt9mkt0_page1}- \ref{fig:comp_condAALfit_residsflt9mkt0_page2}, \ref{fig:comp_condAALfit_data_weighting_TA1.8_condAgeNWFSC_TWL}, and \ref{fig:comp_condAALfit_Andre_plotsflt9mkt0_page1}- \ref{fig:comp_condAALfit_Andre_plotsflt9mkt0_page4} 

- CDFW research survey:Figures \ref{fig:comp_condAALfit_residsflt11mkt0},
\ref{fig:comp_condAALfit_data_weighting_TA1.8_condAgeCDFW_RESEARCH}, and \ref{fig:comp_condAALfit_Andre_plotsflt11mkt0} 

- Early NWFSC hook-and-line survey: Figures \ref{fig:comp_condAALfit_residsflt12mkt0_page1}, \ref{fig:comp_condAALfit_residsflt12mkt0_page2},
\ref{fig:comp_condAALfit_data_weighting_TA1.8_condAgeEARLY_HKL}, and \ref{fig:comp_condAALfit_Andre_plotsflt12mkt0_page1} - \ref{fig:comp_condAALfit_Andre_plotsflt12mkt0_page3} 

Fits to the marginal and conditional age at length data sets were best for the NWFSC hook-and-line survey, which is not surprising given that this survey accounted for the majority of age at length observations (over 9000). Similar to the northern model, the largest residuals were associated with infrequently encountered, older individuals, and no significant residual patterns were apparent. The model was able to reproduce interannual changes in mean age reasonably well, with the exception of 2009, when observed average age was unusually high (~5 years higher than surrounding years), but also had the largest variance.

## Estimated Selectivity and Fits to Length Composition

The following plots show estimated selectivity (when not mirrored) and fits to the length composition for each 
fleet/survey:

* Commercial hook-and-line: Figures \ref{fig:endyr-selex-COM-HKL}, \ref{fig:sel03_len_timevary_surf_flt1sex1}, \ref{fig:len-pearson-COM-HKL}, and \ref{fig:mean-len-fit-COM-HKL}   
* Commercial net: Figures \ref{fig:endyr-selex-COM-NET}, \ref{fig:len-pearson-COM-NET}, and \ref{fig:mean-len-fit-COM-NET}
* Recreational retained PC: Figures \ref{fig:endyr-selex-REC-PC}, \ref{fig:sel03_len_timevary_surf_flt4sex1},  \ref{fig:len-pearson-REC-PC}  and \ref{fig:mean-len-fit-REC-PC}  
* Recreational discard PC Figures \ref{fig:endyr-selex-REC-PC-DIS}, \ref{fig:len-pearson-REC-PC-DIS}  and \ref{fig:mean-len-fit-REC-PC-DIS}
* Recreational retained PR: Figures \ref{fig:endyr-selex-REC-PR}, \ref{fig:sel03_len_timevary_surf_flt6sex1}, \ref{fig:len-pearson-REC-PR} and \ref{fig:mean-len-fit-REC-PR}  
* WCGBT survey: Figures \ref{fig:endyr-selex-NWFSC-TWL}, \ref{fig:endyr-selex-NWFSC-TWL}, \ref{fig:len-pearson-NWFSC-TWL}  and \ref{fig:mean-len-fit-NWFSC-TWL} 
* CDFW research survey: Figures \ref{fig:len-pearson-CDFW-RESEARCH} \ref{fig:mean-len-fit-CDFW-RESEARCH}  
* NWFSC hook-and-line survey: Figure \ref{fig:len-pearson-NWFSC-HKL}, and \ref{fig:mean-len-fit-NWFSC-HKL} 
* Early NWFSC hook-and-line survey: Figures \ref{fig:len-pearson-EARLY-HKL} and \ref{fig:mean-len-fit-EARLY-HKL} 
  
Fits to the time-aggregated length comps were best for the commercial, recreational, and NWFSC survey fleets Figure \@ref(fig:lenfits-all). The NWFSC trawl survey does not sample primary adult habitat types, resulting in a multi-modal length frequency distribution that is difficult for the model to reproduce Figure \@ref(fig:lenfits-all). Fits to the early CDFW research fleet are poor, but the data informing these years are relatively sparse in comparison to current sampling programs such as CRFS. Length composition data from the recreational fleets show evidence of modal progressions due to strong year classes (e.g., the 1999 year class showing up around 2002), do not show evidence of strong patterns in the pearson residual plots, and the model is able to track associated changes in mean length over time.


The commercial hook-and-line fleet (and mirrored commercial trawl fleet) were fit to time-varying asymptotic selectivity and the size a full selectivity shifts to smaller fish in the more recent time block (50 cm to 34 cm).  The most noticeable change in selectivity for the commercial fleet is the implementation of the CCAs and additional regulatory changes. Catches from the commercial net fishery declined prior to the CCAs.  The length compositions from the net fishery did not support a dome shaped selectivity and it was fixed to have asymptotic selectivity (Figure \@ref(fig:endyr-selex-COM-NET)).

Dome-shaped selectivity for the recreational PC and PR fleets are similar with the PR fleet encountering smaller fish than the PC fleet, whereas the recreational discards fleet does not select any fish larger than ~35 cm (Figures \@ref(fig:endyr-selex-REC-PC), \@ref(fig:endyr-selex-REC-PC-DIS), \@ref(fig:endyr-selex-REC-PR)). A number of regulatory changes (e.g., establishment of the CCAs, depth restrictions) supported time blocks in both recreational retained fleets resulting in narrower selectivity patterns in the 2000s.

Both fishery-independent hook-and-line surveys were fit to asymptotic selectivity because attempts to estimate dome-shaped selectivity resulted in poorly informed parameters (very large SEs) for terminal selectivity and the descending width. The length composition data from 2004-2013 for the NWFSC Hook-and-Line survey were fit as a ‘dummy’ fleet, and allowed to take a dome shape due to the lack of sampling inside the CCA where fish of larger size were observed. 

Peak selectivity for the WCGBTS was fixed at the smallest length bin (Figure \@ref(fig:endyr-selex-NWFSC-TWL)), and attempts to estimate other parameters (e.g., descending width) were unsuccessful, with the parameter hitting the lower bound near zero.

## Fits to Indices
The following plots show log-scale fits to the indices and residuals by fleet/survey:  
- MRFSS dockside PC survey: Figures \@ref(fig:log-cpue-REC-PC) and \@ref(fig:cpue-resid-REC-PC)  
- CDFW dockside PR survey: Figures \@ref(fig:log-cpue-REC-PR) and \@ref(fig:cpue-resid-REC-PR)  
- NWFSC hook-and-line survey: Figures \@ref(fig:log-cpue-NWFSC-HKL) and \@ref(fig:cpue-resid-NWFSC-HKL)  
- CDFW onboard CPFV survey: Figures \@ref(fig:log-cpue-REC-PC-ONBOARD) and \@ref(fig:cpue-resid-REC-PC-ONBOARD)  


Fits to the indices vary in quality.  Three of the four recreational indices represented 
the PC fleet. The MRFSS era dockside interview index was fit moderately well given the uncertainty 
in some years, but the model was not able to adequately reproduce the first and last observations of the time series or the rate of decline in the late 1990s, as indicated by a short run of negative residuals (1995-1998) (Figures \@ref(fig:log-cpue-REC-PC) and \@ref(fig:cpue-resid-REC-PC)).
The CDFW onboard index, which now contains 21 years of data was fit well and captures the trend from 
the standardized index; there was also not a strong pattern to the residuals 
Figures \@ref(fig:log-cpue-REC-PC-ONBOARD) and \@ref(fig:cpue-resid-REC-PC-ONBOARD)).

An additional variance parameter was estimated for the recreational PR dockside index.  The index was positively correlated with the base model predictions, but the relationship was not strong and most residuals shifted from positive to negative after 2011 (Figures \@ref(fig:log-cpue-REC-PR) and \@ref(fig:cpue-resid-REC-PR)).
The NWFSC hook-and-line survey index was fit well through 2016, with the model capturing a general trend of increasing abundance, but the model did not capture 
the pattern of increased abundance in the last three years. Since the survey moved into the CCAs in 2014, the increase since 2017 does not appear to be related to the change in survey design. Overall, the fit suggests that the index is weakly informative about changes in abundance for vermilion rockfish.
(Figures \@ref(fig:log-cpue-NWFSC-HKL) and \@ref(fig:cpue-resid-NWFSC-HKL)). 


## Derived Quantities
Vermilion spawning output in southern California was estimated to be 522 million eggs in 2021 (~95% asymptotic intervals: 262-781; Table  \@ref(tab:referenceES), which equates to a depletion level of 49% (~95% asymptotic intervals: 30%-70%; Table  \@ref(tab:referenceES); Figure \@ref(fig:depl)) in 2021. Depletion is a ratio of the estimated spawning output in a particular year relative to estimated unfished, equilibrium spawning output. Spawning output south of Point Conception declined rapidly throughout the 1970s, 1980s, and 1990s to a level below the Minimum Stock Size Threshold (MSST), but catches decreased enough in the 2000s for the stock to reach a stable level of spawning output (Table \@ref(tab:timeseries), Figure \@ref(fig:ssb)). Stock size is estimated to have been at the lowest level in the mid-1990s, but has since increased, in part due to an exceptionally strong recruitment in 1999, followed by several years of above-average recruitment. The stock is estimated to have been below the management target of B40% from 1986-2007 (Figure\@ref(fig:depl). Relative exploitation rates [(1-SPR) / (1-SPR50%)] increased through time, exceeding target levels from the mid-1970s through the late 1990s. Exploitation over the past decade has fluctuated around target levels (Figure  \@ref(fig:1-spr)), with catches almost entirely landed by the recreational sector. In 2021, vermilion biomass south of Point Conception is estimated to be above the target biomass level, while experiencing fishing intensity around the SPR fishing intensity target (Figure \@ref(fig:1-spr)). The equilibrium yield curve is shifted left, as expected from the Beverton-Holt steepness parameter (h=0.72)(Figures \@ref(fig:yield2) and \@ref(fig:yield3)).


The base model parameter estimates along with approximate asymptotic standard errors are shown in Table \ref{tab:params} and the likelihood components are shown in Table \@ref(tab:params). Estimates of derived reference points and approximate 95 percent asymptotic confidence intervals are shown in Table \@ref(tab:referenceES). Estimates of stock size and status over time are shown in Table \@ref(tab:timeseries). 

## Recruitment Deviations

Major recruitments (strong year classes) in southern California were consistently estimated by the primary sources of age data (NWFSC hook-and-line and trawl surveys), with a strong 1999 year class estimated even when either data set is removed (see sensitivity section). Other years with relatively high estimates of recruitment were 1983-84, 1999, and 2016 (Figures \@ref(fig:recdevs), \@ref(fig:bh-resids) and  \@ref(fig:phase)). These are consistent with estimates of strong year classes in other rockfish stock assessments. Due to ageing error, years adjacent to strong (or weak) cohorts are sometimes estimated as having similar deviations.

### Reference Points

Reference points were calculated using the estimated selectivities and catch distribution among fleets in the most recent year of the model, `r endyr`. 
Sustainable total yield (landings plus discards) was 
`r round(model$derived_quants[model$derived_quants$Label == 'Dead_Catch_SPR', 'Value'], 2)` mt when using an $SPR_{50\%}$ 
reference harvest rate. The spawning output equivalent to 40% of the unfished level ($SB_{40\%}$) was `r round(model$derived_quants[model$derived_quants$Label == 'SSB_SPR', 'Value'], 2)` 
million eggs. 

The `r endyr`. spawning biomass relative to unfished equilibrium spawning biomass is above the target of 40% of unfished levels (Figure \@ref(fig:depl)). 
The relative fishing intensity, $(1-SPR)/(1-SPR_{50\%})$, was above the management target (Figure \@ref(fig:1-spr)). 

Table \@ref(tab:referenceES) shows the full suite of estimated reference points for the base model and Figures \@ref(fig:yield2) and \@ref(fig:yield3) show the equilibrium curve based on a steepness value fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"], 2)`.

<!--chapter:end:35model-prestar-base-results-south.Rmd-->

# Assessment Model Diagnostics

## Sensitivity to Assumptions, Data and, Weighting

To better understand how data from individual fishery sectors or scientific surveys affected assessment results, we excluded data sets from the likelihood, one fleet at a time (referred to here as a “drop-one” analysis). “Fleet” in this sense refers to either a fishing fleet or a survey “fleet.” To do this, we set “lambdas” (multipliers for each likelihood component) equal to zero. This is equivalent to removing the data from the model. When composition data were excluded, the selectivity parameters for that fleet were fixed at the base model estimates to standardize the size and age composition of harvested fish. When abundance indices were excluded, relevant catchability and ‘extraSE’ parameters associated with the index were not estimated. Composition data weights for the remaining fleets were kept consistent with the base model values. Results from all the ‘drop-one’ runs were compared to the base model using time series plots and tables containing likelihood components, parameter estimates and derived quantities.

```{asis, echo = model.area=='SCA'}
For the southern California model, the NWFSC hook-and-line (HKL) survey is divided across two fleets (8 and 12; see survey description in the Fishery-Independent Data sources section). For consistency with other ‘drop-one’ runs, fleets 8 and 12 were excluded at the same time to remove all data associated with the hook-and-line survey. Removal of the HKL survey fleet (index, length comps, and age comps) resulted in larger estimates of unfished spawning output (Figure \@ref(fig:drop-spawnbio)), and affected the trend in spawning biomass in recent years. Only removal of the REC_PC fleet had a noticeable effect on spawning output in the terminal year, but the difference was well within the estimated range of uncertainty from the base model. Relative spawning output (‘depletion’) estimates showed little change relative to the range of plausible outcomes predicted by the base model (Figure \@ref(fig:drop-bratio)). Removal of the REC_PC fleet reduced the magnitude of negative recruitment deviations estimated in the 1970s, as well as the strength of the 1999 year class (Figure \@ref(fig:drop-recdev)), but most general patterns in recruitment were consistent across the set of drop-one sensitivity tests. Changes in likelihoods, parameter estimates and derived quantities are recorded in Tables \@ref(tab:drop-one) and \@ref(tab:drop-one2). Comparison of likelihoods among drop-one scenarios should be treated with caution due to changes in the data sets that were fit in each model run.
```

```{asis, echo = model.area=='NCA'}
Drop-one analysis of the northern California assessment revealed slightly larger variability in spawning output trends relative to the south, but all runs were still within the range of uncertainty estimated by the base model (Figure \@ref(fig:drop-spawnbio)). Removal of most fleets had little effect on terminal stock status, with best estimates in the vicinity of target biomass levels (Figure \@ref(fig:drop-bratio)). An exception was removal of the REC_PC fleet, which caused the best estimate of terminal depletion to drop just above the minimum stock size threshold. This suggests that the REC_PC data sets, together, favor a less-depleted stock relative to data from the other fleets. The strength of the 2016 year class is sensitive to the removal of fleet-specific data sets (Figure \@ref(fig:drop-recdev)). Removal of the REC_PR fleet produces the largest estimates of 2016 cohort size, and removal of the NWFSC_TWL fleet estimates a 2016 deviation that is less than half as large (but still positive). Uncertainty in the strength of this recent year class should be taken into consideration for short term forecasts of stock abundance and yield. Changes in likelihoods, parameter estimates and derived quantities are recorded in Table \@ref(tab:drop-one). Comparison of likelihoods among drop-one scenarios should be treated with caution due to changes in the data sets that were fit in each model run.
```

### Sensitivity to Catch Uncertainty
```{asis, echo = model.area=='SCA'}
To evaluate the influence of highly uncertain catch histories, we developed several sensitivity analyses.  A “typical” sensitivity is to both halve and double historical catches, which tend to be far more uncertain than catches in the more recent and better documented era, particularly for rockfish (Sebastes).  This is because historically most rockfish were landed in mixed stock market categories such as “unspecified rockfish” or “group red rockfish,” and the species composition of these market categories were not sampled until the recent era (1978 in central and northern California, 1983 in the southern California Bight).  However, as described in the historical catch section, recent evaluations have suggested that historical catches in the Southern California Bight may be more uncertain than previously realized.  Specifically, vermilion rockfish was explicitly described as “one of the most important commercial species, it is one of the three leading species (of rockfish) in Southern California” [@Roedel1953].  The other two of the most important commercial species in southern waters were bocaccio, which is estimated to represented nine percent of total rockfish catch in southern waters between 1916 and 1950, and 20% between 1916 and 1968; and chilipepper, estimated to represent 11% of the catch between 1916 and 1950 and 14% between 1916 and 1968.  However, the catch reconstruction estimated that vermilion catch to be less than five percent of the historical total for this region, while several species that were not described or described as “minor” importance were estimated to represent 10% or more of the catch (including bank, blackgill, bronzespotted and cowcod rockfish).  The former two in particular are more deeply distributed slope species that were unlikely to represent a large fraction of catches in the 1920s and 1930s [@Miller2014].  

One partial explanation for the discrepancy is that market category 959, which is described as “group red” rockfish was rarely used until the late 1930s and early 1940s, but likely accounted for much of the vermilion catch from that period onward.  Thus, vermilion would have been included in other market categories, such as market category 250, “unspecified rockfish,” which accounted for half of the total rockfish catch early in the historical period.  By the time species composition data were actually collected in the early 1980s, that market category would have very few vermilion, as most would have been sorted into “group red” or the “vermilion” (249) market categories.  Consequently, when recent species composition data were applied to the historical market category catches, the fraction estimated to be vermilion would be biased low, and vermilion rockfish would be underrepresented in the earliest portion of the landings history.  To evaluate a plausible alternative to the current estimates, we evaluated the consequences of assuming that both 10% and 20% of the total rockfish catches in the Southern California Bight were vermilion rockfish (comparable to the other two “leading species”).  This effect would have likely been reduced from the late 1950s and early 1960s onward, thus for these sensitivities we only applied the higher catch levels to the pre-1969 time period (e.g., the time period of the historical reconstruction).  These sensitivities were done in addition to both halving and doubling catches (both commercial and recreational) for the entire pre-1980 time period. 

The halving and doubling of catches did lead to substantive (but not enormous) differences in estimates of stock status, with a slightly more pessimistic perception in the doubling of historical catches and a slightly more optimistic perception in the halving (Figures \@ref(fig:sens2-depl) and \@ref(fig:sens2-spr)).  However, the treatment of only pre-1969 commercial catches did not lead to substantive changes in the perception of stock status, only a slight scaling of historical spawning output and an increase in historical harvest rates, resulted in a considerably earlier and more rapid stock decline relative to the base model.  Associated with that increased scaling of historical spawning output was a slight increase in the equilibrium MSY level, by one to three tons depending on the scenario.  The halving and doubling of all historical catches prior to 1980 had a more substantive effect on the estimated equilibrium MSY level, decreasing by approximately four tons and increasing by ~18 tons, respectively.  However, there is less evidence to support a doubling of both relatively recent (60s through 70s) commercial catches and of recreational catches at this time.  Given the relatively modest influence on the model results, and the need for more rigorous investigations and improvements to historical catch estimates (which are best done as an overarching effort on all historical catches), additional efforts to improve these estimates are likely more appropriate for future research recommendations.  
```


```{asis, echo = model.area=='NCA'}
To evaluate the influence of highly uncertain catch histories, the we both halved and doubled the  historical catches in the pre-STAR base model.  The historical catches tend to be far more uncertain than catches in the more recent and better documented era for rockfish (*Sebastes* spp.), as historically most rockfish were landed in mixed stock market categories.  However, relative to the somewhat elevated uncertainties described in the historical catch sensitivity analysis for southern vermilion, there is less evidence for substantive bias in historical catches of vermilion rockfish north of Point Conception, where there is better evidence that vermilion made up a relatively modest fraction of the total catch. 

The halving and doubling of historical catches in the northern model did lead to substantial differences in estimates of stock status (Figures \@ref(fig:sens2-depl) and \@ref(fig:sens2-spr)). A doubling of historical catches restuled in a stock slightly above the MSST, and a substantially larger predicted biomass when historical catches were halved.  Equilibrium MSY estimates were also larger with greater historical catches (by approximately 32 tons) and reduced with lower historical catches.  The relative change in model fit, as reflected by the total negative log likelihood, was modest, with a slightly improved fit in the lower historical catch scenario, and a slightly poorer fit in the higher historical catch scenario. 
```


## Likelihood Profiles

Likelihood profiles were conducted for natural mortality (M), steepness (h) and the log of R0 (unfished recruitment) by fixing these parameters across a range of values and continuing to estimate the remaining parameters assuming the base model framework.  

```{asis, echo = model.area=='SCA'}
The profiles for natural mortality in the southern base model (Figures \@ref(fig:m-profile), \@ref(fig:m-depl), and \@ref(fig:m-spawn)) suggest that this parameter is reasonably well informed between a range of approximately 0.11 and 0.14.  The profiles suggest a somewhat commonly observed phenomena of tension between the age data, which would suggest a lower natural mortality rate, and the length and index data, which tend to fit the data better with a higher value for M.  The notable exceptions to these generalizations include the NWFSC hook and line survey index, which fits the data better with a considerably lower M, and the commercial fisheries data (hook and line, and setnet), which also fit the data better with a lower M.  Intuitively, spawning output increased with lower natural mortality rate estimates, while the estimate of relative stock status was more pessimistic, while the converse was true (lower spawning output, more optimistic stock status estimates) with higher M values. 

A profile of steepness was conducted on values ranging from 0.30 to 0.90 in 0.10 increments.  The resulting likelihood profiles (by component, and by component and fleet) are shown as Figure \@ref(fig:h-profile), while model trajectories (spawning output and relative depletion) are shown as Figures \@ref(fig:h-depl), and \@ref(fig:h-spawn).  The likelihood profiles show that the overall best fit to the data is associated with high steepness values, although the data were generally uninformative above steepness values of 0.5.  Overall the length data were not very informative, and there were some odd changes in the likelihood in some fleets at very low (0.3) steepness values.  Similarly the age data were only marginally informative, and suggested higher steepness values in general.  Most of the indices also suggested higher steepness values, particularly the NWFSC hook and line survey index, although the Rec PC index had a significantly better fit at lower steepness values.  Predictably, spawning output scaled down with higher steepness values and up with lower values, however the estimate of stock status in 2021 varied relatively little across the range of values.  Interestingly the most optimistic runs with respect to relative stock status were both the highest and the lowest values in the profile, although the overall difference was negligible for the ending year. The higher steepness runs were more pessimistic with respect to historical (late 1980s through the early 2000s) stock status.  
 
A profile on the log of unfished recruitment (Ln R0) was conducted on values ranging from 6.2 to 6.9 (the base model estimate in base model was 6.66).  In general, age data was better fit by the model with lower values of R0, survey data (as well as recruitment via likelihood penalties) were better fit by higher R0 values, and the cumulative fit to length data was best close to the base model estimate (Figure \@ref(fig:r0-profile)).  The components by fleet were variable in the cases of length composition data, in which the commercial hook and line fishery and the Rec PC data fit better with lower R0 values, while the remaining fleets fit better with higher R0 values or were non-informative (Figures \@ref(fig:r0-depl) and \@ref(fig:r0-spawn)).  Counterintuitively, spawning output is estimated to be greater with the higher R0 values and lower with the lower R0 values, as a result of corresponding model changes in the estimate of the natural mortality rate (which is estimated to be much lower in the low R0 model).  This results in the lower R0 runs also being more pessimistic, as the lower R0 runs were associated with considerably lower natural mortality rates.  Additional profiles in which M is fixed may be helpful in evaluating model performance across many of the key model parameters.
```

```{asis, echo = model.area=='NCA'}
The profiles for natural mortality in the northern model (Figures \@ref(fig:m-profile), \@ref(fig:m-depl), and \@ref(fig:m-spawn)) suggest that this parameter is reasonably well informed between a range of approximately 0.07 and 0.11, a somewhat lower range of values than was estimated for the southern model.  Interestingly, profiles for natural mortality in the north indicated that the length data were better fit by the model with a lower natural mortality rate, and the age data were better fit by a higher rate, a result that is in contrast to that observed in the southern model.  Most of the indices were also better fit by a higher natural mortality rate, although the Deb Wilson-Vandenberg Index and the onboard observer index were better fit with lower natural mortality rates.  As is typical, spawning output increased with decreasing natural mortality, such that the model estimate with M = 0.05 was 1.5 times that of the model estimate when M was assumed to be 0.12. Similarly, the model estimated depletion in 2020 was well above the target level, close to 70%, for the M=0.12 model, while the ending depletion was just barely over the minimum stock size threshold of 25% of the unfished level in the M=0.05 model (Figure \@ref(fig:m-depl)).  

A profile of steepness was conducted on values ranging from 0.30 to 0.90 in 0.10 increments.  The likelihood profiles (by component, and by component and fleet) are shown as  Figure \@ref(fig:h-profile), and the resulting model trajectories (spawning output and relative depletion) are shown as Figures \@ref(fig:h-spawn) and \@ref(fig:h-depl).  The likelihood profiles show that the overall best fit to the data is associated with high steepness values, although the data were generally uninformative above steepness values of 0.5.  Overall the length data were not very informative, and there was some odd jumps in the likelihood in some fleets at very low (0.3) steepness values.  Similarly the age data were only marginally informative, and suggested higher steepness values in general.  Most of the indices also suggested higher steepness values, particularly the NWFSC hook and line survey index, although the Rec PC index had a significantly better fit at lower steepness values.  Predictably, spawning output scaled down with higher steepness values and up with lower values, however the estimate of stock status in 2021 was actually more optimistic with lower steepness values and more pessimistic with higher steepness values.  The higher steepness runs were also more pessimistic with respect to historical (late 1980s through the early 2000s) stock status.       

A profile on the log of unfished recruitment was conducted on values ranging from 5.7 to 6.4 (the base model estimate was 6.07), and is shown as Figure \@ref(fig:r0-profile).  In general, age data was better fit by the model with higher values of R0, as was most of the survey data (as well as recruitment via likelihood penalties).  The DWV_onboard survey index and the Rec_PR were both somewhat better fit by the lower R0 values. All length data were either better fit to lower R0 values or were uninformative.  As with the southern model, spawning output is estimated to be greater with the higher R0 values, although the overall difference in scaling was minimal for early years.  Also consistent with the southern model result, the northern model result was more pessimistic with the lower R0 values, with the low R0 values being below the MSST and higher R0 values suggesting that relative spawning output is well above target levels (Figures \@ref(fig:r0-depl) and \@ref(fig:r0-spawn)). As with the southern model, this is a result of corresponding model changes in the estimate of the natural mortality rate (which is estimated to be much lower in the low R0 model), such that the R0 profile is in many ways simply providing the same information as the profile on the natural mortality rate.  Additional profiles in which M is fixed may be helpful in evaluating model performance.
```



## Retrospective Analysis
```{asis, echo = model.area=='SCA'}
A five year retrospective analysis was conducted on the southern base model by sequentially removing data, beginning with data from the year 2020.  Figures \@ref(fig:retro-spawnb), \@ref(fig:retro-bratio), and \@ref(fig:retro-recdev) show the estimated spawning output, the estimated depletion, the recruitment deviation estimates and the estimated fit to the NWFSC hook and line survey index (which appeared to be the index fit most affected by the analysis).  The greatest impact was the declining estimate of the strength of the 2016 year class, similar to the northern model, with the interesting result that with the loss of only 1-3 years of data the model attributes greater recruitment to 2015 relative to the base model, with variable responses among other recruitment estimates.  This change is associated with an increasingly pessimistic perception of stock status, although the overall scaling of spawning output is relatively modest.  This shift is understandably associated with the change in population trajectory as data supporting strong recent recruitment are removed.  Beyond this shift, this analysis does not suggest that there are substantive retrospective patterns (Table \@ref(tab:retro)).  Note that data weighting was not conducted on these models.
```


```{asis, echo = model.area=='NCA'}
A five year retrospective analysis was conducted on the northern base model by sequentially removing data, beginning with data from the year 2020.  Figures \@ref(fig:retro-spawnb), \@ref(fig:retro-bratio), and \@ref(fig:retro-recdev) show the estimated spawning output, the estimated depletion, the recruitment deviation estimates and the estimated fit to the CCFRP index (which was the index most affected by the analysis).  The greatest impact of sequentially removing recent data was the declining estimate of the strength of the 2016 year class, a result similar to the southern model, as the length composition and index data that informed those year classes were removed.  There was also a slightly lesser reduction in the strength of the 2013 and 2014 year classes.  However, aside from a modest rescaling upwards of recruitment deviations, the spawning output and depletion estimates did not change by any significant measure, suggesting no concerning retrospective patterns (Table \@ref(tab:retro)).  Note that data weighting was not conducted on these models. 
```


## Other Model Sensitivities
Results from the pre-STAR base model were compared to several alternative model specifications, as described below.

- Estimate the Beverton-Holt steepness parameter (*h*) rather than fixing it at the prior mean (*h*=0.72); estimate uncertainty intervals for comparison to base
- Start recruitment deviations 5 years earlier than the base model configuration
- Start recruitment deviations 5 years later than the base model configuration
- Compare results based on the McAllister-Ianelli data weighting method (for composition data) to the Francis method used for the base model.
- Mirror the recreational discard fleets’ selectivity curves to the corresponding retained fleets (PC or PR) rather than fitting to discard length comps as in the base model.


```{asis, echo = model.area=='NCA'}
Trends in spawning output for the northern California assessment model were generally robust to this set of sensitivities (Figure \@ref(fig:sens1-spawnb)). Best estimates from all runs were within the estimated range of uncertainty for the base model. Steepness was estimated at a higher value than the prior mean (estimated at 0.94 vs. fixed at 0.72). Similarly, stock status did not vary greatly among this set of sensitivity runs, with only a minor increase in 2021 relative spawning output when using McAllister-Ianelli weights and a slight decrease when estimating steepness (Figure \@ref(fig:sens1-bratio)). The use of McAllister-Ianelli weights had the greatest impact on estimated recruitment deviations (Figure \@ref(fig:sens1-recdev)). This weighting method significantly reduced the magnitude of the 2016 year class, and generally increased the variance of the estimated deviations. The McAllister-Ianelli method gives greater weight to the composition data for this model (Table \@ref(tab:sens1)), and resulted in lower estimates of the male and female natural mortality rates (Table \@ref(tab:data-weights)).
```


```{asis, echo = model.area=='SCA'}
Trends in spawning output for the southern California assessment model were generally robust to this set of sensitivities, with the exception of recent estimates of spawning output which were much lower when using McAllister-Ianelli data weights, relative to the Francis method used in the base model (Figure \@ref(fig:sens1-spawnb)). The model tuned to McAllister-Ianelli weights was below target biomass, while the other models that used Francis weights showed similar trends in depletion and were above target biomass (Figure \@ref(fig:sens1-bratio)). The McAllister-Ianelli approach estimated a natural mortality rate that was about 20% lower than the Francis method (Tables \@ref(tab:drop-one) and \@ref(tab:drop-one2)). Best estimates from all runs were within the estimated range of uncertainty for the base model. Steepness in the southern region was estimated at a similar value than the prior mean (estimated at 0.77 vs. fixed at 0.72), and estimation of this parameter did not have a large effect on uncertainty in spawning output or recruitment deviations. The use of McAllister-Ianelli weights had the greatest impact on estimated recruitment deviations (Figure \@ref(fig:sens1-recdev)). This weighting method increased the variance of the estimated deviations as well as the estimated strength of the 1999 year class, relative to the models using the Francis approach. Changing the start date of the recruitment deviations had almost no effect. The McAllister-Ianelli method gives greater weight to the composition data for this model (Table \@ref(tab:sens1)).
```

## Unresolved Problems and Major Uncertainties

```{asis, echo = model.area=='NCA'}
This assessment treats populations north and south of Point Conception as separate, but there is likely larval or juvenile dispersal, and potentially some adult movement, among these areas.  Dispersal and movement rates are not well known.

The primary fishery-independent survey for west coast groundfish, the NWC WCGBTS, does not sample rocky habitats where most vermilion rockfish are found, and thus does not provide a robust index of abundance.  An alternative survey, the CCFRP hook and line survey, provides a good signal for vermilion rockfish, including relative abundance and demographic structure in marine protected areas, but has a limited depth distribution and thus only reflects abundance of smaller, younger individuals. Increasing spatial management will continue to have impacts on the robustness of fishery-dependent abundance and demographic data to inform assessment models.  

In addition to not including data from closed areas, many of the fishery dependent indices are noisy, and some are not particularly well fit, such as the rec PR index.

Age data are limited and consequently growth and natural mortality estimates are uncertain.  There is an unusual pattern of tension among data sources inferred by the likelihood profiles, with age data suggesting a higher natural mortality rate and length data suggesting a lower *M*.  This is opposite the pattern seen in the southern assessment, and (very generally speaking) many other west coast groundfish assessments.

The model estimates a series of very low recruitment events throughout most of the 1970s, a period in which many other rockfish in this region experienced high levels of recruitment.  Recruitment patterns in more recent years generally follow those for other stocks.  It is possible that selectivity patterns changed, data are biased, model misspecification, or unknown ecosystem interactions could be responsible for this pattern.  
```


```{asis, echo = model.area=='SCA'}
Uncertainty around the magnitude of historical catches may be higher for this stock in this region, as some accounts suggest considerably higher historical catches than estimated in the 2010 catch reconstruction.  

The primary fishery-independent survey for west coast groundfish, the NWC WCGBTS, does not sample rocky habitats where most vermilion rockfish are found, and thus does not provide a robust index of abundance.  The NWFSC hook and line survey provides demographic and relative abundance data throughout the Southern California Bight, with the exception of some state closed areas, and the results of this survey, as well as known spatial management measures (e.g,. CCAs, state MPAs) as well as anecdotal accounts of spatial patterns in fishing effort indicate heterogeneity in fishing effort that likely bias fishery-dependent data sources.

While recent age data are robust, based primarily on the NWC hook and line data, historical age data (both fishery dependent and fishery independent) are very limited.  The likelihood profiles suggest a somewhat commonly seen pattern of tension among data sources, with age data suggesting a lower natural mortality rate and length data (as well as most index data) suggesting a higher M.  Natural mortality appears to be reasonably well estimated but is still uncertain, and seems to have the greatest influence on scaling the relative biomass and stock trajectory. 

The model estimates a series of very low recruitment events through the late 1970s and early 1980s, a period in which many other rockfish in this region experienced high levels of recruitment.  Recruitment patterns in more recent years generally follow those for other stocks.  It is possible that selectivity patterns changed, data are biased, model misspecification, or unknown ecosystem interactions could be responsible for this pattern.  
```

<!--chapter:end:36model-uncertainty.Rmd-->

# Harvest Projections and Decision Tables

**This section will be completed after the STAR panel**
<!--
Projections of OFL (mt), ABC (mt), age 10+ biomass (mt), spawning output (billions of eggs), and depletion (% of unfished spawning output) are shown for the default harvest control rule in Table 62. Catch estimates for 2021 and 2022 are based on GMT recommendations (M. Mandrup, CDFW; pers. comm.), with frog mt for commercial and frog mt for recreational fleets. Projections assume a constant allocation among fleets equal to the recommended catch for 2021 and 2022 (frog% commercial, frog% commercial).
-->

## Regional Management and Spatial Management Considerations

Over the last several decades, spatially explicit management measures at both the state and federal/management council level have been implemented to achieve a wide range of marine resource and fishery management objectives. Depth restrictions to commercial and recreational fisheries in the Rockfish Conservation Areas (RCAs) and the Cowcod Conservation Areas (CCAs) are key among those, as are the suite of total and partial exclusion of commercial and recreational fishing activities in the California statewide network of Marine Protected Areas (MPAs). While the former are associated with explicit fisheries management objectives, the latter have a suite of ecological and economic objectives, most of which are not specific to, nor integrated across, the fisheries management arena. Despite this, both types of spatial management measures are expected to result in various biological, ecological, and socioeconomic effects within and adjacent to their boundaries.  All of these effects have the potential to influence the nature and quality of the data used to inform stock assessments of species that reside in these areas, including vermilion rockfish.

Regardless of the management objective, spatial closures are expected to increase the spatial heterogeneity in abundance and size or age structure of fished stocks. This greater spatial variability can complicate the assumptions made in stock assessment models, particularly the assumption that the densities and demographic structure of assessed populations are relatively homogeneous, at least across predictable habitat types such as bathymetric gradients or substrate types [@Punt2004; @Field2006; @Berger2017].  Although a wide range of factors above and beyond spatial management measures can also lead to violations of those assumptions, and the challenge is intuitively less problematic for populations with high movement rates and/or high population turnover, the challenge can be particularly important for longer lived populations with lower movement rates.  The challenge can best be summarized by the result that the more effective MPAs or other closed areas are at protecting populations within them, the more likely it is that traditional assessment approaches will be biased or more uncertain.  

If the spatial closures also prevent fisheries independent surveys from evaluating the relative abundance and demographic structure of managed populations, the challenges in developing robust population models, and thus robust management advice, become even more severe.  While spatially explicit assessment models provide a means of more explicitly addressing these challenges, such models are computationally intensive, require robust data from the specific areas being modeled, and may also require detailed information regarding movement and dispersal rates [@McGilliard2015; @Berger2017; @Punt2020; @Cadrin2020].  Moreover, the complexity of these spatial models increases substantially if the size and location of closed areas changes over time, as many of the more “fisheries management based” closures (e.g., RCAs) have in California groundfish fisheries.  Thus, such approaches may be less feasible for more data limited stocks, such as northern and southern vermilion rockfish, at least in the near term.  However, the fact that both the northern and southern assessment models are informed by fishery-independent surveys that include habitats both inside and outside area closures provides some hope for greater recognition of spatial factors in future assessments.  


# Research Recommendations
We recommend the following research be conducted before the next assessment:

- Investigate the structure of complex and contribution of each species to the 
vermilion/sunset complex. Investigate possible spatial differences in biological parameters within 
a single species and also between the two species. Little biological data for south of 
Point Conception or north of Point Arena were available for this assessment and is needed 
to better under biological parameters. 
  + Conduct life history studies
  + Conduct research to identify the proportion of each species in population and in catches

- Take a closer look at historical catch reconstructions and 
all other historical data sources.

- Refine CCFRP survey index to look at alternative possible model structures, including 
a hierarchical structure and random effects. The CCFRP survey is the only 
fishery-independent survey available for nearshore rockfish sampling the nearshore rocky 
reef habitats. As of this assessment, only two years of coastwide data are available, 
and the index was limited to the site in central California that have been monitored 
since 2007.

- Continue to investigate the most appropriate model structure for the NWFSC HL survey index.
The NWFSC HL survey is the only long-term fishery-independent survey in rocky (untrawlable) habitat 
in the Southern California Bight. We also recommend evaluating how to structure the NWFSC Hook-and-Line survey index given its expansion into the CCA, also independent analysis of information content in NWFSC Hook-and-Line survey.Increased spatiotemporal sampling around Pt. Conception would aid in identifying stock boundaries.

- Utilize existing ROV survey data sources
  + SWFSC Submersible Survey of the Cowcod Conservation Areas [@Yoklavich2007]. 
  +  This was a line-transect survey designed to estimate cowcod abundance in 2002 
  conducted from a submersible inside the CCAs.  Originally, only cowcod were enumerated from the video footage.  Over the last few years, the SWFSC has re-analyzed the video footage to enumerate other rockfish species. 
    + The SWFSC Fishery Resource Division (FRD) conducted a survey of potential cowcod habitat between Point Conception and the U.S. – Mexico border from October through December of 2012 [@Stierhoff2013].
    +  SWFSC staff are submitting proposals to conduct an additional submersible survey in the southern California Bight
    + CDFW ROV survey data


- Collection of length and age data are recommended for both the commercial and 
recreational fisheries.  Very little age data are available from either fishery for 
vermilion and sunset rockfishes.

- Investigate possible environmental drivers/co-variates for biological parameters, 
particularly for recruitment.

- Resolve differences between CalCOM and PacFIN expanded length composition data sets. 




<!--chapter:end:40management.Rmd-->

\clearpage

# Acknowledgments (not required for draft assessments)

<!--chapter:end:41acknowledgements.Rmd-->

\clearpage
\floatplacement{table}{H}

# Tables

```{r render-51, results = "asis"}
sa4ss::read_child("51tables-execsummary.Rmd")
```



```{r render-52, results = "asis"}
sa4ss::read_child("52tables-catch.Rmd")
```



```{r render-54, results = "asis"}
sa4ss::read_child("54tables-compsamplesize.Rmd")
```

```{r render-56, results = "asis"}
sa4ss::read_child("56tables-results.Rmd")
```


```{r render-57, results = "asis"}
sa4ss::read_child("57tables-uncertainty.Rmd")
```

<!--chapter:end:50tables.Rmd-->

\clearpage
# Figures


```{r render-61, results = "asis"}
sa4ss::read_child("61figures-data-catches.Rmd")
```


```{r render-62, results = "asis"}
sa4ss::read_child("62figures-lengths.Rmd")
```


```{r render-63, results = "asis"}
sa4ss::read_child("63figures-biology.Rmd")
```

\FloatBarrier

```{r render-64, results = "asis"}
sa4ss::read_child("64figures-selectivity-diagnostics.Rmd")
```

\clearpage
\FloatBarrier


```{r render-65, results = "asis"}
sa4ss::read_child("65figures-lenfits.Rmd")
```



\FloatBarrier

```{r render-67, results = "asis"}
sa4ss::read_child("67figures-indices.Rmd")
```

\FloatBarrier

```{r render-67a, results = "asis"}
sa4ss::read_child("67afigures-caal.Rmd")
```

\FloatBarrier

```{r render-68, results = "asis"}
sa4ss::read_child("68figures-timeseries.Rmd")
```

\FloatBarrier

```{r render-68a, results = "asis"}
sa4ss::read_child("68a-figures-recruit-refpoints.Rmd")
```

\FloatBarrier

```{r render-69, results = "asis"}
#if(model.area=="NCA"){
sa4ss::read_child("69figures-sens-likeli-retro.Rmd")
# } else {
#   sa4ss::read_child("69figures-sens-likeli-retro-south.Rmd")
# }
```

<!--chapter:end:60figures.Rmd-->

\clearpage

# Appendix

## Detailed Fit to Length Composition Data{#append-fit} 


```{r, results='asis'}
plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(mod_loc, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\clearpage


## MRFSS Dockside Index of Abundance {#mrfss-index}

```{r mrfss-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_SCA.md") 
```
  
\clearpage
 
## California CPFV Onboard Index of Abundance {#cpfv-index}

```{r ca-cpfv-onboard-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_SCA.md") 
``` 

\clearpage

## CRFS PR Dockside Index of Abundance {#pr-index}

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_SCA.md")
``` 

\clearpage

## NWFSC Hook-and-Line Survey Index of Abundance {#nwfschl-index}

```{r nwfschl-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_NWFSC_HL_writeup_SCA.md")
``` 


\clearpage

## WCGBTS Index of Abundance {#wcgbts-index}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_SCA.md")
``` 

\clearpage

## Recreational Regulations {#regs-graphic}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_SCA.md")
``` 

\clearpage 


# References
       



<!--chapter:end:70appendices-south.Rmd-->

