---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
params:
    model: "south"
preamble: |
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{placeins}
  - \usepackage[inner]{showlabels}
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
lang: en
papersize: a4
---

<!-- Common lat/long 
Cape Mendocino, Pt. Conception and OR border -->
\newcommand\CapeM{$40^\circ 10^\prime N$}
\newcommand\PtC{$34^\circ 27^\prime N$}
\newcommand\CAOR{$42^\circ 00^\prime N$}


```{r, setup, include=FALSE}
rmarkdown::find_pandoc(version = "2.14.0.3")
```


```{r opts, include = FALSE}

library(kableExtra)
library(dplyr)
library(ggplot2)
library(tidyr)
library(rmarkdown)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })
options(knitr.duplicate.label = "allow") #allow duplicate labels - needed for longtable
options(knitr.kable.NA = '') #print blank cells in tables with NA
#knitr::knit_hooks$set(crop = knitr::hook_pdfcrop) #crop figures
#knitr::knit_hooks$set(optipng = knitr::hook_optipng) #optimize figure size


source("C:/Stock_Assessments/VRML_Assessment_2021/GitHub/Vermilion_2021/code/dir_recent.R")
dir.path <- ifelse(params$model=="north",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/NCA/",
             "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/SCA/")
model.dir <- dir_recent(dir = dir.path, pattern = "Verm")
base_loc <- paste0(model.dir,"/")


if (is.null(params$model) & file.exists("00mod.Rdata")) {
  stopifnot(file.exists("00mod.Rdata"))
  load("00mod.Rdata")
} else {
  load(dir(base_loc, pattern = "00mod.Rdata", full.names = TRUE))
}

model.area <- ifelse(params$model=="north", "NCA", "SCA")
spp = 'vermilion rockfish'
Spp = 'Vermilion rockfish'
fig_loc = paste0(getwd(), "/figures")
base_loc_plots = paste0(base_loc,"plots")
table_loc = paste0(getwd(), "/tables/")
tex_tables_loc = paste0(getwd(),"/tex_tables/", params$model)
tex_parent_loc = paste0(getwd(),"/tex_tables/")
#move the tex tables to the parent folder depending on which model you're working on 
#best solution I have so far
files <- list.files(path = tex_tables_loc, full.names = TRUE)
files_new <- gsub(dirname(files[1]), tex_parent_loc, files)
for (i in 1:length(files)){
  file.copy(files[i], files_new[i])
}


# model_loc = "C:/Stock_Assessments/VRML_Assessment_2021/Model_files/"



if(params$model=="north"){
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "Deb Wilson-Vandenberg onboard survey",
                           "West coast groundfish bottomfish trawl survey",
                           "recreational PC onboard survey",
                           "Abrams thesis research survey",
                           "SWFSC groundfish ecology survey",
                           "California Collaborative Fisheries Research Project survey")
} else {
model$FleetNames_parsed <- c("commercial hook-and-line fishery",
                           "commercial trawl fishery",
                           "commercial net fishery",
                           "recreational PC retained fishery",
                           "recreational PC discard fishery",
                           "recreational PR retained fishery",
                           "recreational PR discard fishery",
                           "NWFSC hook-and-line survey",
                           "West Coast Groundfish Bottomfish Trawl Survey",
                           "recreational PC onboard survey",
                           "CDFW reserach (aka green binder)",
                           "Dummy fleet")
}

model$FleetNames_label <- stringr::str_replace_all(model$FleetNames, "_", "-")

fleet_info = data.frame(cbind(model$fleet_ID, model$FleetNames, model$FleetNames_label, model$FleetNames_parsed))
colnames(fleet_info) = c("fleet_ID", "FleetNames", "FleetNames_label", "FleetNames_parsed")

plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))

```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: E. J. Dick
    code: 1
    first: E
    middle: J
    family: Dick
  - name: Melissa H. Monk
    code: 1
    first: M
    middle: H
    family: Monk
  - name: Tanya L. Rogers
    code: 1
    first: T
    middle: L
    family: Rogers
  - name: John C. Field
    code: 1
    first: J
    middle: C
    family: Field
  - name: Emma M. Saas
    code: 1
    first: E
    middle: M
    family: Saas
author_list: Dick, E.J., M.H. Monk, T.L. Rogers, J.C. Field, E.M. Saas
affiliation:
  - code: 1
    address: Southwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110
      McAllister Way, Santa Cruz, California 95060
address: ^1^Southwest Fisheries Science Center, U.S. Department of Commerce, National
  Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110 McAllister
  Way, Santa Cruz, California 95060
---

<!--chapter:end:00authorssouth.Rmd-->

---
bibliography: 
  - sa4ss.bib
---

<!--chapter:end:00bibliography.Rmd-->

---
title: DRAFT The status of Vermilion Rockfish (_Sebastes miniatus_) and Sunset Rockfish (_Sebastes crocotulus_) in U.S. waters off the coast of California south of Pt. Conception in 2021
---


<!--chapter:end:00titlesouth.Rmd-->

\newpage

\includegraphics{cover_photo.png}
Two fish of the vermilion/sunset cryptic species pair.  Confirmation of 
species can only be determined via genetic analysis and species identification 
of these two fish caught in the Santa Barbara channel at approximately 250 ft depth 
is unknown. Photo courtesy of Sabrina Beyer.

<!--
\printnoidxglossary[sort=word]
-->


<!--chapter:end:01a-photo.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}


\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:01a.Rmd-->

# Executive Summary{-}
To be completed after the STAR panel.

## Stock{-}
This assessment reports the status of the vermlion rockfish (_Sebastes miniatus_) 
and sunset rockfish (_Sebastes crocotulus_) complex (referred to as vermilion 
throughout), resource in U.S. waters off the coast of California `r params$model` 
of Point Conception (\PtC) using data 
through 2020.


## Landings{-}
Replace text.

## Data and Assessment{-}
Replace text.

## Stock Biomass{-}
Replace text.

## Recruitment{-}
Replace text.

## Exploitation Status{-}
Replace text.

## Reference Points{-}
Replace text.

## Management Performance{-}
Replace text.

## Unresolved Problems and Major Uncertainties{-}
Replace text.

## Decision Table{-}
Replace text.

## Research and Data Needs{-}
Replace text.

<!--chapter:end:01executive.Rmd-->

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
\setcounter{figure}{0}

<!--chapter:end:10a.Rmd-->

# Introduction
Note to readers: Text in section is the same in both California `r spp` assessment 
documents.

```{r render-12, results = "asis"}
sa4ss::read_child("12basicinfo.Rmd")
```


```{r render-13, results = "asis"}
sa4ss::read_child("13fisheries.Rmd")
```


<!--chapter:end:11introduction.Rmd-->

# Data

The STAT presented proposed analyses and data sources for the 2021 `r spp` 
assessment during the PFMC Pre-Assessment Workshop for 2021 Vermilion and 
Lingcod Stock Assessments, hosted virtually on March 29, 2021. Topics addressed 
included progress on research priorities, data sources and types, stock structure, 
fleet structure, key model parameters (e.g. natural mortality), and potential 
challenges. Descriptions of each data source included in the model 
(Figure \@ref(fig:data-plot)) and sources that were explored, but not included
are included within this section.

## Fishery-Dependent Data

A complete summary of estimated `r spp` removals by each fleet in the 
commercial and recreational fleets modeled in this assessment is provided in Table 
\@ref(tab:landings).  The data sources for landings varied by each fleet and a summary 
of each data source and the time period for which it was used is in Table \@ref(tab:catch-source).
Of note is that the commercial landings are in metric tons (mt) and the recreational landings 
are in numbers of fish (thousands of fish). Data and 
methods used to derive these estimates are described in this section.



```{r render-21, results = "asis"}
sa4ss::read_child("21data-a-commercial.Rmd")
```


```{r render-21b, results = "asis"}
sa4ss::read_child("21data-b-recreational.Rmd")
```



```{r render-21c, results = "asis"}
sa4ss::read_child("21data-c-fishery-independent.Rmd")
```


```{r render-21d, results = "asis"}
sa4ss::read_child("21data-sources-not-used.Rmd")
```



```{r render-2, results = "asis"}
sa4ss::read_child("22biology.Rmd")
```


<!--chapter:end:20data.Rmd-->

# Assessment Model Description

## History of Modeling Approaches

Vermilion was assessed coastwide as a data poor species using 
Depletion-Based Stock Reduction Analysis (DB-SRA) [@Dick2010]. Average catch 
2008-2009 was 136.3 mt, and the median OFL in 2010 was 314.3 mt with a 28% 
probability that recent catch exceeded the 2010 [@Dick2010].

A 2005 assessment was not accepted for management. 
From the September 2005 [Briefing Book](https://www.pcouncil.org/documents/2005/09/f-groundfish-management-september-2005.pdf/): 
"The SSC considers the assessment to be best available science, but at this  stage does not 
endorse the results as being suitable for setting OYs." A 2013 data moderate 
assessment was prepared, but not reviewed. From Pacific Coast Groundfish Stock 
Assessment Review (STAR) Panel Report For Data-Moderate Assessments (2013): 
"There was insufficient time during the review to evaluate all the assessments 
originally requested by the Council. Assessments for vermilion/sunset rockfishes 
(*Sebastes miniatus* and *Sebastes crocotulus*) and yellowtail rockfish 
(south of \CapeM) were not presented by the Stock Assessment Team (STAT)."


### Most Recent STAR Panel and SSC Recommendations 

The 2005 STAR panel report compiled recommendations specific to vermilion, and also 
generic rockfish recommendations The generic rockfish recommendation are not 
presented here.  The 2005 assessment was not accepted for management by the PFMC.

**Vermilion rockfish recommendations**

Investigation into the species composition of nominal vermilion rockfish is needed.
It is not clear that separate assessments for the northern and southern areas are warranted
for vermilion rockfish. Although there were differences in the estimated magnitude and
timing of recruitment events, the estimated stock trends were similar in both areas.
Pooling of data from northern and southern areas may permit a more robust assessment
model to be obtained.

*2021 STAT response.* Since the 2005 assessment, vermilion rockfish were speciated 
to vermilion and sunset rockfishes [@Hyde2009].  Sunset rockfish are more common south of 
Pt. Conception (\PtC) and historical catches and length distributions between 
the two areas are different. The STAT discussed this at the Pre-Assessment workshop 
and all participants agreed that modeling the areas separately was an appropriate 
decision.




```{r render-31, results = "asis"}
sa4ss::read_child("31model-star-responses.Rmd")
```


```{r render-32, results = "asis"}
sa4ss::read_child("32model-description.Rmd") 
```



```{r render-34, results = "asis"}
sa4ss::read_child("34model-prestar-base-selection.Rmd")
```


<!--chapter:end:30model.Rmd-->

# Harvest Projections and Decision Tables

**This section will be completed after the STAR panel**
<!--
Projections of OFL (mt), ABC (mt), age 10+ biomass (mt), spawning output (billions of eggs), and depletion (% of unfished spawning output) are shown for the default harvest control rule in Table 62. Catch estimates for 2021 and 2022 are based on GMT recommendations (M. Mandrup, CDFW; pers. comm.), with frog mt for commercial and frog mt for recreational fleets. Projections assume a constant allocation among fleets equal to the recommended catch for 2021 and 2022 (frog% commercial, frog% commercial).
-->

## Regional Management and Spatial Management Considerations

Over the last several decades, spatially explicit management measures at both the state and federal/management council level have been implemented to achieve a wide range of marine resource and fishery management objectives. Depth restrictions to commercial and recreational fisheries in the Rockfish Conservation Areas (RCAs) and the Cowcod Conservation Areas (CCAs) are key among those, as are the suite of total and partial exclusion of commercial and recreational fishing activities in the California statewide network of Marine Protected Areas (MPAs). While the former are associated with explicit fisheries management objectives, the latter have a suite of ecological and economic objectives, most of which are not specific to, nor integrated across, the fisheries management arena. Despite this, both types of spatial management measures are expected to result in various biological, ecological, and socioeconomic effects within and adjacent to their boundaries.  All of these effects have the potential to influence the nature and quality of the data used to inform stock assessments of species that reside in these areas, including vermilion rockfish.

Regardless of the management objective, spatial closures are expected to increase the spatial heterogeneity in abundance and size or age structure of fished stocks. This greater spatial variability can complicate the assumptions made in stock assessment models, particularly the assumption that the densities and demographic structure of assessed populations are relatively homogeneous, at least across predictable habitat types such as bathymetric gradients or substrate types [@Punt2004; @Field2007; @Berger2017].  Although a wide range of factors above and beyond spatial management measures can also lead to violations of those assumptions, and the challenge is intuitively less problematic for populations with high movement rates and/or high population turnover, the challenge can be particularly important for longer lived populations with lower movement rates.  The challenge can best be summarized by the result that the more effective MPAs or other closed areas are at protecting populations within them, the more likely it is that traditional assessment approaches will be biased or more uncertain.  

If the spatial closures also prevent fisheries independent surveys from evaluating the relative abundance and demographic structure of managed populations, the challenges in developing robust population models, and thus robust management advice, become even more severe.  While spatially explicit assessment models provide a means of more explicitly addressing these challenges, such models are computationally intensive, require robust data from the specific areas being modeled, and may also require detailed information regarding movement and dispersal rates [@McGilliard2015; @Berger2017; @Puntet2020; @Cadrin2020].  Moreover, the complexity of these spatial models increases substantially if the size and location of closed areas changes over time, as many of the more “fisheries management based” closures (e.g., RCAs) have in California groundfish fisheries.  Thus, such approaches may be less feasible for more data limited stocks, such as northern and southern vermilion rockfish, at least in the near term.  However, the fact that both the northern and southern assessment models are informed by fishery-independent surveys that include habitats both inside and outside area closures provides some hope for greater recognition of spatial factors in future assessments.  



# Unresolved Problems and Major Uncertainties
We recommend the following research be conducted before the next assessment:

- Investigate the structure of complex and contribution of each species to the 
vermilion/sunset complex. Investigate possible spatial differences in biological parameters within 
a single species and also between the two species.  Little biological data for south of 
Point Conception or north of Point Arena were available for this assessment and is needed 
to better under biological parameters. 
  + Conduct life history studies
  + Conduct research to identify the proportion of each species in population and in catches

- Take a closer look at the Ralston historical catch reconstruction (\cite{Ralston2010}) and 
all other historical data sources.

- Refine CCFRP survey index to look at alternative possible model structures, including 
a hierarchical structure and random effects. The CCFRP survey is the only 
fishery-independent survey available for nearshore rockfish sampling the nearshore rocky 
reef habitats. As of this assessment, only two years of coastwide data are available, 
and the index was limited to the site in central California that have been monitored 
since 2007.

- Continue to investigate the most appropriate model structure for the NWFSC HL survey index.
The NWFSC HL survey is the only long-term fishery-independent survey in rocky (untrawlable) habitat 
in the Southern California Bight. We also recommend evaluating how to structure the NWFSC Hook-and-Line survey index given its expansion into the CCA, also independent analysis of information content in NWFSC Hook-and-Line survey.Increased spatiotemporal sampling around Pt. Conception would aid in identifying stock boundaries.

- Utilize existing ROV survey data sources
  + SWFSC Submersible Survey of the Cowcod Conservation Areas [@Yoklavich2007]. 
  +  This was a line-transect survey designed to estimate cowcod abundance in 2002 
  conducted from a submersible inside the CCAs.  Originally, only cowcod were enumerated from the video footage.  Over the last few years, the SWFSC has re-analyzed the video footage to enumerate other rockfish species. 
    + The SWFSC Fishery Resource Division (FRD) conducted a survey of potential cowcod habitat between Point Conception and the U.S. – Mexico border from October through December of 2012 [@Stierhoff2013].
    +  SWFSC staff are submitting proposals to conduct an additional submersible survey in the southern California Bight
    + CDFW ROV survey data


- Collection of length and age data are recommended for both the commercial and 
recreational fisheries.  Very little age data are available from either fishery for 
vermilion and sunset rockfishes.

- Investigate possible environmental drivers/co-variates for biological parameters, 
particularly for recruitment.

- Resolve differences between CalCOM and PacFIN expanded length composition data sets. 




<!--chapter:end:40management.Rmd-->

\clearpage

# Acknowledgments (not required for draft assessments)

<!--chapter:end:41acknowledgements.Rmd-->

\clearpage
\floatplacement{table}{H}

# Tables

```{r render-51, results = "asis"}
sa4ss::read_child("51tables-execsummary.Rmd")
```

```{r render-52, results = "asis"}
sa4ss::read_child("52tables-catch.Rmd")
```


```{r render-54, results = "asis"}
sa4ss::read_child("54tables-compsamplesize.Rmd")
```

```{r render-56, results = "asis"}
sa4ss::read_child("56tables-results.Rmd")
```


```{r render-57, results = "asis"}
sa4ss::read_child("57tables-uncertainty.Rmd")
```

<!--chapter:end:50tables.Rmd-->

\clearpage
# Figures


```{r render-61, results = "asis"}
sa4ss::read_child("61figures-data-catches.Rmd")
```


```{r render-62, results = "asis"}
sa4ss::read_child("62figures-lengths.Rmd")
```


```{r render-63, results = "asis"}
sa4ss::read_child("63figures-biology.Rmd")
```

\FloatBarrier

```{r render-64, results = "asis"}
sa4ss::read_child("64figures-selectivity-diagnostics.Rmd")
```

\clearpage
\FloatBarrier


```{r render-65, results = "asis"}
sa4ss::read_child("65figures-lenfits.Rmd")
```



\FloatBarrier

```{r render-67, results = "asis"}
sa4ss::read_child("67figures-indices-age.Rmd")
```


\FloatBarrier

```{r render-68, results = "asis"}
sa4ss::read_child("68figures-timeseries.Rmd")
```

\FloatBarrier

```{r render-68a, results = "asis"}
sa4ss::read_child("68a-figures-recruit-refpoints.Rmd")
```

\FloatBarrier

```{r render-69, results = "asis"}
#if(model.area=="NCA"){
sa4ss::read_child("69figures-sens-likeli-retro.Rmd")
# } else {
#   sa4ss::read_child("69figures-sens-likeli-retro-south.Rmd")
# }
```

<!--chapter:end:60figures.Rmd-->

\clearpage

# Appendix

## MRFSS Dockside Index of Abundance {#mrfss-index}

```{r mrfss-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_MRFSS_dockside_writeup_SCA.md") 
```
  
\clearpage
 
## California CPFV Onboard Index of Abundance {#cpfv-index}

```{r ca-cpfv-onboard-index, results = 'asis'}
 sa4ss::read_child("./indices/vermilion_CA_CPFV_onboard_writeup_SCA.md") 
``` 

\clearpage

## CRFS PR Dockside Index of Abundance {#pr-index}

```{r crfs-pr-index, results = 'asis'}
sa4ss::read_child("./indices/vermilion_CRFS_PR_dockside_writeup_SCA.md")
``` 

\clearpage

## NWFSC Hook-and-Line Survey Index of Abundance {#nwfschl-index}

```{r nwfschl-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_NWFSC_HL_writeup_SCA.md")
``` 


\clearpage

## WCGBTS Index of Abundance {#wcgbts-index}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_SCA.md")
``` 

\clearpage

## Recreational Regulations {#regs-graphic}

```{r wcgbts-index, results = 'asis'}
  sa4ss::read_child("./indices/vermilion_WCGBTS_writeup_SCA.md")
``` 


# References
       



<!--chapter:end:70appendices-south.Rmd-->

